### 2018-08-15 paper/main.tex
added paper

%
%Author: In this template, the places where you need to add information
%        (or delete line) are indicated by {???}.  Mostly the information
%        required is obvious, but some explanations are given in lines starting
%Author:
%All other lines should be ignored.  After editing, there should be
%no instances of ??? after this line.

% use option [preprint] to remove info line at bottom
% journal options: aop,aap,aos,aoas,ssy
% natbib option: authoryear
\documentclass[aap,preprint]{imsart}

\usepackage{amsthm,amsmath,amssymb}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{tikz,caption}
\usepackage{pgfplots}
\usepackage{subcaption}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

\startlocaldefs
\newtheorem{notation}{Notation}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\p}{\mathbb{P}}
\pgfplotsset{
    colormap={blackwhite}{[5pt]
        rgb255(0pt)=(255, 255, 0);
        rgb255(245pt)=(0, 0, 0);
        rgb255(255pt)=(0, 0, 255);
        rgb255(1000pt)=(200, 255, 255)
    },
}
\endlocaldefs

\begin{document}

\begin{frontmatter}

\title{An Engineered Empirical Burnstein Bound}
\runtitle{An Engineered Empirical Burnstein Bound}

\begin{aug}
\author{\fnms{Mark} \snm{Burgess}\corref{}\thanksref{t1}
\ead[label=e1]{mark.burgess@anu.edu.au}
\ead[label=e2]{markburgess1989@gmail.com}}
\thankstext{t1}{A great thanks to Archie Chapman, Paul Scott and Sylvie Thiebaux; for Academic advice and encouragement!}
\address{Mark Alexander Burgess\\College of Engineering \& Computer Science\\Australian National University\\Canberra, ACT, Australia, 2600\\\printead{e1}\\
\printead{e2}}
\affiliation{Australian National University}
\end{aug}

\runauthor{M. Burgess}

\begin{abstract}
We derive a stronger Empirical Burnstein Bound (EBB) using a combination of Chernoff bounds and probability unions.
Like other EBBs, our EBB is a concentration inequality for the divergence of the sample mean from the population mean in terms of the sample variance.
The new EBB is numerically solved and compared against previous work, and also against a bound with perfect information about the variance.
The analysis reveals that our technique can shrink existing probability bounds by about a third, and that perfect variance information would reduce it by about a third again.
\end{abstract}

\begin{keyword}[class=MSC]
\kwd[60E15]{}
\kwd[; 62H10]{}
\end{keyword}

\begin{keyword}
\kwd{Concentration inequality}
\kwd{Chernoff bounds}
\kwd{Hoeffdings inequality}
\kwd{Emperical Burnstein Bound}
\end{keyword}

\end{frontmatter}

\section{Introduction}

Sample statistics are sometimes used to estimate the statistical parameters of the population (eg. mean, variance, etc).
And different methods of doing this are available depending on the sample statistics provided and the assumptions which are made about the population.
A recent development is Empirical Burnstein Bounds (EBB)\cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15} which are probability bounds describing the likely divergence of the sample mean from the mean in terms of the sample variance under assumption that the population data is bounded within an interval of a known width.
EBBs have been used as a method of giving confidence bounds for the mean, which is a common and important process in many industrial applications.
We take inspiration and extend Maurer and Pontil's work \cite{Maurer50empiricalbernstein} as we combine older techniques to develop a new and stronger EBB

\section{Related Work}
Concentration inequalities are particular probabilistic bounds describing how much a random variable is expected to deviate (or otherwise be concentrated) around a particular value.
Famous historical concentration inequalities have often describe the expected deviation of sample statistics.
For instance, Chebyshev's inequality was known as far back as 1853\cite{Chebyshev1}, and some of the early Burnstein inequalities were published in the 1920s \cite{burnstein1}.
Since then, various analysis has yielded a wide range new concentration inequalities\cite{MR3363542,Boucheron2004}; particularly important are the innovations concerning the concentration of more general functions of random variables - for instance the Effron-Stein\cite{efron1981} and Entropy methods \cite{Boucheron_concentrationinequalities}, and applications of Talagrand's concentration inequality\cite{Talagrand1995}.

Inequalities such as these can describe the expected deviation of sample statistics - particularly often the sample mean, such as famously the Burnstein's inequalities \cite{burnstein1}, Hoeffding's inequalities \cite{hoeffding1} Bennett's inequalities \cite{10.2307/2282438} among others.
These inequalities have been used in various contexts, such as in machine learning and hypothesis testing.\cite{Maron1997,Mnih:2008:EBS:1390156.1390241,8000571,Zia-UrRehman2012,DBLP:conf/aaai/ThomasTG15,Maurer50empiricalbernstein}
Recently, the sample variance has also been incorporated into this process as EBBs \cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15} and it remains to be seen how much these EBBs can be sharpened.

\section{Structure}

\begin{itemize}{\leftmargin=1em}
\item[-] We begin in section \ref{background} with fundamental concepts: probability unions, Chernoff bounds, and a decomposition of the sample variance into the mean of sample squares and sample mean.
\item[-] In section \ref{derivation} we outlay two Chernoff bounds (for the sample mean and the mean of sample squares) and use them with a probability union and variance decomposition to create a novel probability bound for the sample variance. After this we use probability union again to create a new EBB.
\item[-] In section \ref{evaluation} we numerically evaluate our EBB and compare it against Maurer and Pontil's EBB to show improvements.
\item[-] In section \ref{discussion} we give some simple expressions as envelopes over our numerical EBB and finish with a caution about its use.
\end{itemize}

\section{Background}\label{background}

To begin we introduce useful lemmas that form the basis for our derivation, the first is an often used result related to union bounds:

\begin{lemma}[Probability Union]\label{prob_union}
For random variables $a,b,c$ that:\\ $\p(a>c) \le \p(a>b) + \p(b>c)$
\end{lemma}
\begin{proof}
For any events $A$ and $B$ that:\\
$\p(A\cup B)\le \p(A)+\p(B)$
hence:\\
$\p((a>b) \cup (b>c))\le \p(a>b) + \p(b>c)$\\
If $a>c$ then $(a>b) \cup (b>c)$ is true irrespective of $b$ hence:\\
$\p(a>c) \le \p((a>b) \cup (b>c))$ and the conclusion follows.
\end{proof}

If $\p(a>c)$ is unknown but if a relationship between $a$ and some $b$, and also between $b$ and $c$ is known, then such a probability union may be useful.
The next lemma is a quick and well known result that relates the value of the sample mean and the value of sample squares to the sample variance.

\begin{lemma}[Variance Decomposition]\label{variance1}
For $\hat{\sigma}^2$ as sample variance, $\hat{\sigma}_0^2$ as average of sample squares, and $\hat{\mu}$ as sample mean, then:
$ \hat{\sigma}_0^2 = \hat{\mu}^2+\frac{n-1}{n}\hat{\sigma}^2 $
\end{lemma}
\begin{proof}
for samples $x_i$ that\\
$\hat{\sigma}^2=\frac{1}{n-1}\sum_i(x_i-\frac{1}{n}\sum_jx_j)^2 = \frac{1}{n-1}\sum_i(x_i-\frac{1}{n}\sum_jx_j)^2$\\
$=\frac{1}{n-1}(\sum_ix_i^2-\frac{1}{n}\sum_i\sum_jx_ix_j) = \frac{1}{n-1}(n\hat{\sigma}_0^2-n\hat{\mu}^2)$.
\end{proof}

It is by this equality that we will create bounds for the sample variance from bounds on the sample squares and sample mean.
However, In order to get these bounds we will use the next lemma. This lemma is the basis of a large number of inequalities called Chernoff bounds and is an application of Markov's inequality to give bounds on the mean of random variables\cite{hoeffding2}:

\begin{lemma}[Chernoff Bound]\label{chernoff1}
If $\hat{\mu}$ is sample mean of $n$ samples of random variable $X$ then for any $s>0$ and $t$:
$$ \textstyle\p(\hat{\mu}\ge t)\le\frac{\E\left[\exp(sX)\right]^n}{\exp(snt)} $$
\end{lemma}
\begin{proof}
$\p(\hat{\mu}\ge t) = \p(\exp(s\sum_ix_i)\ge \exp(snt))$\\
$\p(\hat{\mu}\ge t) \le \E[\exp(s\sum_ix_i)]\exp(-snt)$ via Markov's inequality \\ 
$\p(\hat{\mu}\ge t) \le \E\left[\exp(sX)\right]^n\exp(-snt)$ assuming i.i.d of samples.
\end{proof}

We will be using this to get the bounds on the sample mean and the mean of sample squares.
And with lemmas \ref{prob_union} and \ref{variance1} we will create a new EBB.

\section{Derivation}\label{derivation}

Our first probability bound is a Chernoff bound on the sample mean. This bound is not new and was derived by Wassily Hoeffding\footnote{Apparently it is also known as Bennet's inequality\cite{MR1782937}} \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598,MR1782937}.

\begin{theorem}[Hoeffding's inequality]\label{hoeffdings1}
For a random variable with a mean of zero that is bounded $a\le X\le b$, then the mean $\hat{\mu}$ of $n$ samples is probability bounded. For $t>0$:
\begin{equation}\label{eq_no2} \textstyle\p(\hat{\mu}\ge t)\le 
\left(\left(\frac{\sigma^2}{b^2}(\frac{\sigma^2}{b^2}+\frac{t}{b})^{-1}\right)^{\frac{\sigma^2}{b^2}+\frac{t}{b}}
\left(1-\frac{t}{b}\right)^{\frac{t}{b}-1}\right)^{n(\frac{\sigma^2}{b^2}+1)^{-1}} = H_1^n\left(\frac{\sigma^2}{b^2},\frac{t}{b}\right) \end{equation}
\end{theorem}
\begin{proof}
For $\alpha,\beta,\gamma$ that $\alpha s^2X^2+\beta sX+\gamma\ge \exp(sX)$ for all $a\le X\le b$:\\
$E\left[\exp(sX)\right] \le \E[\alpha s^2X^2+\beta sX+\gamma] = \alpha s^2\E[X^2]+\gamma = as^2\sigma^2+c$\\
If $c=\max(sa,sb)$ choosing $\alpha,\beta,\gamma$ to minimize the expression leads\footnote{see Appendix \ref{appendix1}} to:\\
$E\left[\exp(sX)\right] \le (s^2\sigma^2\exp(c) + c^2\exp(-s^2\sigma^2/c))/(s^2\sigma^2 + c^2) $\\
Hence by application of our lemma \ref{chernoff1}:\\
$ \textstyle\p(\hat{\mu}\ge t)\le \left(s^2\sigma^2\exp(c) + c^2\exp(-s^2\sigma^2/c)\right)^n\exp(-nst)(s^2\sigma^2 + c^2)^{-n} $\\
minimizing with respect to $s$ gives the result.
\end{proof}
We will also use a double sided version:
\begin{equation}\label{eq_no1} \textstyle\p(|\hat{\mu}|\ge |r|)=\p(\hat{\mu}^2\ge r^2)\le H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right) \end{equation}
The assumption that the mean is zero occurs without a loss of generality.
And in this way Hoeffding's inequality gives us a probability bound for the divergence of the sample mean from the true mean given the variance. However in practice we often don't know the variance but can only estimate it via a sample variance statistic.
So we endeavor to create a bound to characterize the divergence of the sample variance from the variance, we begin with a bound on the sample squares:

\begin{lemma}[Sample Square bound]\label{sample_squares}
For a random variable with a mean of zero that is bounded $a\le X\le b$, then the mean $\hat{\sigma}_0^2$ of $n$ samples squares is probability bounded:
\begin{align*} \p(\sigma^2 - \hat{\sigma}_0^2> y) \le \min_{\substack{s>0,\alpha,\beta,\gamma \\ \text{s.t}~\alpha x^2 + \beta x + \gamma\ge\exp(-sx^2)\\ \forall x\in[a,b]}} &\left(\exp(s(\sigma^2-y))(\alpha\sigma^2 + \gamma)\right)^n \\& ~~= H_2^n(a,b,y,\sigma^2)
\end{align*}
\end{lemma}
\begin{proof}
For $\alpha,\beta,\gamma$ that $\alpha X^2 + \beta X + \gamma \ge \exp(-qX^2)$ for all $a\le X\le b$:\\
$ \E[\exp(-qX^2)] \le \E[\alpha x^2 +\beta x +\gamma] \le \alpha\sigma^2 + \gamma $\\
Applying lemma \ref{chernoff1} to the mean of minus sample squares, gives:\\
$\p(-\hat{\sigma}_0^2\ge t) \le (\alpha\sigma^2 + \gamma)^n\exp(-snt) $\\
Substituting $t$ for $y-\sigma^2$ gives:\\
$\p(\sigma^2 - \hat{\sigma}_0^2> y) \le ((\alpha\sigma^2 + \gamma)\exp(s(\sigma^2-y)))^n $\\
Minimizing subject to constraints gives result.
\end{proof}

This probability bound is not easily put into closed form and so we will use numerics to evaluate it as necessary.
It is worth noting that the domain of function $H_2^n$ is restricted, firstly that it is defined for $a<0<b$ and secondly that $\sigma^2\le-ab\le (b-a)^2/4$ per Popoviciu's inequality \cite{zbMATH05780164}. It is important that these restrictions should propagate with the analysis.

At this point we have a probability bound on the mean squared by equation \ref{eq_no1} and also a probability bound on the sample squares by lemma \ref{sample_squares}. We proceed by using lemma \ref{variance1} to create a bound on the sample variance as follows:

\begin{theorem}[Sample Variance Bound]\label{variance2}
For a random variable that is bounded $a\le X\le b$ with variance $\sigma^2$ and a mean of zero, the sample variance $\hat{\sigma}^2$ of $n$ samples is probability bounded:
\begin{align}\label{eq_no8} \p(\sigma^2 - \hat{\sigma}^2 > w)\le &\min_{\phi\in[0,1]}
\begin{pmatrix}
	H_2^n\left(a,b,(1-\phi)(\frac{n-1}{n}w+\frac{1}{n}\sigma^2),\sigma^2\right)\\
	+H_1^n\left(\frac{\sigma^2}{b^2},\frac{\sqrt{\phi(\frac{n-1}{n}w+\frac{1}{n}\sigma^2)}}{b}\right)\quad\quad\\
	+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-\sqrt{\phi(\frac{n-1}{n}w+\frac{1}{n}\sigma^2)}}{a}\right)
\end{pmatrix} \\
&=H_3^n(a,b,w,\sigma^2)\nonumber\end{align}
\end{theorem}
\begin{proof}
By lemma \ref{sample_squares}: $\p(\sigma^2 - \hat{\sigma}_0^2> y) \le H_2^n(a,b,y,\sigma^2)$\\
So by lemma \ref{variance1}: $\p\left(\sigma^2 - \hat{\sigma}^2 > \frac{n}{n-1}\left(\hat{\mu}^2+y-\frac{1}{n}\sigma^2\right)\right) \le H_2^n(a,b,y,\sigma^2)$\\
Also by manipulatin the inner inequality of equation \ref{eq_no1}: \\$\p\left(\frac{n}{n-1}\left(\hat{\mu}^2+y-\frac{1}{n}\sigma^2\right)\ge \frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)\right)\le H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right)$\\
Applying union bound (lemma \ref{prob_union}) to the above two equations gives:\\
$\p\left(\sigma^2 - \hat{\sigma}^2 > \frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)\right) \le H_2^n(a,b,y,\sigma^2)+H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right)$\\
We let $w=\frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)$. And for a given $w$ we have a range of possible $r>0$ and $y>0$ which we want to parameterize over with $0\le\phi\le 1$:\\
$y(\phi) = (1-\phi)\left(\frac{n-1}{n}w+\frac{1}{n}\sigma^2\right)$ and
$r(\phi)^2 = \phi\left(\frac{n-1}{n}w+\frac{1}{n}\sigma^2\right)$\\
$\p\left(\sigma^2 - \hat{\sigma}^2 > w\right) \le H_2^n(a,b,y(\phi),\sigma^2)+H_1^n\left(\frac{\sigma^2}{b^2},\frac{r(\phi)}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r(\phi)}{a}\right)$\\
The result follows by minimizing over $\phi$.
\end{proof}
This function $H_3^n$ is subject to similar restrictions as $H_2^n$.\\
Thus we now have a probability bound for the divergence of the sample variance from the variance, and by theorem \ref{hoeffdings1} we have a bound for the sample mean given the variance. We combine these two together to create a bound for the sample mean given the sample variance - and thus a new Empirical Burnstein Bound.
To proceed further we outlay a theorem that embodies a process slightly improved from that followed by Maurer and Pontil \cite{Maurer50empiricalbernstein}. We state some notation to ease the presentation:

\begin{notation}
For a function $f$ with numbered inputs, we denote the inverse of $f$ with respect to its $i$'th input (counting from one) as $f^{-i}$, assuming it exists.
\end{notation}

\begin{theorem}[Essential EBB]\label{ebb1} If we have bounds between the mean and sample mean, and the variance and sample variance:
\\ $\p(\hat{\mu}-\mu>t)\le h(\sigma^2,t)$\\
$\p(\sigma^2-\hat{\sigma}^2>w)\le f(\sigma^2,w)$ \\ 
for $f$ and $h$ depending on those two parameters (not exclusively)\\
if $z(\sigma^2,w) = \sigma^2-f^{-2}(\sigma^2,w)$ and $f^{-2}$ exists\\
if $z^{-1}$ exists and is monotonic increasing in its first argument\\
if $h^{-2}$ exists and is monotonically increasing in its first argument\\then for $x\in[0,y]$:\\
$\p(\hat{\mu}-\mu>h^{-2}(z^{-1}(\hat{\sigma}^2,y-x),x))\le y$
\end{theorem}
\begin{proof}
Substituting $w\rightarrow f^{-2}(\sigma^2,w)$ gives\\ 
$\p(\sigma^2-\hat{\sigma}^2>f^{-2}(\sigma^2,w))\le w$\\
thus:
$\p(z(\sigma^2,w)>\hat{\sigma}^2)\le w$\\
hence:
$\p(\sigma^2>z^{-1}(\hat{\sigma}^2,w))\le w$\\
so:
$\p(h^{-2}(\sigma^2,t)>h^{-2}(z^{-1}(\hat{\sigma}^2,w),t))\le w$

Substituting $t\rightarrow h^{-2}(\sigma^2,t)$ gives\\ $\p(\hat{\mu}-\mu>h^{-2}(\sigma^2,t))\le t$\\
applying probability union (lemma \ref{prob_union}) gives:\\
$\p(\hat{\mu}-\mu>h^{-2}(z^{-1}(\hat{\sigma}^2,w),t))\le t+w$\\
letting $y=t+w$ and $x=y-w$ gives:\\
$\p(\hat{\mu}-\mu>h^{-2}(z^{-1}(\hat{\sigma}^2,y-x),x))\le y$
\end{proof}

The result of this theorem is an EBB - that is a probabilistic bound for the divergence of the sample mean from the mean parametrized by the sample variance. Care must be taken in applying this theorem that all the assumptions hold, the inverses exist, and the domains of the functions are propagated through the analysis\footnote{see notes in Appendix \ref{appendix2}}.

In applying theorem \ref{ebb1} to the results of theorems \ref{variance2} and \ref{hoeffdings1} (letting $h(\sigma^2,t)=H_1^n\left(\sigma^2/b^2,t/b\right)$ and $f(\sigma^2,w)=H_3^n(a,b,w,\sigma^2)$) we typically don't know the values of $a$ and $b$ but instead know the mean is somewhere within a finite interval of width $D=b-a$.
So after applying theorem \ref{ebb1} we take the worst case values of $a$ and $b$ consistent with a given $D$ and $\sigma^2$, and take the best $x\in[0,y]$ subject to all other bounds.
And we are done.

\begin{figure}[h]
\centering
\captionsetup{justification=centering,margin=0.01cm}
\begin{tikzpicture}
\begin{axis}[
	xmin=0,   xmax=0.25,
	ymin=0,   ymax=0.25,
	zmin=-0.15,   zmax=1.0,
	xtick={0.05,0.10,0.15,0.20,0.25},
	ytick={0.05,0.10,0.15,0.20},
	%ztick={-0.2,-0.1,0,0.1},
	xlabel=$\frac{\sigma^2}{D^2}$,
	ylabel=$\frac{w}{D^2}$,
	%zlabel=$blah$,
	xticklabel style={/pgf/number format/fixed},
	yticklabel style={/pgf/number format/fixed},
	zticklabel style={/pgf/number format/fixed},
	view={-110}{35},
	%point meta min=-0.3, point meta max=0.3,
	point meta min=-0.1, point meta max=0.3,
	title={Advantage over Entropic bound for n=200},
	%colorbar horizontal,
	colorbar,
	colorbar style={
        at={(1.07,0.66)},
		title=Advantage,
		%ylabel=Z-value,
		%ytick={-1,-0.75,...,1},
        height=0.54*\pgfkeysvalueof{/pgfplots/parent axis height},
		xticklabel style={
			text width=2.5em,
			%align=below,
			%anchor=north west,
			/pgf/number format/.cd,
			fixed,
			fixed zerofill
		}
	}
]
\addplot3[patch, shader=flat] 
	file
	{graph1.dat};
\end{axis}
\end{tikzpicture}
\caption{Our variance bound over Entropic bound:\\$\scriptstyle\exp\left(\frac{-(n-1)w^2}{2\sigma^2D^2}\right)-\max_{b\in\left[0.5,0.5-\sqrt{0.25-\sigma^2/D^2}\right]}H_3^n\left(D(1-b),Db,w,\sigma^2\right)$}
\label{biggraph2}
\end{figure}

\section{Evaluation}\label{evaluation}
Evaluating this new EBB consisted of numerically solving a minimization over a maximization over inversions of nested function minimizations.
This process was conducted in C and Python, using techniques of direct parameter searching, coordinate transforming of data points (for inversions) and interpolations as necessary.\footnote{see Appendix \ref{appendix2} for discussion of the details}
And through this process we were able to witness that the assumptions necessary for our theorems held true and thus were able evaluate our new EBB.

We began by comparing our variance bound (per theorem \ref{variance2}) against the entropic bound utilized in Maurer and Pontil's work \cite{Maurer50empiricalbernstein}, originally per \cite{MR2245497}:
\begin{equation}\label{eq:fe} \p(\sigma^2 - \hat{\sigma}^2>w) \le \exp\left(\frac{-(n-1)w^2}{2\sigma^2D^2}\right) \end{equation}
The advantage of our variance bound is shown in figure \ref{biggraph2}.
From this graph we see large regions of advantage and hence we suspect our variance bound may be of independent interest.
It is possible to take the minima of several bounds, hence we used the minima of our variance bound and the entropic bound in the creation of our EBB for good measure.

We also compared our EBB directly with Maurer and Pontil's EBB\cite{Maurer50empiricalbernstein}:
$$ \p\left(\mu-\hat{\mu}>\sqrt{\frac{2\hat{\sigma}^2\log(2/y)}{n}}+\frac{7D\log(2/y)}{3(n-1)}\right)<y $$
We felt were able to fairly compare in the domain of their EBB if had they carried Popoviciu's inequality in their derivation, specifically the domain where:
$$ \frac{1}{2}>\frac{\sqrt{\hat{\sigma}^2}}{D}+\sqrt{\frac{2\log(2/y)}{n-1}} $$
Hence we were able to plot the improvement our EBB offers in this domain, as shown in figure \ref{biggraph3}. In this graph a probability 0.5 bound is shown to approximately shrink by at least a third irrespective of $n$.
More generally we note that our expectations were confirmed as our refinement of their EBB was seen to be tighter across a large range of values.

We also compared the loss in confidence that our EBB gave over a bound which could be achieved with perfect information about the variance. Specifically Hoeffding's inequality\footnote{Hoeffding's inequality per theorem \ref{hoeffdings1} is understood here to be relatively tight.} assuming $\hat{\sigma}^2=\sigma^2$. The decrease of the bounds that perfect variance information would offer over our EBB is plotted in figure \ref{biggraph4}.
From this graph we notice that when the variance is small there is the most potential gain to be made and where uncertainty about the variance is most detrimental, but generally that going from our EBB to perfect variance information shrinks the bounds by about another third.

\begin{figure}[]
	\centering
    \begin{subfigure}[b]{.76\linewidth}
        \centering
		\begin{tikzpicture}
		\begin{axis}[
			title={Percent reduction of a probability 0.5 bound that our EBB achieves},
			xlabel={$\hat{\sigma}^2/D^2$},
			xmin=0, xmax=0.25,
			ymin=25, ymax=45,
			xtick={0,0.05,0.1,0.15,0.2,0.25},
			ytick={25,30,35,40,45},
			yticklabel=$\pgfmathprintnumber{\tick}\%$,
			ymajorgrids=true,
			grid style=dashed,
			xticklabel style={/pgf/number format/fixed},
		]
		\addplot[] coordinates {
		(0.005, 31.33262397944378)(0.01, 34.72886250674945)(0.015, 36.909296945183726)(0.02, 38.627583846687266)(0.025, 39.59462124039761)
			}node[pos=1.0](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=25$};
		\addplot[] coordinates {
		(0.005, 28.333532153239666)(0.01, 31.153830409409)(0.015, 32.87549096079947)(0.02, 33.81992265562242)(0.025, 34.89945361309619)(0.03, 35.74891595008532)(0.035, 36.60739883058407)(0.04, 37.276099921865196)(0.045, 37.59026746494855)(0.05, 38.218754538940686)(0.055, 38.83065159779602)(0.06, 39.39861647873854)(0.065, 39.910212250065214)
			}node[pos=1.0](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=50$};
		\addplot[] coordinates {
		(0.005, 30.038701393161688)(0.01, 31.412520149627277)(0.015, 32.49171315420119)(0.02, 32.876510879893)(0.025, 33.61899806422779)(0.03, 34.07734163182933)(0.035, 34.27418933046886)(0.04, 34.76092837396386)(0.045, 35.00082505166452)(0.05, 35.60742157468709)(0.055, 36.00845546401498)(0.06, 36.09363022383078)(0.065, 36.49561598871189)(0.07, 36.871363860949025)(0.075, 36.995564126738095)(0.08, 37.25705721710657)(0.085, 37.63281018078307)(0.09, 37.94537201050319)(0.095, 38.313563615135976)(0.1, 38.57428091364722)(0.105, 38.898129385115695)(0.11, 38.919035439297076)
			}node[pos=1.0](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=100$};
		\addplot[] coordinates {
		(0.005, 31.585709637284875)(0.01, 32.14640200496432)(0.015, 32.480242185958275)(0.02, 32.72477439020389)(0.025, 32.85137640603805)(0.03, 33.164192395805884)(0.035, 33.41972794004208)(0.04, 33.34159833965975)(0.045, 33.824240924074424)(0.05, 33.77957868846732)(0.055, 34.028900979162536)(0.06, 34.23479104354531)(0.065, 34.320408892537166)(0.07, 34.556516165135605)(0.075, 34.775904883097695)(0.08, 34.98535349546355)(0.085, 35.19862669231675)(0.09, 35.3945988354474)(0.095, 35.601977507693036)(0.1, 35.72487858163208)(0.105, 35.83625307070917)(0.11, 36.04135799347741)(0.115, 36.25828614993272)(0.12, 36.48817284893286)(0.125, 36.73194354036559)(0.13, 36.91341720219515)(0.135, 37.18914713784862)(0.14, 37.407683615789495)(0.145, 37.415360037546876)
			}node[pos=1.0](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=200$};
		\addplot[] coordinates {
		(0.005, 30.95805680601551)(0.01, 31.852731472234087)(0.015, 31.65165353001502)(0.02, 31.838019953330228)(0.025, 31.80514856457896)(0.03, 32.049553438239556)(0.035, 31.874671808872318)(0.04, 32.15628114167258)(0.045, 32.18970870320976)(0.05, 32.29347571578702)(0.055, 32.328022832020885)(0.06, 32.32551565971646)(0.065, 32.51203709690735)(0.07, 32.671571263469616)(0.075, 33.00950294213178)(0.08, 32.921019505844626)(0.085, 33.017153308081845)(0.09, 33.11615572233624)(0.095, 33.393651317961485)(0.1, 33.19788472106813)(0.105, 33.458020247263455)(0.11, 33.5638596989855)(0.115, 33.685389159897156)(0.12, 33.74232351659747)(0.125, 33.86778330552732)(0.13, 34.01232127428546)(0.135, 34.31523066744031)(0.14, 34.360222768291344)(0.145, 34.35739937066466)(0.15, 34.42537992870109)(0.155, 34.52118296490931)(0.16, 34.64446824473269)(0.165, 34.79488974531291)(0.17, 34.972098710274665)(0.175, 35.1757460413815)(0.18, 35.294877117787664)
			}node[pos=1.0](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=500$};
		\addplot[] coordinates {
		(0.005, 30.260287580516597)(0.01, 31.072712082932913)(0.015, 30.438989170134068)(0.02, 31.07887032375107)(0.025, 31.03408484266436)(0.03, 30.826085689381884)(0.035, 31.046097650764082)(0.04, 31.154259509093446)(0.045, 31.016858116914054)(0.05, 31.183097869794107)(0.055, 31.225975525465564)(0.06, 31.23249090698877)(0.065, 31.428023434202135)(0.07, 31.489666903553392)(0.075, 31.56173735319704)(0.08, 31.761301359885042)(0.085, 31.729964289057005)(0.09, 31.886510772066785)(0.095, 32.04347363722421)(0.1, 32.20435818840492)(0.105, 32.371965761927385)(0.11, 32.21538679904917)(0.115, 32.38001692151431)(0.12, 32.48085273757601)(0.125, 32.525780745561875)(0.13, 32.54658216492318)(0.135, 32.74841841730962)(0.14, 32.73824299176051)(0.145, 32.744293569773916)(0.15, 32.7796880354745)(0.155, 32.844022563820616)(0.16, 32.936888670494405)(0.165, 33.05787673349303)(0.17, 33.027986659386485)(0.175, 33.20865432723783)(0.18, 33.246662344351044)(0.185, 33.484850761982344)(0.19, 33.58811058089041)(0.195, 33.72513316286922)(0.2, 33.74255294433519)
			}node[pos=1.0](endofplotsquare){} ;
		\node [below] at (endofplotsquare) {$n=1000$};
		\end{axis}
		\end{tikzpicture}
		\caption{The percent reduction of the 0.5 probability bound, that going from Maurer and Pontil's EBB to our EBB would achieve, for various $n$, in the domain valid for their EBB.}
		\label{biggraph3}
    \end{subfigure}\\
    \vspace{5mm}
    \begin{subfigure}[b]{.76\linewidth}
        \centering
		\begin{tikzpicture}
		\begin{axis}[
			title={Percent reduction of a probability 0.5 bound yet potentially possible},
			xlabel={$\hat{\sigma}^2/D^2$},
			xmin=0, xmax=0.25,
			ymin=0, ymax=100,
			xtick={0,0.05,0.1,0.15,0.2,0.25},
			ytick={0,20,40,60,80,100},
			yticklabel=$\pgfmathprintnumber{\tick}\%$,
			legend pos=south west,
			ymajorgrids=true,
			grid style=dashed,
			xticklabel style={/pgf/number format/fixed},
		]
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 76.80881648298994)(0.01, 70.80012751036021)(0.015, 66.60353535353535)(0.02, 62.960629921259844)(0.025, 59.830268741159834)(0.03, 57.38265464718681)(0.035, 54.86272684969753)(0.04, 52.966426490878426)(0.045, 50.833715771760744)(0.05, 49.34260238778903)(0.055, 47.48114630467571)(0.06, 46.261543044384865)(0.065, 45.21393912659903)(0.07, 43.60780860120358)(0.075, 42.741234424804404)(0.08, 41.970541970541966)(0.085, 41.27275292789615)(0.09, 41.34324249931186)(0.095, 40.828241683638836)(0.1, 40.36967586391642)(0.105, 40.67885117493473)(0.11, 40.33732457834427)(0.115, 40.80762478053674)(0.12, 41.318681318681314)(0.125, 41.896387832699624)(0.13, 42.54679916801479)(0.135, 43.2678270634475)(0.14, 44.87427466150871)(0.145, 46.60652040188641)(0.15, 48.55862874951305)(0.155, 50.767251676927316)(0.16, 53.47442378545112)(0.165, 59.068590983484604)
			}node[pos=0.7](endofplotsquare){} ;
		\node [above right] at (endofplotsquare) {$n=10$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 77.6561403508772)(0.01, 71.34845838015866)(0.015, 66.77283196861327)(0.02, 62.981189851268596)(0.025, 60.0)(0.03, 57.0902927514777)(0.035, 54.45127942244435)(0.04, 51.96859607876512)(0.045, 49.97258771929825)(0.05, 47.57404572092287)(0.055, 45.676705541500894)(0.06, 43.987817089452605)(0.065, 42.12854540723393)(0.07, 40.28687246647957)(0.075, 38.81136950904393)(0.08, 36.880072137060424)(0.085, 35.22028211023427)(0.09, 33.87552312037438)(0.095, 32.53546508941362)(0.1, 30.81437249047669)(0.105, 28.95112416489131)(0.11, 27.395132055929572)(0.115, 26.174496644295303)(0.12, 24.903425186711306)(0.125, 23.670007710100233)(0.13, 23.065173116089614)(0.135, 21.940071102082275)(0.14, 20.811153358681874)(0.145, 20.550688360450565)(0.15, 19.490254872563717)(0.155, 19.37869822485207)(0.16, 19.30933852140078)(0.165, 19.34787820666507)(0.17, 19.38534278959811)(0.175, 20.506329113924053)(0.18, 20.644283121597095)(0.185, 22.798605056669572)(0.19, 24.916247906197654)(0.195, 27.07537688442211)(0.2, 31.11861861861862)(0.205, 35.2304469273743)(0.21, 41.46645865834633)(0.215, 51.718869365928185)
			}node[pos=0.7](endofplotsquare){} ;
		\node [above right] at (endofplotsquare) {$n=25$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 73.41959943954505)(0.01, 66.4436173582515)(0.015, 61.55984585594049)(0.02, 57.93403164698015)(0.025, 54.687443245795656)(0.03, 51.969260326609025)(0.035, 49.440167949615116)(0.04, 47.26428079834825)(0.045, 45.52155103348822)(0.05, 43.63969363969365)(0.055, 41.895873454808815)(0.06, 40.23579989577905)(0.065, 38.6774968170317)(0.07, 37.13806461919406)(0.075, 36.073059360730596)(0.08, 34.695663042119726)(0.085, 33.263492802545294)(0.09, 31.835726416550862)(0.095, 30.517167250168896)(0.1, 29.4787827093551)(0.105, 27.9820525495266)(0.11, 27.141351798886053)(0.115, 25.998680422264876)(0.12, 25.14569457659372)(0.125, 23.599320882852297)(0.13, 22.825830083894598)(0.135, 21.39899438036083)(0.14, 20.631424375917767)(0.145, 19.502512341971507)(0.15, 18.148213342721355)(0.155, 17.384900322293685)(0.16, 16.283268301205524)(0.165, 14.950369495824049)(0.17, 13.428466886205634)(0.175, 12.641165755919854)(0.18, 11.73265528514348)(0.185, 10.732414793328498)(0.19, 10.808876163206872)(0.195, 9.896391568417291)(0.2, 10.109193377949982)(0.205, 11.514736120630568)(0.21, 13.028990336554482)(0.215, 15.574032619123763)(0.22, 21.29793510324484)(0.225, 28.771466314398943)(0.23, 40.30243261012492)
			}node[pos=0.745](endofplotsquare){} ;
		\node [above] at (endofplotsquare) {$n=50$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 66.63264504985476)(0.01, 59.04596954607779)(0.015, 53.999488883209814)(0.02, 50.347727640304065)(0.025, 47.17075223238636)(0.03, 44.61167971101746)(0.035, 42.5287356321839)(0.04, 40.44242768009076)(0.045, 38.82229464729603)(0.05, 36.95086234949561)(0.055, 35.37062155908402)(0.06, 34.21394768318686)(0.065, 32.83438879293802)(0.07, 31.577620967741936)(0.075, 30.56930693069307)(0.08, 29.513914294773297)(0.085, 28.306342780027)(0.09, 27.2679657647577)(0.095, 26.1414503133393)(0.1, 25.240174672489086)(0.105, 24.242424242424242)(0.11, 23.719661228897856)(0.115, 22.66414141414141)(0.12, 21.690588327422837)(0.125, 20.795378804710058)(0.13, 19.986774673499745)(0.135, 19.030112044817923)(0.14, 18.19329010922065)(0.145, 17.679088336256697)(0.15, 16.523420713364853)(0.155, 15.733937115516067)(0.16, 15.263202437373053)(0.165, 14.070096816471484)(0.17, 13.594470046082947)(0.175, 12.479061976549408)(0.18, 11.941848390446522)(0.185, 10.83476924993254)(0.19, 10.110966462091636)(0.195, 9.32322149863986)(0.2, 8.034350357128114)(0.205, 6.9143446852425186)(0.21, 6.365503080082135)(0.215, 5.532786885245901)(0.22, 5.906108026249369)(0.225, 6.26865671641791)(0.23, 10.4)(0.235, 19.900083263946712)(0.24, 39.94439295644115)
			}node[pos=1.0](endofplotsquare){} ;
		%\node [above] at (endofplotsquare) {$n=100$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 58.98664343786295)(0.01, 50.57766367137355)(0.015, 45.77709671715683)(0.02, 42.100909842845326)(0.025, 39.265978521530606)(0.03, 36.95646756871246)(0.035, 34.86590038314177)(0.04, 33.287324591672416)(0.045, 31.549749463135292)(0.05, 30.303030303030305)(0.055, 28.925445534113674)(0.06, 27.7629141798724)(0.065, 26.8988231513837)(0.07, 25.831202046035806)(0.075, 24.751099791618426)(0.08, 23.846328711070697)(0.085, 22.90933467404057)(0.09, 22.152617503755)(0.095, 21.356421356421354)(0.1, 20.641965664778876)(0.105, 19.924470242674317)(0.11, 19.246298788694478)(0.115, 18.532910658894913)(0.12, 17.784217265314382)(0.125, 17.0)(0.13, 16.44693473961766)(0.135, 15.58770225480432)(0.14, 14.952787478980731)(0.145, 14.591315453384416)(0.15, 14.068681753441997)(0.155, 13.438921122785)(0.16, 12.576495566379412)(0.165, 12.1045477014335)(0.17, 11.67240719479524)(0.175, 10.71428571428572)(0.18, 10.216812015503878)(0.185, 9.878838771593088)(0.19, 8.965888367365245)(0.195, 8.532969639468684)(0.2, 7.883082373782105)(0.205, 7.0957119967072035)(0.21, 6.501031561388886)(0.215, 5.830903790087479)(0.22, 4.503241633082184)(0.225, 3.994190268700073)(0.23, 3.258508327299059)(0.235, 3.7089871611982885)(0.24, 9.308510638297872)(0.245, 38.92587660896582)
			}node[pos=1.0](endofplotsquare){} ;
		%\node [above] at (endofplotsquare) {$n=200$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 48.82985928211302)(0.01, 40.20061728395061)(0.015, 35.8974358974359)(0.02, 32.10526315789474)(0.025, 29.89508775370134)(0.03, 27.697441601779754)(0.035, 26.26728110599078)(0.04, 24.66329966329966)(0.045, 23.238526179702653)(0.05, 22.453433091730965)(0.055, 21.28060263653484)(0.06, 20.47278564132497)(0.065, 19.744318181818187)(0.07, 18.640077551585644)(0.075, 17.621533663299214)(0.08, 17.415433403805487)(0.085, 16.612798965740136)(0.09, 16.096757852076994)(0.095, 15.320195510725066)(0.1, 15.115005476451262)(0.105, 14.304548450889918)(0.11, 13.963287073867834)(0.115, 13.283062645011604)(0.12, 12.956621004566218)(0.125, 12.517580872011253)(0.13, 12.032412032412036)(0.135, 11.314900744076228)(0.14, 10.927008880225257)(0.145, 10.857264866019005)(0.15, 10.408432147562582)(0.155, 10.170285892829247)(0.16, 9.61994026161294)(0.165, 9.276248725790005)(0.17, 8.879802110151953)(0.175, 8.181135851888914)(0.18, 7.840951319212183)(0.185, 7.4437788470980895)(0.19, 7.141815353201405)(0.195, 6.774544137181502)(0.2, 6.153993855606756)(0.205, 5.965045592705168)(0.21, 5.580409700965385)(0.215, 4.929577464788732)(0.22, 4.562383612662934)(0.225, 3.944315545243619)(0.23, 2.784222737819025)(0.235, 2.7586206896551726)(0.24, 2.059496567505721)(0.245, 4.0)
			}node[pos=1.0](endofplotsquare){} ;
		%\node [above] at (endofplotsquare) {$n=500$};
		\addplot[] coordinates {
		(0.0, 100.0)(0.005, 42.16746291174252)(0.01, 33.35416015828387)(0.015, 29.34782608695652)(0.02, 26.232905097389136)(0.025, 23.465482932802693)(0.03, 22.176210195630443)(0.035, 20.876445526475944)(0.04, 19.515807095486448)(0.045, 18.938835666912308)(0.05, 17.877821103627564)(0.055, 16.87069407276661)(0.06, 16.3916391639164)(0.065, 15.064102564102571)(0.07, 14.902449149024491)(0.075, 14.14141414141414)(0.08, 13.669774554782698)(0.085, 12.951474053768097)(0.09, 12.437623575934465)(0.095, 11.8800461361015)(0.1, 11.280101394169831)(0.105, 10.638865424798817)(0.11, 10.834674437823494)(0.115, 10.141206675224653)(0.12, 9.932659932659941)(0.125, 9.76821192052981)(0.13, 9.201954397394145)(0.135, 8.78038979304803)(0.14, 8.623417721518992)(0.145, 8.424908424908427)(0.15, 8.168754322600472)(0.155, 7.856817837099964)(0.16, 7.490636704119851)(0.165, 7.441688263606079)(0.17, 7.214611872146119)(0.175, 6.684027777777785)(0.18, 6.699077715021094)(0.185, 6.061680255228631)(0.19, 5.955012808365783)(0.195, 5.437352245862879)(0.2, 5.426783135016155)(0.205, 4.826880436636545)(0.21, 4.832613390928723)(0.215, 4.233870967741943)(0.22, 3.8909211839042195)(0.225, 3.712985556947849)(0.23, 3.1198686371100166)(0.235, 2.134646962233169)(0.24, 1.1494252873563218)(0.245, 1.6181229773462782)
			}node[pos=0.85](endofplotsquare){} ;
		\node [below left] at (endofplotsquare) {$n=1000$};
		\end{axis}
		\end{tikzpicture}
		\caption{The percent reduction in the 0.5 probability bound, that going from our EBB to Hoeffding's inequality (representing perfect knowledge of the variance, $\hat{\sigma}^2=\sigma^2$) achieves, for various n=10,25,50,100,200,500,1000.}
		\label{biggraph4}
    \end{subfigure}
\end{figure}

\section{Discussion}\label{discussion}
We also fitted some rough envelopes over our calculated numerics for $25\le n\le 1000$:
$$\scriptstyle \p\left(\sigma^2 - \hat{\sigma}^2>\frac{D^2}{\sqrt{n}}\left(0.09+0.3\log(1/w)+\frac{25w}{D^6}(\sigma^2)^2(D^2-4\sigma^2)+\frac{3}{2n}\right)\right) \le w$$
And
$$\scriptstyle \p\left(\mu - \hat{\mu}^2>\frac{D}{20\sqrt{n}}\left(16 - 10y + \frac{20D^2}{nD^2-4n\hat{\sigma}^2} + \left(y- \exp\left(-\frac{n^2}{16D^4}(1-4\hat{\sigma}^2)^2\right)\right)^{-1}\right)\right) \le y$$
\hfill When $\scriptstyle y-exp\left(-\frac{n^2}{16D^4}(1-4\hat{\sigma}^2)^2\right)>\frac{3}{20}$\\

Over our computed datapoints these envelopes were witnessed to always widen the probability bounds with a median width increase of $0.03367D^2$ across $7569$ datapoints and $0.0105D$ across $36918$ datapoints respectively.
These envelopes are supplied only as a loose approximation over the results of this paper and the reader is encouraged to explore the technique and source code\footnote{at: \href{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}} if tighter or more accurate expressions are required.

\subsection{A Bayesian Caution}
The derivation of EBBs and similar bounds begin with population parameters (variance, mean, etc) and analytically bound the sample statistics relative to them (sample mean, sample variance, etc).
These bounds are thus implicitly statements of probability between sample statistics and population parameters, that are conditioned on those parameters.
However these can potentially be quite different from the same probability statements conditioned on the sample statistics.

I.e, if we know population parameters such as mean and variance we can analytically deduce probability bounds on sample mean and sample variance, however the converse process is potentially very different.

In various applications EBBs (and other similar bounds) have been used with sample statistics to give bounds on the population parameters. However it pays to note that this kind of use potentially goes beyond what can strictly be known by analysis.

\appendix

\section{Parabola Fitting}\label{appendix1}
For the task\footnote{Here we carry the derivation with the $x$-axis scaling factor $s$ removed for simplicity} of selecting an $\alpha,\beta,\gamma$ as the parameters of a parabola $\alpha x^2+\beta x+\gamma\ge \exp(x)$ for all $c\le x\le d$ which minimizes $z\alpha+\gamma$ for constants $c,d,z$.
We witness that any such parabola much tangentially touch the exponential curve at one point (at $x=f<d$) and intersect it at another (at $x=d$), as illustrated in the following figure \ref{fig:graph1}:
\begin{figure}[h]
\begin{tikzpicture}
\draw[->] (-3.5,0) -- (2,0) node[anchor=north] {$x$};
\draw[->] (0,0) -- (0,4) node[anchor=east] {};
\draw[smooth, domain=-3.5:2.0, color=black, line width=0.20mm] 
    plot (\x,{e^(\x)/2}) node [right] {\footnotesize $e^x$};
\draw[smooth, domain=-3.5:2.0, color=red, line width=0.20mm] 
    plot (\x,{(0.316137167001903*\x*\x + 1.39988395124422*\x + 1.67055451771745)/2}) node [right] {\footnotesize $\alpha x^2+\beta x+\gamma$};
\draw (1.5,-0.1) -- (1.5,{e^(1.5)/2});
\draw (-2,-0.1) -- (-2,{e^(-2)/2});
\draw (-2.5,-0.1) -- (-2.5,0);
\draw[black,fill] (1.5,{e^(1.5)/2}) circle (0.25mm);
\draw[black,fill] (-2,{e^(-2)/2}) circle (0.25mm);
\draw	(-2.5,-0.25) node{{\scriptsize $c$}}
		(-2,-0.25) node{{\scriptsize $f$}}
		(1.5,-0.25) node{{\scriptsize $d$}};
\end{tikzpicture}
\caption{\footnotesize Fitting a parabola above an exponential curve for all $c\le x\le d$}
\label{fig:graph1}
\end{figure}
The parabola's intersection at $x=d$ and its tangential intersection at $x=f$ can be written in matrix algebra:
$$
\begin{bmatrix}
    \alpha \\
    \beta \\
	\gamma
\end{bmatrix}
=
\begin{bmatrix}
    d^2 & d & 1 \\
    f^2 & f & 1 \\
	2f  & 1 & 0
\end{bmatrix}^{-1}
\begin{bmatrix}
    \exp(d) \\
    \exp(f) \\
	\exp(f)
\end{bmatrix}$$
which gives our parabola parameters $\alpha,\beta,\gamma$ in terms of $f$ and $d$, hence our objective function $z\alpha+\gamma$ can be written as:
$$z\alpha+\gamma = \frac{((z+fd-d)(f-d-1)-d)e^f+(f^2+z)e^d}{(d-f)^2}$$
since $d$ is fixed, minimizing with respect to $f$ gives $f=\frac{-z}{d}$ where our objective function becomes:
$$z\alpha+\gamma = \frac{ze^d + d^2e^{-z/d}}{z + d^2}$$
Which is sufficient for our purposes.

\section{Computational Process}\label{appendix2}
In this section we detail more closely the numerical approach we used to calculate our EBB.
We begin with the method used to numerically solve the function $ H_2^n(a,b,y,\sigma^2) $ per lemma \ref{sample_squares}.

\subsection{Computing $H_2^n(a,b,y,\sigma^2)$}
The function is a result of an optimization problem solving for the minima of an objective function subject to constraints: $$s>0,~\alpha,\beta,\gamma\quad  \text{s.t}~\alpha x^2 + \beta x + \gamma\ge\exp(-sx^2)\quad \forall x\in[a,b]$$
with $a<0<b$. Particularly this is over the family of parabolas fitting above an exponential $\exp(-sx^2)$ in the required range. Without loss of generality we consider $b>-a$ and also restrict the range of parabolas to thoes intersecting at $x=b$ and tangentially intersecting at another point $x=x_0$ as graphed in figure \ref{fig:graph2}. We note that the parabola characterized by $x_0=0$ is always valid, and that there exists a minimum value of $x_0$ such that all the parabolas $x_\text{min}\le x_0\le 0$ are all valid.
Analytically solving for $x_\text{min}$ is difficult, but it is simple enough that we can numerically determine it very quickly and accurately.

Then we take $n_1$ evenly spaced points of $x_0$ in the range $x_\text{min}\le x_0\le 0$, and $n_2$ evenly spaced points of $s$ in the range $0<s\le s_\text{max}$ and evaluate and take the minimum of the objective function for all combinations of these points. Note that any lack of resolution for these divisions (and/or unnecessary constriction in our choice of parabolas) would only serve to increase the computed value of $H_2^n(a,b,y,\sigma^2)$ which does not hamper the analytical accuracy of their use as an upper bound.

\begin{figure}
\begin{tikzpicture}[scale=1.9]
\draw[->] (-1.5,0) -- (2,0) node[anchor=north] {$x$};
\draw[->] (0,0) -- (0,1.5) node[anchor=east] {};
\draw[smooth, domain=-1.5:2.0, color=black, line width=0.20mm] 
    plot (\x,{e^(-\x*\x)}) node [above] {\footnotesize $e^{-x^2}$};
\draw (1.5,-0.1) -- (1.5,{e^(-1.5*1.5)});
\draw (-1,-0.1) -- (-1,{e^(-1*1)});

\draw[densely dotted] (-0.150534231,-0.1) -- (-0.150534231,{e^(-0.150534231*0.150534231)});
\draw[black,fill] (-0.150534231,{e^(-0.150534231*0.150534231)}) circle (0.15mm);
\draw[smooth, domain=-1.5:2.0, color=red, line width=0.10mm] 
    plot (\x,{(-0.49847785609681*\x*\x + 0.144246841020498*\x + 1.01060413924894)}) node [right] {\footnotesize intercepts at $a$ and $b$};

\draw[densely dotted] (0.1,-0.1) -- (0.1,{e^(-0.1*0.1)});
\draw[black,fill] (0.1,{e^(-0.1*0.1)}) circle (0.15mm);
\draw[smooth, domain=-1.5:2.0, color=blue, line width=0.10mm] 
    plot (\x,{(-0.30991666109058*\x*\x + -0.136026634531718*\x + 1.00675166381325)}) node [right] {\footnotesize intercepts at $b$};

\draw[densely dotted] (-0.150534231,-0.1) -- (0.1,-0.1);
\draw	(-0.1,-0.25) node{{\scriptsize $x_0$}}
		(-1,-0.25) node{{\scriptsize $a$}}
		(1.5,-0.25) node{{\scriptsize $b$}};
\end{tikzpicture}
\caption{\footnotesize parabolas above $\exp(-x^2)$ for all $a\le x\le b$, intercepting at $x=b$ and parametrized by a $x_0$ tangential intercept}
\label{fig:graph2}
\end{figure}

\subsection{Computing $H_3^n(a,b,w,\sigma^2)$}
The function is a result of an optimization problem solving for the minima of an objective function subject to constraint $\phi\in[0,1]$.
Straightforwardly this can be solved numerically by taking $n_3$ evenly spaced points of $\phi$ in the range $0\le\phi\le 1$ and taking the minimum of the objective function evaluated at each point.
Yet again, any lack of resolution for these divisions would only serve to increase the computed value of $H_3^n(a,b,w,\sigma^2)$ which does not hamper the analytical accuracy of its use as an upper bound. In this way the computed values of the variance bound of theorem \ref{variance2} should be analytically appropriate.

\subsection{Computing the EBB}
The next step in computing our EBB consisted in verifying assumptions and applying theorem \ref{ebb1}.
In the theorem \ref{ebb1} two interesting function inversions are necessary: $h^{-2}$ and $f^{-2}$.

The first is the inversion of Hoeffding's inequality on the second argument. Since Hoeffding's function is a closed form mathematical function and monotonically decreasing from $1$ to $0$ on the second argument, evaluating the inverse function at a point can be done quickly and accurately, furthermore the requirement that $h^{-2}$ be monotonically increasing in its first argument was not only witnessed numerically but also is intuitively recognized as being true of the function (that the increasing the variance would necessarily lead to widening probability bounds).

The second is the inversion of our computed function $H_3^n(a,b,w,\sigma^2)$ on its third argument - which is more difficult.
Generally, for any function, the values that the function takes can be plotted as points and the values that the inverse of that function takes can be determined by conducting coordinate swapping on those points. And so we evaluated $H_3^n(a,b,w,\sigma^2)$ across a range of input values and calculated $z^{-1}$ by coordinate swapping on those points. In this way $z^{-1}$ was witnessed to be a regular function monotonically increasing on its first argument.

After calculating datapoints for $z^{-1}$ we then made those datapoints regularly spaced by linear interpolation - at this point which it should be noted that specific analytical guarantees are lost as the process of interpolation can give datapoints that can be either below or above the underlying function.
In doing this interpolation we were thence able to appropriately compose the function as required by the theorem \ref{ebb1} as $h^{-2}(z^{-1}(\hat{\sigma}^2,y-x),x)$.
We did linear interpolation of $n_4$ data points evenly between $0$ and $1$ on the second argument.

We then took the maximum value of this bound for $a$ and $b$ consistent with a given $D=b-a$ and $\sigma^2$ specifically:
$$\max_{b\in\left[\frac{D}{2},\frac{D}{2}-\sqrt{\frac{D^2}{4}-\sigma^2}\right]} h^{-2}(z^{-1}(\hat{\sigma}^2,y-x),x)$$
We did this by taking $n_5$ evenly spaced values of $b$ in $\left[D/2,D\right]$ and considered those that satisfied $b<\frac{D}{2}-\sqrt{\frac{D^2}{4}-\sigma^2}$.
Then taking minimum $x$:
$$\min_{x\in[0,y]}\max_{b\in\left[\frac{D}{2},\frac{D}{2}-\sqrt{\frac{D^2}{4}-\sigma^2}\right]} h^{-2}(z^{-1}(\hat{\sigma}^2,y-x),x)$$
And in this context the values that have been computed for $x$ are implicitly constrained by the resolution of the interpolation $n_4$.

\subsection{Summary of Computation}
In this way we have detailed the components of the methodology used to evaluate our new EBB.
It is hoped that all of the components should be relatively transparent and simple numerical steps, and that the result of the method should be tunable without systematic bias to increasingly greater accuracy (at the cost of compute time) with parameters: $n_1,n_2,n_3,n_4,n_5$ and $s_\text{max}$.

For further information, the reader is encouraged to download, inspect and experiment with the sourcecode, available at:\\\href{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}\\
The sourcecode consists of a small\footnote{$\sim 150$ lines of C code, and $\sim 250$ lines of Python code} documented package of C and Python code, that was used (and is setup) to compute the results of the paper.

\newpage
\bibliographystyle{imsart-number}
\bibliography{bib}

\end{document}

### 2018-08-15 EBB_envelope.py

@@ -1,4 +1,5 @@
 import json
+from math import exp, sqrt
 from utils import *
 import sys
 
@@ -21,12 +22,11 @@ for ii in range(lenargv):
 	for a,b,c in data:
 		if b-exp(-((0.25-a)*n)**2)>0.15:
 			# calculate the height of the envelope above the data
-			v = (0.75 - 0.5*b + 0.25/((0.25-a)*n) + 0.05/(b-exp(-((0.25-a)*n)**2)))/sqrt(n)-c
+			v = (0.80 - 0.5*b + 0.25/((0.25-a)*n) + 0.05/(b-exp(-((0.25-a)*n)**2)))/sqrt(n)-c
 			# raise exception if the envelope below the data
 			if v<0:
 				raise Exception("envelope below the data!")
 			datapoints.append(v)
 
 # calculate the median height of the envelope above the data, and the number of datapoints
-from statistics import median
 print "EBB envelope: {} above data, datapoints: {}".format(median(datapoints),len(datapoints))

### 2018-08-15 compile.sh

@@ -8,7 +8,6 @@ g++ -o sim sim.c
 ./sim 300 50 50
 ./sim 500 50 50
 ./sim 1000 50 50
-./sim 2000 50 50
 python gen.py data25_50_50.json
 python gen.py data50_50_50.json
 python gen.py data75_50_50.json
@@ -18,6 +17,5 @@ python gen.py data200_50_50.json
 python gen.py data300_50_50.json
 python gen.py data500_50_50.json
 python gen.py data1000_50_50.json
-python gen.py data2000_50_50.json
-python variance_envelope.py data10_50_50.json data25_50_50.json data50_50_50.json data75_50_50.json data100_50_50.json data150_50_50.json data200_50_50.json data300_50_50.json data500_50_50.json data1000_50_50.json data2000_50_50.json
+python variance_envelope.py data25_50_50.json data50_50_50.json data75_50_50.json data100_50_50.json data150_50_50.json data200_50_50.json data300_50_50.json data500_50_50.json data1000_50_50.json
 python EBB_envelope.py formatted_data25_50_50.json 25 formatted_data50_50_50.json 50 formatted_data75_50_50.json 75 formatted_data100_50_50.json 100 formatted_data150_50_50.json 150 formatted_data200_50_50.json 200 formatted_data300_50_50.json 300 formatted_data500_50_50.json 500 formatted_data1000_50_50.json 1000

### 2018-08-15 sim.c

@@ -11,8 +11,8 @@ int ddims;
 //========== SIMULATION PARAMETERS:
 double D=1.0;
 double phi_iterator=0.009999;
-double q_max= 6.0;
-double q_iterator=0.01;
+double q_max= 1.0;
+double q_iterator=0.001;
 double x0_iterator=0.1;
 
 //========== CORE PROCEDURES

### 2018-08-15 utils.py

@@ -8,6 +8,11 @@ try:
 except ImportError:
 	tqdm_enabled=False
 
+# a cheap function to compute the median of a list of data
+def median(data):
+	data = sorted(data)
+	return data[len(data)/2]
+
 # convert a list of points into nested set of dictionaries in order of indices
 def categorize(data,indices):
 	if len(indices)==1:

### 2018-08-15 variance_envelope.py

@@ -1,5 +1,6 @@
 import json
 from utils import *
+from math import sqrt
 import sys
 
 print "*computing deviation of variance bound from envelope*"
@@ -23,7 +24,7 @@ for ii in range(lenargv):
 
 	# take the maximum with d
 	print "maximizing"
-	for a in tqdm(data.keys()):
+	for a in data.keys():
 		for b in data[a].keys():
 			data[a][b] = max(data[a][b].values())
 	# reformulate the data from being a nested dictionaries of values to a list of points
@@ -38,10 +39,9 @@ for ii in range(lenargv):
 
 	# raise exception if the envelope below the data
 	for d in data:
-		if d[-1]<0:
+		if d<0:
 			raise Exception("envelope below the data!")
 		datapoints.append(d[-1])
 
 # calculate the median height of the envelope above the data, and the number of datapoints
-from statistics import median
 print "variance envelope: {} above data, datapoints: {}".format(median(datapoints),len(datapoints))

### 2018-08-15 plot.py
removing files

@@ -1,24 +1,0 @@
-import json
-from utils import *
-import sys
-import random
-
-fig = plt.figure()
-ax = fig.gca(projection='3d')
-
-lenargv = len(sys.argv)-1
-for ii in range(lenargv):
-	filename = sys.argv[ii+1]
-	print "loading data {}".format(filename)
-	data = []
-	with open("{}".format(filename), "r") as f:
-		data = json.load(f)
-	x = [a[0] for a in data]
-	y = [a[1] for a in data]
-	z = [a[2] for a in data]
-	ax.scatter(x, y, z,s=2.7, c=['b', 'g', 'r', 'c', 'm', 'y', 'k'][ii])
-
-ax.set_xlabel("$\hat{\sigma}^2$")
-ax.set_ylabel("y")
-plt.show()
-

### 2018-08-17 EBB_envelope.py
update with graph

@@ -6,6 +6,14 @@ import sys
 print "*computing deviation of EBB bound from envelope*"
 datapoints = []
 
+# define the envelope
+def envelope(a,b,n):
+	return (1.0/(b-exp(-0.1*(n/4.0-n*a)**2))+100/((n/4.0-n*a)**3)-12*b+13+20*a+8000/(n**2))/(20*sqrt(n))
+
+# define envelope bound:
+def bound(a,b,n):
+	return b-exp(-0.1*((0.25-a)*n)**2)>0.05
+
 # for each of the data files inputted
 lenargv = (len(sys.argv)-1)/2
 for ii in range(lenargv):
@@ -20,9 +28,9 @@ for ii in range(lenargv):
 
 	# for each of the data values in range
 	for a,b,c in data:
-		if b-exp(-((0.25-a)*n)**2)>0.15:
+		if bound(a,b,n):
 			# calculate the height of the envelope above the data
-			v = (0.80 - 0.5*b + 0.25/((0.25-a)*n) + 0.05/(b-exp(-((0.25-a)*n)**2)))/sqrt(n)-c
+			v = envelope(a,b,n)-c
 			# raise exception if the envelope below the data
 			if v<0:
 				raise Exception("envelope below the data!")

### 2018-08-17 compile.sh

@@ -17,5 +17,6 @@ python gen.py data200_50_50.json
 python gen.py data300_50_50.json
 python gen.py data500_50_50.json
 python gen.py data1000_50_50.json
-python variance_envelope.py data25_50_50.json data50_50_50.json data75_50_50.json data100_50_50.json data150_50_50.json data200_50_50.json data300_50_50.json data500_50_50.json data1000_50_50.json
-python EBB_envelope.py formatted_data25_50_50.json 25 formatted_data50_50_50.json 50 formatted_data75_50_50.json 75 formatted_data100_50_50.json 100 formatted_data150_50_50.json 150 formatted_data200_50_50.json 200 formatted_data300_50_50.json 300 formatted_data500_50_50.json 500 formatted_data1000_50_50.json 1000
+python variance_envelope.py data50_50_50.json data75_50_50.json data100_50_50.json data150_50_50.json data200_50_50.json data300_50_50.json data500_50_50.json data1000_50_50.json
+python EBB_envelope.py formatted_data50_50_50.json 50 formatted_data75_50_50.json 75 formatted_data100_50_50.json 100 formatted_data150_50_50.json 150 formatted_data200_50_50.json 200 formatted_data300_50_50.json 300 formatted_data500_50_50.json 500 formatted_data1000_50_50.json 1000
+python graph.py

### 2018-08-17 graph.py

@@ -1,0 +1,44 @@
+
+import json
+from utils import *
+
+filename = "data200_50_50"
+n=200
+D=1.0
+
+print "loading data"
+with open("{}.json".format(filename), "r") as f:
+	import_data = json.load(f)
+
+data = import_data['data']
+results = [list(eval(a))+[b] for a,b in data.iteritems()]
+print "trimming data"
+results = [(a,b,c,d) for a,b,c,d in results if a<=D*c*(1-c)]
+print "recategorzing data"
+results = categorize(results,[0,1,2,3])
+print "maximizing"
+for a in results.keys():
+	for b in results[a].keys():
+		results[a][b] = max(results[a][b].values())
+
+print "generating graph"
+K1 = sorted(results.keys())
+s = ""
+
+
+for i,k1 in enumerate(K1[:-1]):
+	K2 = sorted(results[K1[i+1]].keys())
+	for o,k2 in enumerate(K2[:-1]):
+		if o>0:
+			s += "{} {} {}\n".format(K1[i],K2[o],		entropy(K1[i],K2[o],D,n) - results[K1[i]][K2[o]])
+			s += "{} {} {}\n".format(K1[i+1],K2[o],		entropy(K1[i+1],K2[o],D,n) - results[K1[i+1]][K2[o]])
+			s += "{} {} {}\n".format(K1[i],K2[o-1],		entropy(K1[i],K2[o-1],D,n) - results[K1[i]][K2[o-1]])
+		s += "\n"
+		s += "{} {} {}\n".format(K1[i],K2[o],		entropy(K1[i],K2[o],D,n) - results[K1[i]][K2[o]])
+		s += "{} {} {}\n".format(K1[i+1],K2[o],		entropy(K1[i+1],K2[o],D,n) - results[K1[i+1]][K2[o]])
+		s += "{} {} {}\n".format(K1[i+1],K2[o+1],	entropy(K1[i+1],K2[o+1],D,n) - results[K1[i+1]][K2[o+1]])
+with open("{}_graph.dat".format(filename),"w") as f:
+	f.write(s)
+
+
+print "done :-)"

### 2018-08-17 variance_envelope.py

@@ -6,6 +6,10 @@ import sys
 print "*computing deviation of variance bound from envelope*"
 datapoints = []
 
+# define the envelope
+def envelope(a,b,n):
+	return (0.12+0.3*log(1.0/b)+25*b*a*a*(1-4*a)+1.5/n)/sqrt(n)
+
 # for each of the data files inputted
 lenargv = len(sys.argv)-1
 for ii in range(lenargv):
@@ -30,18 +34,24 @@ for ii in range(lenargv):
 	# reformulate the data from being a nested dictionaries of values to a list of points
 	print "decategorzing data"
 	data = decategorize(data)
+	
+	# invert function on the second argument
+	print "inverting data"
+	data = [(a,c,b) for a,b,c in data]
 
 	# trim of the redundant upper bound 1 values
+	print "trimming redundant 1s"
 	data = [d for d in data if d[-1]<1.0]
 	
 	# calculate the height of the envelope above the data
-	data = [((0.09+0.3*log(1.0/b)+25*b*a*a*(1-4*a)+1.5/n)/sqrt(n)-c) for a,b,c in data if b!=0 and c!=0]
+	print "calculating"
+	data = [envelope(a,b,n)-c for a,b,c in data if b>0]
 
 	# raise exception if the envelope below the data
 	for d in data:
 		if d<0:
 			raise Exception("envelope below the data!")
-		datapoints.append(d[-1])
+		datapoints.append(d)
 
 # calculate the median height of the envelope above the data, and the number of datapoints
 print "variance envelope: {} above data, datapoints: {}".format(median(datapoints),len(datapoints))

### 2018-08-17 graph2.py
added graph generator

@@ -1,0 +1,44 @@
+import json
+from utils import *
+import sys
+from math import sqrt,log
+
+# Maurer and Pontil's EBB
+def entropy2(s,w,n):
+	if w>2:
+		w=2
+	if w<=0:
+		return float("inf")
+	return sqrt(2*s*log(2/w)/n) + 7*log(2/w)/(3*(n-1))
+
+# Hoeffdings, inverted on first argument
+h = invert(hoeffding_1,argument=1)
+
+# open files holding data for latex 2d plots
+f1 = open("graph_1.tex","w")
+f2 = open("graph_2.tex","w")
+
+#shorthand for calculating percent loss from y to x
+l = lambda x,y:(y-x)*100.0/y
+
+# read arguments and load data
+lenargv = (len(sys.argv)-1)/2
+for ii in range(lenargv):
+	filename = sys.argv[ii*2+1]
+	n = int(sys.argv[ii*2+2])
+	print "loading data {}".format(filename)
+	data = []
+	with open("{}".format(filename), "r") as f:
+		data = json.load(f)
+	# write datums
+	f1.write("\n{}:\n".format(n))
+	f2.write("\n{}:\n".format(n))
+	f1.write("".join([str((d[0],l(d[2],entropy2(d[0],0.5,n)))) for d in data if (d[1]==0.5) and (0.5>sqrt(d[0])+sqrt(2*log(2.0/0.5)/(n-1)))])+'\n')
+	f2.write("".join([str((d[0],l(h(d[0],0.5,n),d[2]))) for d in data if d[1]==0.5])+'\n')
+
+print "done"
+#close files
+f1.close()
+f2.close()
+
+

### 2018-08-17 utils.py

@@ -197,7 +197,7 @@ def protected_div(a,b):
 	else:
 		return 1
 
-# Maurer and Pontil's entropy bound
+# Maurer and Pontil's entropy variance bound
 def entropy(s,t,d,n):
 	if s>d/4.0 or s<0:
 		raise Exception

### 2018-08-17 compile.sh
updated compile script

@@ -1,5 +1,4 @@
 g++ -o sim sim.c
-./sim 25 50 50
 ./sim 50 50 50
 ./sim 75 50 50
 ./sim 100 50 50
@@ -8,7 +7,6 @@ g++ -o sim sim.c
 ./sim 300 50 50
 ./sim 500 50 50
 ./sim 1000 50 50
-python gen.py data25_50_50.json
 python gen.py data50_50_50.json
 python gen.py data75_50_50.json
 python gen.py data100_50_50.json
@@ -20,3 +18,4 @@ python gen.py data1000_50_50.json
 python variance_envelope.py data50_50_50.json data75_50_50.json data100_50_50.json data150_50_50.json data200_50_50.json data300_50_50.json data500_50_50.json data1000_50_50.json
 python EBB_envelope.py formatted_data50_50_50.json 50 formatted_data75_50_50.json 75 formatted_data100_50_50.json 100 formatted_data150_50_50.json 150 formatted_data200_50_50.json 200 formatted_data300_50_50.json 300 formatted_data500_50_50.json 500 formatted_data1000_50_50.json 1000
 python graph.py
+python graph2.py formatted_data50_50_50.json 50 formatted_data75_50_50.json 75 formatted_data100_50_50.json 100 formatted_data150_50_50.json 150 formatted_data200_50_50.json 200 formatted_data300_50_50.json 300 formatted_data500_50_50.json 500 formatted_data1000_50_50.json 1000

### 2018-08-17 paper/main.tex
updated paper

@@
 		\addplot[] coordinates {
-		(0.005, 31.33262397944378)(0.01, 34.72886250674945)(0.015, 36.909296945183726)(0.02, 38.627583846687266)(0.025, 39.59462124039761)
+(0.0, 5.68279906803574)(0.005, 21.836118930505265)(0.01, 25.802823484071254)(0.015, 28.022512115598744)(0.02, 29.864039382966602)(0.025, 31.111321132916768)(0.03, 32.0919738463798)(0.035, 33.05847784139354)(0.04, 33.736278995225796)(0.045, 34.440280964621486)(0.05, 35.15592306441015)(0.055, 35.64597513743734)(0.06, 36.16219390744528)(0.065, 36.685357809102705)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=25$};
+		\node [above] at (endofplotsquare) {$\scriptstyle n=50$};
 		\addplot[] coordinates {
-		(0.005, 28.333532153239666)(0.01, 31.153830409409)(0.015, 32.87549096079947)(0.02, 33.81992265562242)(0.025, 34.89945361309619)(0.03, 35.74891595008532)(0.035, 36.60739883058407)(0.04, 37.276099921865196)(0.045, 37.59026746494855)(0.05, 38.218754538940686)(0.055, 38.83065159779602)(0.06, 39.39861647873854)(0.065, 39.910212250065214)
+(0.0, 5.854298988166525)(0.005, 23.964254032213393)(0.01, 27.37245164317984)(0.015, 29.355131457208117)(0.02, 30.91363823414449)(0.025, 31.790584639065834)(0.03, 32.66128510303768)(0.035, 33.26400387886201)(0.04, 33.92107357684253)(0.045, 34.471764641790685)(0.05, 34.8305410962864)(0.055, 35.36497453138069)(0.06, 35.79802010253675)(0.065, 36.02369268944928)(0.07, 36.377072129280634)(0.075, 36.79581728264095)(0.08, 37.15435342833946)(0.085, 37.50755150324622)(0.09, 37.848233168432564)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=50$};
+		\node [above] at (endofplotsquare) {$\scriptstyle n=75$};
 		\addplot[] coordinates {
-		(0.005, 30.038701393161688)(0.01, 31.412520149627277)(0.015, 32.49171315420119)(0.02, 32.876510879893)(0.025, 33.61899806422779)(0.03, 34.07734163182933)(0.035, 34.27418933046886)(0.04, 34.76092837396386)(0.045, 35.00082505166452)(0.05, 35.60742157468709)(0.055, 36.00845546401498)(0.06, 36.09363022383078)(0.065, 36.49561598871189)(0.07, 36.871363860949025)(0.075, 36.995564126738095)(0.08, 37.25705721710657)(0.085, 37.63281018078307)(0.09, 37.94537201050319)(0.095, 38.313563615135976)(0.1, 38.57428091364722)(0.105, 38.898129385115695)(0.11, 38.919035439297076)
+(0.0, 6.832182513392391)(0.005, 25.52090535766474)(0.01, 28.650608209343815)(0.015, 30.50309695254201)(0.02, 31.50863773916302)(0.025, 32.33004657032931)(0.03, 33.029564280282244)(0.035, 33.44221704351276)(0.04, 33.965329939500016)(0.045, 34.30605952371319)(0.05, 34.692416934952185)(0.055, 35.160885337710546)(0.06, 35.45220688581006)(0.065, 35.903347122285375)(0.07, 36.23498648051504)(0.075, 36.37175783096322)(0.08, 36.65259726736771)(0.085, 36.988036601825)(0.09, 37.26282798128783)(0.095, 37.544772095379265)(0.1, 37.60863642146002)(0.105, 37.904706139336135)(0.11, 38.1586914821099)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=100$};
+		\node [above right] at (endofplotsquare) {$\scriptstyle n=100$};
 		\addplot[] coordinates {
-		(0.005, 31.585709637284875)(0.01, 32.14640200496432)(0.015, 32.480242185958275)(0.02, 32.72477439020389)(0.025, 32.85137640603805)(0.03, 33.164192395805884)(0.035, 33.41972794004208)(0.04, 33.34159833965975)(0.045, 33.824240924074424)(0.05, 33.77957868846732)(0.055, 34.028900979162536)(0.06, 34.23479104354531)(0.065, 34.320408892537166)(0.07, 34.556516165135605)(0.075, 34.775904883097695)(0.08, 34.98535349546355)(0.085, 35.19862669231675)(0.09, 35.3945988354474)(0.095, 35.601977507693036)(0.1, 35.72487858163208)(0.105, 35.83625307070917)(0.11, 36.04135799347741)(0.115, 36.25828614993272)(0.12, 36.48817284893286)(0.125, 36.73194354036559)(0.13, 36.91341720219515)(0.135, 37.18914713784862)(0.14, 37.407683615789495)(0.145, 37.415360037546876)
+(0.0, 7.693682332229607)(0.005, 27.990066618755765)(0.01, 30.446803018183655)(0.015, 31.488910428759073)(0.02, 32.375218883686195)(0.025, 32.767178192308855)(0.03, 33.24333663177549)(0.035, 33.51602854693247)(0.04, 33.87791050108074)(0.045, 34.016628689572016)(0.05, 34.273764717129254)(0.055, 34.575402898651696)(0.06, 34.927925485299724)(0.065, 35.1528833291239)(0.07, 35.44618521289669)(0.075, 35.63701544350516)(0.08, 35.90448901985416)(0.085, 36.16597179371182)(0.09, 36.167776741773636)(0.095, 36.40559868439304)(0.1, 36.64827000607862)(0.105, 36.82647424171691)(0.11, 37.02387109415649)(0.115, 37.08745263644369)(0.12, 37.31109551975997)(0.125, 37.486455368251484)(0.13, 37.69786237630875)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=200$};
+		\node [above right] at (endofplotsquare) {$\scriptstyle n=150$};
 		\addplot[] coordinates {
-		(0.005, 30.95805680601551)(0.01, 31.852731472234087)(0.015, 31.65165353001502)(0.02, 31.838019953330228)(0.025, 31.80514856457896)(0.03, 32.049553438239556)(0.035, 31.874671808872318)(0.04, 32.15628114167258)(0.045, 32.18970870320976)(0.05, 32.29347571578702)(0.055, 32.328022832020885)(0.06, 32.32551565971646)(0.065, 32.51203709690735)(0.07, 32.671571263469616)(0.075, 33.00950294213178)(0.08, 32.921019505844626)(0.085, 33.017153308081845)(0.09, 33.11615572233624)(0.095, 33.393651317961485)(0.1, 33.19788472106813)(0.105, 33.458020247263455)(0.11, 33.5638596989855)(0.115, 33.685389159897156)(0.12, 33.74232351659747)(0.125, 33.86778330552732)(0.13, 34.01232127428546)(0.135, 34.31523066744031)(0.14, 34.360222768291344)(0.145, 34.35739937066466)(0.15, 34.42537992870109)(0.155, 34.52118296490931)(0.16, 34.64446824473269)(0.165, 34.79488974531291)(0.17, 34.972098710274665)(0.175, 35.1757460413815)(0.18, 35.294877117787664)
+(0.0, 8.943146707982761)(0.005, 29.201936453915007)(0.01, 31.11204837699122)(0.015, 31.91913616534297)(0.02, 32.552273811717235)(0.025, 32.609834594548985)(0.03, 33.164192395805884)(0.035, 33.41972794004208)(0.04, 33.34159833965974)(0.045, 33.824240924074424)(0.05, 33.77957868846732)(0.055, 34.028900979162536)(0.06, 34.23479104354531)(0.065, 34.32040889253717)(0.07, 34.556516165135605)(0.075, 34.775904883097695)(0.08, 34.98535349546355)(0.085, 35.19862669231675)(0.09, 35.3945988354474)(0.095, 35.601977507693036)(0.1, 35.72487858163208)(0.105, 35.83625307070917)(0.11, 36.04135799347741)(0.115, 36.174635606822406)(0.12, 36.40685168740781)(0.125, 36.65285846979104)(0.13, 36.83648234512465)(0.135, 37.03941924068021)(0.14, 37.26195063235711)(0.145, 37.433344129490116)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=500$};
+		\node [right] at (endofplotsquare) {$\scriptstyle n=200$};
 		\addplot[] coordinates {
-		(0.005, 30.260287580516597)(0.01, 31.072712082932913)(0.015, 30.438989170134068)(0.02, 31.07887032375107)(0.025, 31.03408484266436)(0.03, 30.826085689381884)(0.035, 31.046097650764082)(0.04, 31.154259509093446)(0.045, 31.016858116914054)(0.05, 31.183097869794107)(0.055, 31.225975525465564)(0.06, 31.23249090698877)(0.065, 31.428023434202135)(0.07, 31.489666903553392)(0.075, 31.56173735319704)(0.08, 31.761301359885042)(0.085, 31.729964289057005)(0.09, 31.886510772066785)(0.095, 32.04347363722421)(0.1, 32.20435818840492)(0.105, 32.371965761927385)(0.11, 32.21538679904917)(0.115, 32.38001692151431)(0.12, 32.48085273757601)(0.125, 32.525780745561875)(0.13, 32.54658216492318)(0.135, 32.74841841730962)(0.14, 32.73824299176051)(0.145, 32.744293569773916)(0.15, 32.7796880354745)(0.155, 32.844022563820616)(0.16, 32.936888670494405)(0.165, 33.05787673349303)(0.17, 33.027986659386485)(0.175, 33.20865432723783)(0.18, 33.246662344351044)(0.185, 33.484850761982344)(0.19, 33.58811058089041)(0.195, 33.72513316286922)(0.2, 33.74255294433519)
+(0.0, 9.324714689596224)(0.005, 30.095584441654534)(0.01, 31.606829627205162)(0.015, 32.244548074817345)(0.02, 32.319578663450045)(0.025, 32.58807145785705)(0.03, 32.54223055419724)(0.035, 32.74254561191743)(0.04, 32.71082614646207)(0.045, 32.945140817400365)(0.05, 33.26420226830405)(0.055, 33.352403581449735)(0.06, 33.26484741097522)(0.065, 33.4364755257399)(0.07, 33.542579090314256)(0.075, 33.65929472234714)(0.08, 33.90576069594512)(0.085, 34.14334017925624)(0.09, 34.08757080939384)(0.095, 34.29799190734557)(0.1, 34.512134923158726)(0.105, 34.73247721906126)(0.11, 34.70947485893356)(0.115, 34.923922016875885)(0.12, 35.04233819928953)(0.125, 35.28459751937852)(0.13, 35.54051858700078)(0.135, 35.71160118222253)(0.14, 35.90299191316566)(0.145, 35.906383030560136)(0.15, 36.01964491090135)(0.155, 36.249355643497005)(0.16, 36.412319774410044)
 			}node[pos=1.0](endofplotsquare){} ;
-		\node [below] at (endofplotsquare) {$n=1000$};
+		\node [right] at (endofplotsquare) {$\scriptstyle n=300$};
+		\addplot[] coordinates {
+(0.0, 9.572501789514533)(0.005, 30.95805680601551)(0.01, 31.852731472234083)(0.015, 31.651653530015025)(0.02, 31.83801995333023)(0.025, 31.805148564578964)(0.03, 32.04955343823956)(0.035, 31.874671808872318)(0.04, 31.962115616320467)(0.045, 32.18970870320976)(0.05, 32.29347571578702)(0.055, 32.32802283202089)(0.06, 32.32551565971646)(0.065, 32.51203709690735)(0.07, 32.671571263469616)(0.075, 33.00950294213178)(0.08, 32.921019505844626)(0.085, 33.01715330808184)(0.09, 33.11615572233624)(0.095, 33.39365131796149)(0.1, 33.19788472106813)(0.105, 33.45802024726345)(0.11, 33.5638596989855)(0.115, 33.685389159897156)(0.12, 33.74232351659747)(0.125, 33.86778330552731)(0.13, 34.01232127428546)(0.135, 34.31523066744031)(0.14, 34.360222768291344)(0.145, 34.357399370664666)(0.15, 34.42537992870109)(0.155, 34.521182964909315)(0.16, 34.6444682447327)(0.165, 34.79488974531291)(0.17, 34.972098710274665)(0.175, 35.175746041381494)(0.18, 35.29487711778767)
+			}node[pos=1.0](endofplotsquare){} ;
+		\node [right] at (endofplotsquare) {$\scriptstyle n=500$};
+		\addplot[] coordinates {
+(0.0, 5.787276464643081)(0.005, 30.032322717189135)(0.01, 31.072712082932913)(0.015, 30.438989170134064)(0.02, 31.078870323751065)(0.025, 31.034084842664363)(0.03, 30.826085689381884)(0.035, 31.04609765076408)(0.04, 31.154259509093443)(0.045, 31.016858116914054)(0.05, 31.183097869794107)(0.055, 31.225975525465568)(0.06, 31.23249090698877)(0.065, 31.428023434202135)(0.07, 31.489666903553392)(0.075, 31.561737353197035)(0.08, 31.761301359885042)(0.085, 31.729964289057)(0.09, 31.886510772066778)(0.095, 32.04347363722421)(0.1, 32.20435818840492)(0.105, 32.371965761927385)(0.11, 32.21538679904917)(0.115, 32.38001692151431)(0.12, 32.480852737576015)(0.125, 32.525780745561875)(0.13, 32.54658216492318)(0.135, 32.74841841730962)(0.14, 32.738242991760515)(0.145, 32.744293569773916)(0.15, 32.77968803547449)(0.155, 32.844022563820616)(0.16, 32.936888670494405)(0.165, 33.05787673349303)(0.17, 33.027986659386485)(0.175, 33.208654327237824)(0.18, 33.24666234435104)(0.185, 33.484850761982344)(0.19, 33.7582361354258)(0.195, 33.72513316286922)(0.2, 33.742552944335195)
+			}node[pos=1.0](endofplotsquare){} ;
+		\node [below] at (endofplotsquare) {$\scriptstyle n=1000$};
 		\end{axis}
@@
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 76.80881648298994)(0.01, 70.80012751036021)(0.015, 66.60353535353535)(0.02, 62.960629921259844)(0.025, 59.830268741159834)(0.03, 57.38265464718681)(0.035, 54.86272684969753)(0.04, 52.966426490878426)(0.045, 50.833715771760744)(0.05, 49.34260238778903)(0.055, 47.48114630467571)(0.06, 46.261543044384865)(0.065, 45.21393912659903)(0.07, 43.60780860120358)(0.075, 42.741234424804404)(0.08, 41.970541970541966)(0.085, 41.27275292789615)(0.09, 41.34324249931186)(0.095, 40.828241683638836)(0.1, 40.36967586391642)(0.105, 40.67885117493473)(0.11, 40.33732457834427)(0.115, 40.80762478053674)(0.12, 41.318681318681314)(0.125, 41.896387832699624)(0.13, 42.54679916801479)(0.135, 43.2678270634475)(0.14, 44.87427466150871)(0.145, 46.60652040188641)(0.15, 48.55862874951305)(0.155, 50.767251676927316)(0.16, 53.47442378545112)(0.165, 59.068590983484604)
-			}node[pos=0.7](endofplotsquare){} ;
-		\node [above right] at (endofplotsquare) {$n=10$};
+(0.0, 100.0)(0.005, 75.6291090455679)(0.01, 68.86366141298357)(0.015, 64.15161809404613)(0.02, 60.30668127053669)(0.025, 57.17914392613188)(0.03, 54.55578277664167)(0.035, 52.12060967528165)(0.04, 50.0814332247557)(0.045, 48.13910921293472)(0.05, 46.30180448145945)(0.055, 44.77126228174479)(0.06, 43.265700483091784)(0.065, 41.80088407592652)(0.07, 40.46538368433793)(0.075, 38.982235714929814)(0.08, 37.767521494770534)(0.085, 36.57442916986252)(0.09, 35.434337525592284)(0.095, 34.23204098688274)(0.1, 33.228055753852374)(0.105, 32.00063188430773)(0.11, 30.73345259391771)(0.115, 30.234530726493926)(0.12, 28.65745660644704)(0.125, 28.41693992883556)(0.13, 27.203065134099617)(0.135, 26.740179186767747)(0.14, 26.437563797209936)(0.145, 26.291079812206572)(0.15, 26.312314295146912)(0.155, 26.404676843130886)(0.16, 27.169094363521214)(0.165, 28.051787916152897)(0.17, 29.097992208570574)(0.175, 30.20954598370198)(0.18, 32.12290502793296)(0.185, 34.90216816499207)(0.19, 37.85536159600998)(0.195, 41.80895246885095)(0.2, 47.16356107660455)(0.205, 55.58231549974196)
+			}node[pos=0.715](endofplotsquare){} ;
+		\node [above] at (endofplotsquare) {$\scriptstyle n=50$};
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 77.6561403508772)(0.01, 71.34845838015866)(0.015, 66.77283196861327)(0.02, 62.981189851268596)(0.025, 60.0)(0.03, 57.0902927514777)(0.035, 54.45127942244435)(0.04, 51.96859607876512)(0.045, 49.97258771929825)(0.05, 47.57404572092287)(0.055, 45.676705541500894)(0.06, 43.987817089452605)(0.065, 42.12854540723393)(0.07, 40.28687246647957)(0.075, 38.81136950904393)(0.08, 36.880072137060424)(0.085, 35.22028211023427)(0.09, 33.87552312037438)(0.095, 32.53546508941362)(0.1, 30.81437249047669)(0.105, 28.95112416489131)(0.11, 27.395132055929572)(0.115, 26.174496644295303)(0.12, 24.903425186711306)(0.125, 23.670007710100233)(0.13, 23.065173116089614)(0.135, 21.940071102082275)(0.14, 20.811153358681874)(0.145, 20.550688360450565)(0.15, 19.490254872563717)(0.155, 19.37869822485207)(0.16, 19.30933852140078)(0.165, 19.34787820666507)(0.17, 19.38534278959811)(0.175, 20.506329113924053)(0.18, 20.644283121597095)(0.185, 22.798605056669572)(0.19, 24.916247906197654)(0.195, 27.07537688442211)(0.2, 31.11861861861862)(0.205, 35.2304469273743)(0.21, 41.46645865834633)(0.215, 51.718869365928185)
-			}node[pos=0.7](endofplotsquare){} ;
-		\node [above right] at (endofplotsquare) {$n=25$};
+(0.0, 100.0)(0.005, 71.70551322277007)(0.01, 64.21561427636762)(0.015, 59.152215799614645)(0.02, 55.14354066985646)(0.025, 51.94629575968318)(0.03, 49.275021184445905)(0.035, 46.972740315638454)(0.04, 44.80417284949862)(0.045, 43.010835657359536)(0.05, 41.346756248784814)(0.055, 39.7071490094746)(0.06, 38.23283082077052)(0.065, 37.03703703703704)(0.07, 35.79600778967868)(0.075, 34.463684463684466)(0.08, 33.269969506158176)(0.085, 32.158590308370044)(0.09, 31.136680613668062)(0.095, 30.152342627191725)(0.1, 29.132513661202182)(0.105, 28.262910798122064)(0.11, 27.26222851395148)(0.115, 26.33194069582578)(0.12, 25.371764273912248)(0.125, 24.603463329452854)(0.13, 24.022145204122978)(0.135, 23.156745925250025)(0.14, 21.999107541276217)(0.145, 21.22984228247387)(0.15, 20.78947368421054)(0.155, 19.490781387181737)(0.16, 19.133486206656936)(0.165, 18.550474547023295)(0.17, 18.398637137989777)(0.175, 18.506084767100294)(0.18, 19.443307408923456)(0.185, 19.87127916331456)(0.19, 21.904024767801857)(0.195, 24.071322436849925)(0.2, 26.37949448202207)(0.205, 30.45212765957447)(0.21, 35.468130527599875)(0.215, 42.673452986873826)(0.22, 54.60844005878648)
+			}node[pos=0.693](endofplotsquare){} ;
+		\node [above] at (endofplotsquare) {$\scriptstyle n=75$};
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 73.41959943954505)(0.01, 66.4436173582515)(0.015, 61.55984585594049)(0.02, 57.93403164698015)(0.025, 54.687443245795656)(0.03, 51.969260326609025)(0.035, 49.440167949615116)(0.04, 47.26428079834825)(0.045, 45.52155103348822)(0.05, 43.63969363969365)(0.055, 41.895873454808815)(0.06, 40.23579989577905)(0.065, 38.6774968170317)(0.07, 37.13806461919406)(0.075, 36.073059360730596)(0.08, 34.695663042119726)(0.085, 33.263492802545294)(0.09, 31.835726416550862)(0.095, 30.517167250168896)(0.1, 29.4787827093551)(0.105, 27.9820525495266)(0.11, 27.141351798886053)(0.115, 25.998680422264876)(0.12, 25.14569457659372)(0.125, 23.599320882852297)(0.13, 22.825830083894598)(0.135, 21.39899438036083)(0.14, 20.631424375917767)(0.145, 19.502512341971507)(0.15, 18.148213342721355)(0.155, 17.384900322293685)(0.16, 16.283268301205524)(0.165, 14.950369495824049)(0.17, 13.428466886205634)(0.175, 12.641165755919854)(0.18, 11.73265528514348)(0.185, 10.732414793328498)(0.19, 10.808876163206872)(0.195, 9.896391568417291)(0.2, 10.109193377949982)(0.205, 11.514736120630568)(0.21, 13.028990336554482)(0.215, 15.574032619123763)(0.22, 21.29793510324484)(0.225, 28.771466314398943)(0.23, 40.30243261012492)
-			}node[pos=0.745](endofplotsquare){} ;
-		\node [above] at (endofplotsquare) {$n=50$};
-		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 66.63264504985476)(0.01, 59.04596954607779)(0.015, 53.999488883209814)(0.02, 50.347727640304065)(0.025, 47.17075223238636)(0.03, 44.61167971101746)(0.035, 42.5287356321839)(0.04, 40.44242768009076)(0.045, 38.82229464729603)(0.05, 36.95086234949561)(0.055, 35.37062155908402)(0.06, 34.21394768318686)(0.065, 32.83438879293802)(0.07, 31.577620967741936)(0.075, 30.56930693069307)(0.08, 29.513914294773297)(0.085, 28.306342780027)(0.09, 27.2679657647577)(0.095, 26.1414503133393)(0.1, 25.240174672489086)(0.105, 24.242424242424242)(0.11, 23.719661228897856)(0.115, 22.66414141414141)(0.12, 21.690588327422837)(0.125, 20.795378804710058)(0.13, 19.986774673499745)(0.135, 19.030112044817923)(0.14, 18.19329010922065)(0.145, 17.679088336256697)(0.15, 16.523420713364853)(0.155, 15.733937115516067)(0.16, 15.263202437373053)(0.165, 14.070096816471484)(0.17, 13.594470046082947)(0.175, 12.479061976549408)(0.18, 11.941848390446522)(0.185, 10.83476924993254)(0.19, 10.110966462091636)(0.195, 9.32322149863986)(0.2, 8.034350357128114)(0.205, 6.9143446852425186)(0.21, 6.365503080082135)(0.215, 5.532786885245901)(0.22, 5.906108026249369)(0.225, 6.26865671641791)(0.23, 10.4)(0.235, 19.900083263946712)(0.24, 39.94439295644115)
+(0.0, 100.0)(0.005, 68.65666138131937)(0.01, 60.63128685397155)(0.015, 55.31576856878062)(0.02, 51.33935647487716)(0.025, 48.17702361843614)(0.03, 45.47825056299633)(0.035, 43.247126436781606)(0.04, 41.15998879237881)(0.045, 39.46929740660782)(0.05, 37.83422459893048)(0.055, 36.21545003543586)(0.06, 34.86767583153125)(0.065, 33.45501559053921)(0.07, 32.26047904191617)(0.075, 31.25)(0.08, 30.186491448449132)(0.085, 29.03995229576625)(0.09, 28.059248095512835)(0.095, 27.050610820244327)(0.1, 26.39724849527085)(0.105, 25.45442167608415)(0.11, 24.657534246575345)(0.115, 23.77777777777778)(0.12, 22.975352112676052)(0.125, 22.305764411027564)(0.13, 21.322987559061936)(0.135, 20.541178997100825)(0.14, 20.171546251671927)(0.145, 19.27825261158595)(0.15, 18.712795673051776)(0.155, 17.89802289281998)(0.16, 17.240096708201612)(0.165, 15.968992248062015)(0.17, 15.514592933947773)(0.175, 14.936914936914944)(0.18, 14.343434343434344)(0.185, 14.314214463840399)(0.19, 14.538310412573674)(0.195, 15.749162278602203)(0.2, 17.11627906976744)(0.205, 19.464285714285715)(0.21, 22.907861369399832)(0.215, 27.28706624605678)(0.22, 34.412385643912735)(0.225, 45.040840140023334)
 			}node[pos=1.0](endofplotsquare){} ;
@@
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 58.98664343786295)(0.01, 50.57766367137355)(0.015, 45.77709671715683)(0.02, 42.100909842845326)(0.025, 39.265978521530606)(0.03, 36.95646756871246)(0.035, 34.86590038314177)(0.04, 33.287324591672416)(0.045, 31.549749463135292)(0.05, 30.303030303030305)(0.055, 28.925445534113674)(0.06, 27.7629141798724)(0.065, 26.8988231513837)(0.07, 25.831202046035806)(0.075, 24.751099791618426)(0.08, 23.846328711070697)(0.085, 22.90933467404057)(0.09, 22.152617503755)(0.095, 21.356421356421354)(0.1, 20.641965664778876)(0.105, 19.924470242674317)(0.11, 19.246298788694478)(0.115, 18.532910658894913)(0.12, 17.784217265314382)(0.125, 17.0)(0.13, 16.44693473961766)(0.135, 15.58770225480432)(0.14, 14.952787478980731)(0.145, 14.591315453384416)(0.15, 14.068681753441997)(0.155, 13.438921122785)(0.16, 12.576495566379412)(0.165, 12.1045477014335)(0.17, 11.67240719479524)(0.175, 10.71428571428572)(0.18, 10.216812015503878)(0.185, 9.878838771593088)(0.19, 8.965888367365245)(0.195, 8.532969639468684)(0.2, 7.883082373782105)(0.205, 7.0957119967072035)(0.21, 6.501031561388886)(0.215, 5.830903790087479)(0.22, 4.503241633082184)(0.225, 3.994190268700073)(0.23, 3.258508327299059)(0.235, 3.7089871611982885)(0.24, 9.308510638297872)(0.245, 38.92587660896582)
+(0.0, 100.0)(0.005, 63.73968339872818)(0.01, 55.25949492940943)(0.015, 49.836271162823095)(0.02, 45.76241291119146)(0.025, 42.848738259828124)(0.03, 40.2020202020202)(0.035, 38.270402897591175)(0.04, 36.19752340682573)(0.045, 34.672815107597714)(0.05, 33.17294840951617)(0.055, 31.764378220303577)(0.06, 30.434782608695652)(0.065, 29.205903960462162)(0.07, 28.03868535365953)(0.075, 27.118862217645933)(0.08, 26.08420386198165)(0.085, 25.031172069825438)(0.09, 24.41860465116279)(0.095, 23.50749083447746)(0.1, 22.719556865898333)(0.105, 21.842863019333617)(0.11, 21.073630758070365)(0.115, 20.600858369098713)(0.12, 19.767935474741762)(0.125, 19.123511550785672)(0.13, 18.417662783772183)(0.135, 17.85180410603837)(0.14, 17.085768655702044)(0.145, 16.275049964889536)(0.15, 15.851899342843398)(0.155, 15.317031861966747)(0.16, 14.52991452991453)(0.165, 13.919031719532558)(0.17, 13.261072502852397)(0.175, 13.0033104934945)(0.18, 12.267278755419527)(0.185, 11.519029121283687)(0.19, 10.920446659516758)(0.195, 10.175879396984925)(0.2, 10.130515848353014)(0.205, 10.458715596330276)(0.21, 11.057692307692308)(0.215, 13.560300057703405)(0.22, 17.312943746586566)(0.225, 23.076923076923077)(0.23, 33.36203185535945)(0.235, 53.74149659863946)
+			}node[pos=1.0](endofplotsquare){} ;
+		%\node [above] at (endofplotsquare) {$n=150$};
+		\addplot[] coordinates {
+(0.0, 100.0)(0.005, 60.3675645342312)(0.01, 51.319740793425)(0.015, 46.22398877718026)(0.02, 42.248989357313754)(0.025, 39.48366318632798)(0.03, 36.95646756871247)(0.035, 34.86590038314176)(0.04, 33.287324591672416)(0.045, 31.549749463135292)(0.05, 30.303030303030305)(0.055, 28.925445534113674)(0.06, 27.7629141798724)(0.065, 26.898823151383702)(0.07, 25.83120204603581)(0.075, 24.751099791618426)(0.08, 23.846328711070697)(0.085, 22.90933467404057)(0.09, 22.152617503755)(0.095, 21.356421356421354)(0.1, 20.641965664778876)(0.105, 19.924470242674317)(0.11, 19.246298788694478)(0.115, 18.639682728804615)(0.12, 17.889352537353624)(0.125, 17.10362047440699)(0.13, 16.548704612042002)(0.135, 15.788444936719163)(0.14, 15.150341979610268)(0.145, 14.5667656734055)(0.15, 14.26135287058674)(0.155, 13.72303844951547)(0.16, 13.038076899186276)(0.165, 12.357716063644613)(0.17, 11.672407194795255)(0.175, 11.417322834645667)(0.18, 10.993035542747359)(0.185, 10.327952015756024)(0.19, 9.697508896797151)(0.195, 9.397944199706314)(0.2, 8.847889916297829)(0.205, 7.737226277372263)(0.21, 7.525325615050651)(0.215, 7.845934379457917)(0.22, 9.22970159611381)(0.225, 13.19763624425476)(0.23, 20.286396181384248)(0.235, 32.93591654247392)
 			}node[pos=1.0](endofplotsquare){} ;
@@
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 48.82985928211302)(0.01, 40.20061728395061)(0.015, 35.8974358974359)(0.02, 32.10526315789474)(0.025, 29.89508775370134)(0.03, 27.697441601779754)(0.035, 26.26728110599078)(0.04, 24.66329966329966)(0.045, 23.238526179702653)(0.05, 22.453433091730965)(0.055, 21.28060263653484)(0.06, 20.47278564132497)(0.065, 19.744318181818187)(0.07, 18.640077551585644)(0.075, 17.621533663299214)(0.08, 17.415433403805487)(0.085, 16.612798965740136)(0.09, 16.096757852076994)(0.095, 15.320195510725066)(0.1, 15.115005476451262)(0.105, 14.304548450889918)(0.11, 13.963287073867834)(0.115, 13.283062645011604)(0.12, 12.956621004566218)(0.125, 12.517580872011253)(0.13, 12.032412032412036)(0.135, 11.314900744076228)(0.14, 10.927008880225257)(0.145, 10.857264866019005)(0.15, 10.408432147562582)(0.155, 10.170285892829247)(0.16, 9.61994026161294)(0.165, 9.276248725790005)(0.17, 8.879802110151953)(0.175, 8.181135851888914)(0.18, 7.840951319212183)(0.185, 7.4437788470980895)(0.19, 7.141815353201405)(0.195, 6.774544137181502)(0.2, 6.153993855606756)(0.205, 5.965045592705168)(0.21, 5.580409700965385)(0.215, 4.929577464788732)(0.22, 4.562383612662934)(0.225, 3.944315545243619)(0.23, 2.784222737819025)(0.235, 2.7586206896551726)(0.24, 2.059496567505721)(0.245, 4.0)
+(0.0, 100.0)(0.005, 55.39254559873117)(0.01, 46.27647958069447)(0.015, 40.98883572567782)(0.02, 37.57387706855791)(0.025, 34.92709747016042)(0.03, 32.80632411067194)(0.035, 30.68683049779459)(0.04, 29.356357927786497)(0.045, 27.967337416156322)(0.05, 26.414400135850336)(0.055, 25.340360122968818)(0.06, 24.41984245262934)(0.065, 23.43230897009966)(0.07, 22.48062015503876)(0.075, 21.73374613003096)(0.08, 20.796890184645278)(0.085, 20.076344983895975)(0.09, 19.445222751470993)(0.095, 18.699186991869922)(0.1, 17.921584588251264)(0.105, 17.33511586452763)(0.11, 16.812609457092822)(0.115, 16.187842917008684)(0.12, 15.665729619217991)(0.125, 14.9634806036751)(0.13, 14.223850766155895)(0.135, 13.786008230452675)(0.14, 13.098339303158584)(0.145, 12.854905425484917)(0.15, 12.447885646217985)(0.155, 11.866540761724895)(0.16, 11.363060799096086)(0.165, 10.81081081081081)(0.17, 10.077459927908572)(0.175, 9.79381443298968)(0.18, 9.509058481179007)(0.185, 8.700522778192685)(0.19, 8.360485781990516)(0.195, 7.958553791887135)(0.2, 7.704070487147756)(0.205, 6.985161056822299)(0.21, 6.2404211968770875)(0.215, 6.123395977226902)(0.22, 5.431878895814782)(0.225, 6.036745406824147)(0.23, 7.731520815632965)(0.235, 15.277777777777779)(0.24, 32.60340632603406)
+			}node[pos=1.0](endofplotsquare){} ;
+		%\node [above] at (endofplotsquare) {$n=300$};
+		\addplot[] coordinates {
+(0.0, 100.00000000000001)(0.005, 48.82985928211302)(0.01, 40.20061728395061)(0.015, 35.8974358974359)(0.02, 32.10526315789474)(0.025, 29.89508775370134)(0.03, 27.69744160177975)(0.035, 26.26728110599078)(0.04, 24.878294443511834)(0.045, 23.238526179702653)(0.05, 22.453433091730965)(0.055, 21.28060263653484)(0.06, 20.47278564132497)(0.065, 19.744318181818187)(0.07, 18.640077551585644)(0.075, 17.62153366329921)(0.08, 17.41543340380549)(0.085, 16.612798965740136)(0.09, 16.096757852076994)(0.095, 15.320195510725066)(0.1, 15.115005476451262)(0.105, 14.304548450889916)(0.11, 13.963287073867834)(0.115, 13.283062645011602)(0.12, 12.95662100456622)(0.125, 12.517580872011251)(0.13, 12.032412032412036)(0.135, 11.314900744076228)(0.14, 10.927008880225257)(0.145, 10.857264866019005)(0.15, 10.408432147562582)(0.155, 10.170285892829245)(0.16, 9.619940261612939)(0.165, 9.276248725790005)(0.17, 8.879802110151953)(0.175, 8.181135851888914)(0.18, 7.840951319212183)(0.185, 7.44377884709809)(0.19, 7.141815353201405)(0.195, 6.774544137181501)(0.2, 6.297929447852767)(0.205, 5.965045592705168)(0.21, 5.580409700965386)(0.215, 5.32959326788219)(0.22, 4.6023546930988015)(0.225, 4.557714918044133)(0.23, 3.67816091954023)(0.235, 4.514672686230249)(0.24, 11.203319502074688)(0.245, 43.82314694408323)
 			}node[pos=1.0](endofplotsquare){} ;
@@
 		\addplot[] coordinates {
-		(0.0, 100.0)(0.005, 42.16746291174252)(0.01, 33.35416015828387)(0.015, 29.34782608695652)(0.02, 26.232905097389136)(0.025, 23.465482932802693)(0.03, 22.176210195630443)(0.035, 20.876445526475944)(0.04, 19.515807095486448)(0.045, 18.938835666912308)(0.05, 17.877821103627564)(0.055, 16.87069407276661)(0.06, 16.3916391639164)(0.065, 15.064102564102571)(0.07, 14.902449149024491)(0.075, 14.14141414141414)(0.08, 13.669774554782698)(0.085, 12.951474053768097)(0.09, 12.437623575934465)(0.095, 11.8800461361015)(0.1, 11.280101394169831)(0.105, 10.638865424798817)(0.11, 10.834674437823494)(0.115, 10.141206675224653)(0.12, 9.932659932659941)(0.125, 9.76821192052981)(0.13, 9.201954397394145)(0.135, 8.78038979304803)(0.14, 8.623417721518992)(0.145, 8.424908424908427)(0.15, 8.168754322600472)(0.155, 7.856817837099964)(0.16, 7.490636704119851)(0.165, 7.441688263606079)(0.17, 7.214611872146119)(0.175, 6.684027777777785)(0.18, 6.699077715021094)(0.185, 6.061680255228631)(0.19, 5.955012808365783)(0.195, 5.437352245862879)(0.2, 5.426783135016155)(0.205, 4.826880436636545)(0.21, 4.832613390928723)(0.215, 4.233870967741943)(0.22, 3.8909211839042195)(0.225, 3.712985556947849)(0.23, 3.1198686371100166)(0.235, 2.134646962233169)(0.24, 1.1494252873563218)(0.245, 1.6181229773462782)
+(0.0, 100.0)(0.005, 42.35588972431077)(0.01, 33.35416015828387)(0.015, 29.347826086956516)(0.02, 26.232905097389136)(0.025, 23.46548293280269)(0.03, 22.176210195630443)(0.035, 20.876445526475948)(0.04, 19.515807095486448)(0.045, 18.938835666912308)(0.05, 17.877821103627564)(0.055, 16.87069407276661)(0.06, 16.391639163916395)(0.065, 15.064102564102573)(0.07, 14.902449149024491)(0.075, 14.141414141414142)(0.08, 13.669774554782698)(0.085, 12.951474053768099)(0.09, 12.437623575934463)(0.095, 11.8800461361015)(0.1, 11.28010139416983)(0.105, 10.638865424798817)(0.11, 10.834674437823494)(0.115, 10.141206675224653)(0.12, 9.932659932659941)(0.125, 9.76821192052981)(0.13, 9.201954397394145)(0.135, 8.780389793048029)(0.14, 8.62341772151899)(0.145, 8.424908424908427)(0.15, 8.168754322600472)(0.155, 7.856817837099964)(0.16, 7.49063670411985)(0.165, 7.441688263606079)(0.17, 7.2146118721461185)(0.175, 6.684027777777784)(0.18, 6.699077715021094)(0.185, 6.061680255228631)(0.19, 5.713481564874738)(0.195, 5.43735224586288)(0.2, 5.426783135016154)(0.205, 5.037440435670528)(0.21, 4.832613390928723)(0.215, 4.233870967741943)(0.22, 3.9005087620124423)(0.225, 3.8208168642951144)(0.23, 3.4433097669547124)(0.235, 2.7256406071486934)(0.24, 2.588996763754045)(0.245, 10.850439882697946)
 			}node[pos=0.85](endofplotsquare){} ;
-		\node [below left] at (endofplotsquare) {$n=1000$};
+		\node [below left] at (endofplotsquare) {$\scriptstyle n=1000$};
 		\end{axis}
 		\end{tikzpicture}
-		\caption{The percent reduction in the 0.5 probability bound, that going from our EBB to Hoeffding's inequality (representing perfect knowledge of the variance, $\hat{\sigma}^2=\sigma^2$) achieves, for various n=10,25,50,100,200,500,1000.}
+		\caption{The percent reduction in the 0.5 probability bound, that going from our EBB to Hoeffding's inequality (representing perfect knowledge of the variance, $\hat{\sigma}^2=\sigma^2$) achieves, for various $n=50,75,100,150,200,300,500,1000$.}
 		\label{biggraph4}
@@
 \section{Discussion}\label{discussion}
-We also fitted some rough envelopes over our calculated numerics for $25\le n\le 1000$:
-$$\scriptstyle \p\left(\sigma^2 - \hat{\sigma}^2>\frac{D^2}{\sqrt{n}}\left(0.09+0.3\log(1/w)+\frac{25w}{D^6}(\sigma^2)^2(D^2-4\sigma^2)+\frac{3}{2n}\right)\right) \le w$$
+We also fitted some rough envelopes over our calculated numerics for $50\le n\le 1000$:
+$$\scriptstyle \p\left(\sigma^2 - \hat{\sigma}^2>\frac{D^2}{\sqrt{n}}\left(0.12+0.3\log(1/w)+\frac{25w}{D^6}(\sigma^2)^2(D^2-4\sigma^2)+\frac{3}{2n}\right)\right) \le w$$
 And
-$$\scriptstyle \p\left(\mu - \hat{\mu}^2>\frac{D}{20\sqrt{n}}\left(16 - 10y + \frac{20D^2}{nD^2-4n\hat{\sigma}^2} + \left(y- \exp\left(-\frac{n^2}{16D^4}(1-4\hat{\sigma}^2)^2\right)\right)^{-1}\right)\right) \le y$$
-\hfill When $\scriptstyle y-exp\left(-\frac{n^2}{16D^4}(1-4\hat{\sigma}^2)^2\right)>\frac{3}{20}$\\
+$$\scriptstyle \p\left(\mu - \hat{\mu}>\frac{D}{20\sqrt{n}}\left(\left(y-exp\left(\frac{-1}{10}\left(\frac{n}{4}-\frac{n\hat{\sigma}^2}{D^2}\right)^2\right)\right)^{-1}+ 100\left(\frac{n}{4}-\frac{n\hat{\sigma}^2}{D^2}\right)^{-3} -12y+13+20\frac{\hat{\sigma}^2}{D^2} +\frac{8000}{n^2}\right)\right) \le y$$
+\hfill When $\scriptstyle y-\exp\left(\frac{-1}{10}(\frac{n}{4}-n\hat{\sigma}^2)^2\right)>\frac{1}{20}$\\
 
-Over our computed datapoints these envelopes were witnessed to always widen the probability bounds with a median width increase of $0.03367D^2$ across $7569$ datapoints and $0.0105D$ across $36918$ datapoints respectively.
+Over our computed datapoints these envelopes were witnessed to always widen the probability bounds with a median width increase of $0.031858D^2$ across $7823$ datapoints and $0.0063895D$ across $35002$ datapoints respectively.
 These envelopes are supplied only as a loose approximation over the results of this paper and the reader is encouraged to explore the technique and source code\footnote{at: \href{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}} if tighter or more accurate expressions are required.

### 2018-08-20 paper/main.tex
updated paper

@@
         rgb255(0pt)=(255, 255, 0);
-        rgb255(245pt)=(0, 0, 0);
-        rgb255(255pt)=(0, 0, 255);
+        rgb255(85pt)=(0, 0, 0);
+        rgb255(95pt)=(0, 0, 255);
+        rgb255(365pt)=(200, 255, 255);
         rgb255(1000pt)=(200, 255, 255)
@@
 \title{An Engineered Empirical Burnstein Bound}
-\runtitle{An Engineered Empirical Burnstein Bound}
+\runtitle{Engineered Empirical Burnstein Bound}
 
@@
 \begin{abstract}
-We derive a stronger Empirical Burnstein Bound (EBB) using a combination of Chernoff bounds and probability unions.
+We derive a stronger Empirical Burnstein Bound (EBB) using a combination of probability unions and Chernoff bounds for the mean of samples and mean of sample squares.
 Like other EBBs, our EBB is a concentration inequality for the divergence of the sample mean from the population mean in terms of the sample variance.
-The new EBB is numerically solved and compared against previous work, and also against a bound with perfect information about the variance.
+The new EBB is numerically solved and compared against previous work, And for context it is also compared against a bound with perfect information about the variance.
 The analysis reveals that our technique can shrink existing probability bounds by about a third, and that perfect variance information would reduce it by about a third again.
@@
 A recent development is Empirical Burnstein Bounds (EBB)\cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15} which are probability bounds describing the likely divergence of the sample mean from the mean in terms of the sample variance under assumption that the population data is bounded within an interval of a known width.
-EBBs have been used as a method of giving confidence bounds for the mean, which is a common and important process in many industrial applications.
+EBBs have been used as a method of giving confidence bounds for the mean, which is a common and important process in industrial applications.
 We take inspiration and extend Maurer and Pontil's work \cite{Maurer50empiricalbernstein} as we combine older techniques to develop a new and stronger EBB
@@
 Our first probability bound is a Chernoff bound on the sample mean.
-This bound is not new and was derived by Wassily Hoeffding\footnote{Apparently it is also known as Bennet's inequality\cite{MR1782937}} \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598,MR1782937}.
+This bound is not new and was derived by Wassily Hoeffding \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598,MR1782937}.
 
@@
 $E\left[\exp(sX)\right] \le \E[\alpha s^2X^2+\beta sX+\gamma] = \alpha s^2\E[X^2]+\gamma = as^2\sigma^2+c$\\
-If $c=\max(sa,sb)$ choosing $\alpha,\beta,\gamma$ to minimize the expression leads\footnote{see Appendix \ref{appendix1}} to:\\
+If $c=\max(sa,sb)$ choosing $\alpha,\beta,\gamma$ to minimize the expression leads to:\\
 $E\left[\exp(sX)\right] \le (s^2\sigma^2\exp(c) + c^2\exp(-s^2\sigma^2/c))/(s^2\sigma^2 + c^2) $\\
-Hence by application of our lemma \ref{chernoff1}:\\
+(See Appendix \ref{appendix1}), Hence by application of our lemma \ref{chernoff1}:\\
 $ \textstyle\p(\hat{\mu}\ge t)\le \left(s^2\sigma^2\exp(c) + c^2\exp(-s^2\sigma^2/c)\right)^n\exp(-nst)(s^2\sigma^2 + c^2)^{-n} $\\
@@
 The result of this theorem is an EBB - that is a probabilistic bound for the divergence of the sample mean from the mean parametrized by the sample variance.
-Care must be taken in applying this theorem that all the assumptions hold, the inverses exist, and the domains of the functions are propagated through the analysis\footnote{see notes in Appendix \ref{appendix2}}.
+Care must be taken in applying this theorem that all the assumptions hold, the inverses exist, and the domains of the functions are propagated through the analysis (see notes in Appendix \ref{appendix2}).
 
@@
 	zticklabel style={/pgf/number format/fixed},
-	view={-110}{35},
+	view={-105}{35},
 	%point meta min=-0.3, point meta max=0.3,
-	point meta min=-0.1, point meta max=0.3,
+	point meta min=-0.1, point meta max=1.0,
 	title={Advantage over Entropic bound for n=200},
@@
 	colorbar style={
-        at={(1.07,0.66)},
+        at={(1.07,0.64)},
 		title=Advantage,
@@
 		%ytick={-1,-0.75,...,1},
-        height=0.54*\pgfkeysvalueof{/pgfplots/parent axis height},
+        height=0.52*\pgfkeysvalueof{/pgfplots/parent axis height},
 		xticklabel style={
@@
 Evaluating this new EBB consisted of numerically solving a minimization over a maximization over inversions of nested function minimizations.
-This process was conducted in C and Python, using techniques of direct parameter searching, coordinate transforming of data points (for inversions) and interpolations as necessary.\footnote{see Appendix \ref{appendix2} for discussion of the details}
+This process was conducted in C and Python, using techniques of direct parameter searching, coordinate transforming of data points for inversions and interpolations as necessary (see Appendix \ref{appendix2} for discussion of the details).
 And through this process we were able to witness that the assumptions necessary for our theorems held true and thus were able evaluate our new EBB.
@@
 We also compared the loss in confidence that our EBB gave over a bound which could be achieved with perfect information about the variance.
-Specifically Hoeffding's inequality\footnote{Hoeffding's inequality per theorem \ref{hoeffdings1} is understood here to be relatively tight.} assuming $\hat{\sigma}^2=\sigma^2$.
+Specifically Hoeffding's inequality assuming $\hat{\sigma}^2=\sigma^2$ (here assumed it to be relatively tight).
 The decrease of the bounds that perfect variance information would offer over our EBB is plotted in figure \ref{biggraph4}.
@@
 Over our computed datapoints these envelopes were witnessed to always widen the probability bounds with a median width increase of $0.031858D^2$ across $7823$ datapoints and $0.0063895D$ across $35002$ datapoints respectively.
-These envelopes are supplied only as a loose approximation over the results of this paper and the reader is encouraged to explore the technique and source code\footnote{at: \href{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}} if tighter or more accurate expressions are required.
+These envelopes are supplied only as an approximation over the results and the reader is encouraged to explore the technique and source code (see Appendix \ref{appendix2}) if tighter or more accurate expressions are required.
 
@@
 \section{Parabola Fitting}\label{appendix1}
-For the task\footnote{Here we carry the derivation with the $x$-axis scaling factor $s$ removed for simplicity} of selecting an $\alpha,\beta,\gamma$ as the parameters of a parabola $\alpha x^2+\beta x+\gamma\ge \exp(x)$ for all $c\le x\le d$ which minimizes $z\alpha+\gamma$ for constants $c,d,z$.
+For the task of selecting an $\alpha,\beta,\gamma$ as the parameters of a parabola $\alpha x^2+\beta x+\gamma\ge \exp(x)$ for all $c\le x\le d$ which minimizes $z\alpha+\gamma$ for constants $c,d,z$.
 We witness that any such parabola much tangentially touch the exponential curve at one point (at $x=f<d$) and intersect it at another (at $x=d$), as illustrated in the following figure \ref{fig:graph1}:
@@
 For further information, the reader is encouraged to download, inspect and experiment with the sourcecode, available at:\\\href{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}{https://github.com/Markopolo141/Engineered-Empirical-Burnstein-Bound}\\
-The sourcecode consists of a small\footnote{$\sim 150$ lines of C code, and $\sim 250$ lines of Python code} documented package of C and Python code, that was used (and is setup) to compute the results of the paper.
+The sourcecode consists of a small documented package of C and Python code, that was used (and is setup to) compute the results of the paper.
 

### 2018-08-21 paper/main.tex
update paper

@@
 Our first probability bound is a Chernoff bound on the sample mean.
-This bound is not new and was derived by Wassily Hoeffding \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598,MR1782937}.
+This bound is not new and was derived by Wassily Hoeffding \cite{hoeffding1} and has subsequently been a subject of discussion and many further developments \cite{hoeffding2,Bentkus08boundsfor,Pinelis2014,zbMATH00812598}.
 

### 2018-08-21 paper/main.tex
update paper

@@
 \ead[label=e2]{markburgess1989@gmail.com}}
-\thankstext{t1}{A great thanks to Archie Chapman, Paul Scott and Sylvie Thiebaux; for Academic advice and encouragement!}
+\thankstext{t1}{A great thanks to Archie Chapman, Paul Scott and Sylvie Thi{\'e}baux; for Academic advice and encouragement!}
 \address{Mark Alexander Burgess\\College of Engineering \& Computer Science\\Australian National University\\Canberra, ACT, Australia, 2600\\\printead{e1}\\
@@
 Like other EBBs, our EBB is a concentration inequality for the divergence of the sample mean from the population mean in terms of the sample variance.
-The new EBB is numerically solved and compared against previous work, And for context it is also compared against a bound with perfect information about the variance.
+The new EBB is numerically solved and compared against previous work, and for context it is also compared against a bound with perfect information about the variance.
 The analysis reveals that our technique can shrink existing probability bounds by about a third, and that perfect variance information would reduce it by about a third again.
@@
 \kwd{Chernoff bounds}
-\kwd{Hoeffdings inequality}
-\kwd{Emperical Burnstein Bound}
+\kwd{Hoeffding's inequality}
+\kwd{Empirical Burnstein Bound}
 \end{keyword}

### 2020-05-09 latex/main.tex
added latex

\documentclass[runningheads, envcountsame, a4paper]{llncs}

% Recommended, but optional, packages for figures and better typesetting:
%\usepackage{microtype}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amssymb}
%\usepackage{thmtools}
\usepackage{mathtools}	
\usepackage{pgfplots}
%\usepackage{hyperref}
%\usepackage{subcaption}
\usepackage[misc]{ifsym}

\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\p}{\mathbb{P}}
\pgfplotsset{
    colormap={blackwhite}{[5pt]
        rgb255(0pt)=(255, 255, 0);
        rgb255(85pt)=(0, 0, 0);
        rgb255(95pt)=(0, 0, 255);
        rgb255(500pt)=(200, 255, 255);
        rgb255(1000pt)=(200, 255, 255)
    },
}
%\renewcommand{\qedhere}{\begin{equation}\tag*{$\blacksquare$}\end{equation}}
%\newtheorem{Lemma}{Lemma}
%\newtheorem{Theorem}{Theorem}
%\newcommand{\theHalgorithm}{\arabic{algorithm}}

\begin{document}

\title{An Engineered Empirical Bernstein Bound\thanks{A great thanks to Sylvie Thi\'ebaux for advice and encouragement.}
}

\author{Mark A. Burgess\inst{1} (\Letter) \and
Archie C. Chapman\inst{2} \and
Paul Scott\inst{1}}

\authorrunning{M. Burgess, A. Chapman, P. Scott}
\institute{Australian National University, \\College of Engineering \& Computer Science, ACT, 0200, Australia. \\\email{markburgess1989@gmail.com, mark.burgess@anu.edu.au}\\\email{paul.scott@anu.edu.au}\vspace{2mm}\and
University of Sydney, \\School of Electrical and Information Engineering, NSW, 2006, Australia \\\email{archie.chapman@sydney.edu.au}}

\toctitle{An Engineered Empirical Bernstein Bound}
\tocauthor{M.~Burgess, A.~Chapman, P.~Scott}

\maketitle
\setcounter{footnote}{0}

\begin{abstract}
We derive a tightened \textit{empirical Bernstein bound} (EBB) on the variation of the sample mean from the population mean, and show that it improves the performance of \textit{upper confidence bound} (UCB) methods in multi-armed bandit problems.
Like other EBBs, our EBB is a concentration inequality for the variation of the sample mean in terms of the sample variance.
Its derivation uses a combination of probability unions and Chernoff bounds for the mean of samples and mean of sample squares.
Analysis reveals that our approach can tighten the best existing EBBs by about a third, 
and thereby halves the distance to a bound constructed with perfect variance information.
We illustrate the practical usefulness of our novel EBB by applying it to a multi-armed bandit problem as a component of a UCB method. 
Our method outperforms existing approaches by producing lower expected regret than variants of UCB employing several other bounds, including state-of-the-art EBBs.
\keywords{Concentration inequality \and Chernoff bounds \and Hoeffding's inequality \and Empirical Bernstein bound}
\end{abstract}

\section{Introduction}

Data-driven processes and decision-making applications typically rely on sample statistics 
to infer parameters of a population or evaluate decision options.
Depending on the domain, different assumptions can be made about the distribution of the data, 
which in turn determine which computational routines are used to compute the required population statistics. 
These assumptions may be based on prior information, expert opinion, or 
determined from the characteristics of the system under observation.

Within this context, finite-sample \textit{concentration inequalities} are used to place bounds on 
the variation of sample statistics around their population values.
Such bounds are applied in a range of data science contexts for a variety of prediction, machine learning and hypothesis testing tasks, including:
change detection \cite{KiferShaiGehrke2004,8000571} 
and classification \cite{Zia-UrRehman2012} in data streams;
outlier analysis in large databases \cite{Aggarwal2015};
online optimisation \cite{FlaxmanKalaiMcMahan2005,AgarwalDekelXiao2010}; and, of most relevance to this paper, 
online prediction and learning problems \cite{Cesa-BianchiLugosi2006,%Maron1997,
Mnih:2008:EBS:1390156.1390241,DBLP:conf/aaai/ThomasTG15,Maurer50empiricalbernstein},
particularly in settings with \textit{bandit feedback} \cite{AuerCesa-BianchiEtal_SIAM2003,AudibertBubeck_COLT2009,Tran-ThanhChapmanRJ_AAAI2009}. 
% Bandit feedback describes settings where a decision-maker wishes to learn about a system, and to do this, chooses samples from a set of actions and receives feedback regarding their chosen actions only, in the form of a realization of a random variable. 
%Specifically, the decision-maker does not see how the system would have responded, if they had chosen a different action.
%
In particular, the recently developed \textit{empirical Bernstein bounds} (EBB) are of significant interest ~\cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15}. 
These are probability bounds describing the likely difference of a sample mean from the population mean 
in terms of the \textit{sample} variance, 
under the assumption that the population data is bounded within an interval of known width.
EBBs have been used as a method of generating confidence bounds for the mean, and an outstanding task is to see how much these techniques can be improved.

Given this challenge, in this work, we take inspiration and extend the work of  Maurer and Pontil (\cite{Maurer50empiricalbernstein}, M\&P in the remainder)
%combined with older techniques, 
to develop a new EBB.
Our EBB tightens existing bounds by incorporating a combination of bounds on the variation of the sample variance.
Specifically, we use two Chernoff bounds, for the sample mean and the mean of sample squares, which are fused using a probability union and variance decomposition,
to create a novel probability bound for the sample variance, which is then used to derive our novel EBB.

Evaluations show that our EBB significantly tightens the current state-of-the-art bounds. 
Specifically, our EBB can shrink the best existing EBBs by about a third. This represents half of the distance between the best existing EBBs and an unattainable Bernstein bound constructed with perfect variance information.
Moreover, we demonstrate the use of our novel EBB in an \textit{upper-confidence bound} (UCB) multi-armed bandit (MAB) algorithm.  
Results from a set of MABs show that using our bound in a UCB algorithm outperforms existing approaches, by producing comparable or lower expected regret than employing other existing bounds, including state-of-the-art EBBs.

The paper is organised as follows. 
Related work and preliminary concepts are reviewed in Sections~\ref{sec:related-work} and~\ref{sec:preliminaries}, respectively.
Our main results are in Section~\ref{derivation}, where we derive %a novel probability bound for the sample variance, and use this to create 
a novel EBB.
In Section~\ref{evaluation} we evaluate our EBB and show its improvements over existing bounds. 
In Section~\ref{sec:bandits} we apply it to a multi-armed bandit problem as part of a UCB algorithm, which demonstrates how our tighter EBB improves the algorithm's learning performance.
Section \ref{sec:conclusion} concludes.

\section{Related Work}\label{sec:related-work}
Concentration inequalities are probabilistic bounds describing how far a random variable is expected to deviate from (or otherwise be concentrated around) a particular value.
Most classic concentration inequalities describe the expected deviation of sample statistics, including 
Chebyshev's inequality~\cite{Chebyshev1}, 
the Bernstein's inequalities~\cite{Burnstein1}, 
Hoeffding's inequalities~\cite{hoeffding1} and 
Bennett's inequalities~\cite{10.2307/2282438}.
Building on these, new analysis has yielded a wide range concentration inequalities and methods of generating them ~\cite{MR3363542,Boucheron2004}. 
In particular, recent innovations concern the concentration of more-general functions of random variables, such as 
the Efron-Stein~\cite{efron1981} and 
entropy methods~\cite{Boucheron_concentrationinequalities}, and 
applications of Talagrand's concentration inequality~\cite{Talagrand1995}.
Inequalities such as these are used to describe the expected variability of sample statistics, such as the distance of a sample mean from the population mean.

Furthermore, additional sample statistics can be used to tighten such bounds, because these statistics provide extra distributional information that are incorporated as a factor into classical inequalities. 
EBBs \cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15} are one example of this, where sample variance information is used to tighten a classical Bernstein bound.
However, it remains to be seen how far bounds derived by this approach can be tightened.

% In addition, concentration inequalities that describe sampling without replacement can give additional tightening over those that assume sampling with replacement. This refinement was first demonstrated in \cite{serfling1974} with a martingale argument.
% More recently, this result was improved with a reverse martingale argument and used to extend M\&P's EBB to the case of sampling without replacement \cite{bardenet2015}.
% Furthermore, if small sample sizes are assumed, then it may be possible to derive perfectly tight %ideal 
% concentration inequalities in some circumstances, and there do exist some computational methods to derive these perfect bounds more generally \cite{OUQ1,doi:10.1137/13094712X}.
% However, in this paper we focus on refining bounds in the case of sampling with replacement in the context of large numbers of samples.

\section{Preliminaries}\label{sec:preliminaries}

To begin, we state three lemmas which form the basis for our derivation (proofs in Appendix \ref{appendix:small}).
The first is an often used result related to union bounds:

\begin{lemma}[Probability Union]\label{prob_union}
For any random variables $a,b$ and $c$:
\[\p(a>c) \; \le \; \p(a>b) + \p(b>c)\]
\end{lemma}

This result is used to bound the probability relationship between two variables via knowledge of the probability relationship between them and a third variable.
%
The second definition relates the value of the sample mean and the value of sample squares to the sample variance. It is expanded here because we will later use these relationships to create bounds for the sample variance from bounds on the sample squares and sample mean.

\begin{lemma}[Variance Decomposition]\label{variance1}
For $n$ samples $x_i$, sample mean $\hat{\mu} = \frac{1}{n}\sum_ix_i$, sample variance $\hat{\sigma}^2=\frac{1}{n-1}\sum_i(x_i-\hat{\mu})^2$, and average of sample squares $\hat{\sigma}_0^2 = \frac{1}{n}\sum_ix_i^2$, the following relationship holds:
% \begin{align*}
% \quad\hat{\sigma}^2 
% &=\frac{1}{n-1}\sum_i\left(x_i-\frac{1}{n}\sum_jx_j \right)^2 
%  =\frac{1}{n-1}\left(\sum_ix_i^2-\frac{1}{n}\sum_{i,j}x_ix_j \right) % \\
% &= \frac{n}{n-1}\left(\hat{\sigma}_0^2-\hat{\mu}^2\right)
% \end{align*}
% which rearranging gives:
\[ 
\hat{\sigma}_0^2=\hat{\mu}^2+\frac{n-1}{n}\hat{\sigma}^2
\]
\end{lemma}

In order to derive our novel bound, we use the next lemma, which encapsulates a range of inequalities called \textit{Chernoff bounds} that give bounds on the mean of random variables:

\begin{lemma}[Chernoff Bound]\label{chernoff1}
If $\hat{\mu}$ is sample mean of $n$ independent and identically distributed samples of random variable $X$ then for any $s>0$ and $t$:
\[ \p(\hat{\mu}\ge t)\le\E\left[\exp(sX)\right]^n\exp(-snt) \]
\end{lemma}

The proof of this statement is straightforward and uses Markov's inequality and the i.i.d of the samples.
In the next section, we use these components to derive the bounds on the sample mean and the mean of sample squares, 
which we then use to create a new EBB.

\section{Derivation and numerical implementation}
\label{derivation}
In this section, we derive two Chernoff bounds, 
for the sample mean and the mean of sample squares, (Lemmas~\ref{sample_squares} and~\ref{variance2}, respectively). 
These are fused using a probability union and variance decomposition, defined above, to derive a bound for the sample variance. 
This bound is then used to derive our new EBB, as presented in Theorem~\ref{ebb1}.
However, due to its analytic intractability, we complete the derivation by discussing how to numerically implement the bound.

\subsection{Derivation}
Our first probability bound is a Chernoff bound on the sample mean called \textit{Bennett's inequality}. 
This bound is not new and was derived by \cite{hoeffding1} and \cite{10.2307/2282438} and has subsequently been a subject of discussion and many further developments \cite{Bentkus08boundsfor,Pinelis2014,zbMATH00812598}; we %give a statement of Bennett's inequality as lemma \ref{hoeffdings1} and also 
provide a proof in Appendix \ref{appendix:A}.

\begin{theorem}[Bennett's inequality]\label{hoeffdings1}
Let $X$ be a real-valued random variable with a mean of zero and variance $\sigma^2$, that is bounded $a\le X\le b$. 
Then for $t>0$, the mean $\hat{\mu}$ of $n$ samples of $X$ is probability bounded by:
\begin{equation}\label{eq_no2}\p(\hat{\mu}\ge t)\le H_1^n\left(\frac{\sigma^2}{b^2},\frac{t}{b}\right),
\end{equation}
where:
\begin{equation*}
H_1^n\left(\frac{\sigma^2}{b^2},\frac{t}{b}\right) =
\left(\left(\frac{\frac{\sigma^2}{b^2}}{\frac{\sigma^2}{b^2}+\frac{t}{b}}\right)^{\frac{\sigma^2}{b^2}+\frac{t}{b}}
\left(1-\frac{t}{b}\right)^{\frac{t}{b}-1}\right)^{\frac{n}{\frac{\sigma^2}{b^2}+1}}
\end{equation*}
\end{theorem}

We will also use a double-sided version of this bound:
\begin{equation}\label{eq_no1}\p(\hat{\mu}^2\ge r^2) \le H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right) + H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right) \end{equation}

The assumption that the mean is zero can be used without a loss of generality.
In this way, Bennett's inequality gives us a probability bound for the difference of the sample mean from the true mean \textit{given the variance}.

However, often in practice the variance is unknown, 
but can only estimate it via a sample variance statistic.
Thus, we derive a bound the difference of the sample variance from the variance as follows (proof in Appendix \ref{appendix:B}):

\begin{lemma}[Sample square bound]\label{sample_squares}
Let $X$ be a real-valued random variable with a mean of zero and variance $\sigma^2$, that is bounded $a\le X\le b$, if $d=\max(b,-a)$ then for $y>0$, the mean of sample squares $\hat{\sigma}_0^2=\frac{1}{n}\sum_ix_i^2$ is probability bounded:
\begin{equation}\label{equation_squares}\p(\sigma^2 - \hat{\sigma}_0^2> y) \le H_2^n\left(\frac{\sigma^2}{d^2},\frac{y}{d^2}\right),
\end{equation}
where:
\begin{align*} H_2^n\left(\frac{\sigma^2}{d^2},\frac{y}{d^2}\right) = \left(
\left(\frac{1-\frac{\sigma^2}{d^2}}{1+\frac{y}{d^2}-\frac{\sigma^2}{d^2}}\right)^{1+\frac{y}{d^2}-\frac{\sigma^2}{d^2}}
\left(\frac{\frac{\sigma^2}{d^2}}{\frac{\sigma^2}{d^2}-\frac{y}{d^2}}\right)^{\frac{\sigma^2}{d^2}-\frac{y}{d^2}}
\right)^n
\end{align*}
\end{lemma}

It is worth noting that we choose to restrict the use of function $H_2^n$ to cases which are sensible for it to be applied:
(i) it is defined for $a<0<b$, because otherwise the mean could not be zero), and (ii) $\sigma^2\le-ab\le (b-a)^2/4$ by Popoviciu's inequality \cite{zbMATH05780164}, as it is not possible for the variance to be larger given the width of the data bounds.  
It is important that these domain restrictions are conserved with the analysis.

At this point, we have a probability bound on the mean squared (Equation \ref{eq_no1}) 
and a probability bound on the sample squares (Lemma \ref{sample_squares}). With these in hand, we use lemma \ref{variance1} to create a bound on the sample variance, as follows.

\begin{lemma}[Sample Variance Bound]\label{variance2}
For a random variable that is bounded $a\le X\le b$ with variance $\sigma^2$ and a mean of zero, if $d=\max(b,-a)$ then for $w>0$, the sample variance $\hat{\sigma}^2$ of $n$ samples is probability bounded by:
\begin{equation}\label{eq_no8}
\p(\sigma^2 - \hat{\sigma}^2 > w) \le H_3^n(a,b,w,\sigma^2),
\end{equation}
where:
\begin{align*} H_3^n(a,b,w,\sigma^2) =\min_{\phi\in[0,1]}
\begin{Bmatrix}
	H_1^n\left(\frac{\sigma^2}{b^2},\frac{\sqrt{\phi(\frac{n-1}{n}w+\frac{1}{n}\sigma^2)}}{b}\right)\\
	+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-\sqrt{\phi(\frac{n-1}{n}w+\frac{1}{n}\sigma^2)}}{a}\right)\\
	+H_2^n\left(\frac{\sigma^2}{d^2},\frac{(1-\phi)(\frac{n-1}{n}w+\frac{1}{n}\sigma^2)}{d^2}\right)
\end{Bmatrix}\end{align*}
\end{lemma}

A proof is provided in Appendix \ref{appendix:B}.
The use of the function $H_3^n$ is subject to the same restrictions on its domain as $H_2^n$.
Thus, in Lemma \ref{hoeffdings1} we have a bound for the sample mean given the variance, and in Lemma \ref{variance2} we have a probability bound for the difference of the sample variance from the population variance. 
Next, we outline a method of combining these two to create a bound for the sample mean given the sample variance --- and thereby derive a new empirical Bernstein bound.
To do this, we now expound a theorem that embodies a process %slightly improved
followed by M\&P \cite{Maurer50empiricalbernstein}.

Before beginning, we introduce some notation.
For a function $f$ with ordered inputs, 
we denote the inverse of $f$ with respect to its $i${th} input 
(counting from one) as $f^{-(i)}$, assuming it exists.
Denote probability bounds on the differences of the sample mean from the mean, and the sample variance from the variance, by
$\p(\hat{\mu}-\mu>t)\le h(\sigma^2,t)$ and $\p(\sigma^2-\hat{\sigma}^2>w)\le f(\sigma^2,w)$, respectively.
Note that functions $h$ and $f$ have arguments $\sigma^2$ and $t$, and $\sigma^2$ and $w$, respectively.

\newpage

\begin{theorem}[Essential EBB]\label{ebb1} 
Assume $f^{-(2)}$ and $h^{-(2)}$ both exist, and also if $h^{-(2)}$ is monotonically increasing in its first argument, so that we can define:
\[
z(\sigma^2,w) = \sigma^2-f^{-(2)}\left(\sigma^2,w\right)
\]
If $z^{-(1)}$ exists and is monotonic increasing in its first argument, then for any $x\in[0,y]$, the following relationship holds:
\[
\p\left(\hat{\mu}-\mu>h^{-(2)}\left(z^{-(1)}\left(\hat{\sigma}^2,y-x\right),x\right)\right)
\le y
\]
\end{theorem}
%
\begin{proof}
Substituting $w$ for $f^{-2}(\sigma^2,w)$ gives:
%$\p(\sigma^2-\hat{\sigma}^2>f^{-2}(\sigma^2,w))\le w$\\
%$\p(z(\sigma^2,w)>\hat{\sigma}^2)\le w$\\
%$\p(\sigma^2>z^{-1}(\hat{\sigma}^2,w))\le w$\\
%$\p(h^{-2}(\sigma^2,t)>h^{-2}(z^{-1}(\hat{\sigma}^2,w),t))\le w$\\
\begin{align*}
w & \ge \p\left(\sigma^2-\hat{\sigma}^2>f^{-(2)}\left(\sigma^2,w\right)\right)\\
 & \ge \p\left(z\left(\sigma^2,w\right)>\hat{\sigma}^2\right)\\
 & \ge \p\left(\sigma^2>z^{-(1)}\left(\hat{\sigma}^2,w\right)\right)\\
 & \ge \p\left(h^{-2}\left(\sigma^2,t\right)>h^{-(2)}\left(z^{-(1)}\left(\hat{\sigma}^2,w\right),t\right)\right)
\end{align*}
% $w  \ge \p(\sigma^2-\hat{\sigma}^2>f^{-2}(\sigma^2,w))$\\
% \-\hspace{4mm}$\ge \p(z(\sigma^2,w)>\hat{\sigma}^2)$\\
% \-\hspace{4mm}$\ge \p(\sigma^2>z^{-1}(\hat{\sigma}^2,w))$\\
% \-\hspace{4mm}$\ge \p(h^{-2}(\sigma^2,t)>h^{-2}(z^{-1}(\hat{\sigma}^2,w),t))$\\
Substituting $t$ for $h^{-(2)}(\sigma^2,t)$ gives:
\[
\p\left(\hat{\mu}-\mu>h^{-(2)}\left(\sigma^2,t\right)\right)
\le t.
\]
Applying probability union (lemma \ref{prob_union}) gives:\\
\[
\p\left(\hat{\mu}-\mu>h^{-(2)}\left(z^{-(1)}\left(\hat{\sigma}^2,w\right),t\right)\right)
\le t+w.
\]
Letting $y=t+w$ and $x=y-w$ completes the proof.$\hfill\blacksquare$
\end{proof}

The result of this Theorem is an EBB, and our novel EBB is completed by substituting  $h(\sigma^2,t)=H_1^n\left(\sigma^2/b^2,t/b\right)$ and $f(\sigma^2,w)=H_3^n\left(a,b,w,\sigma^2\right)$ into Theorem \ref{ebb1}. 
Care must be taken in applying this theorem that all the assumptions hold, 
the inverses exist, and the domains of the functions are propagated through the analysis.

\subsection{Numerical Implementation}
\label{numerical-implementation}
Analytically solving this new EBB is challenging, however it is possible to evaluate it to arbitrary accuracy using numerical techniques.
This section provides a high-level description of a process for calculating our EBB.\footnote{sourcecode available at:\\\url{https://github.com/Markopolo141/Engineered-Empirical-Bernstein-Bound}}

This calculation is composed of three primary parts:
(i) the computation of function $f(\sigma^2,w)=H_3^n(a,b,y,\sigma^2)$;
(ii) verifying that the assumptions of Theorem \ref{ebb1} hold for $h(\sigma^2,t)=H_1$ and $f(\sigma^2,w)=H_3$, and;
(iii) calculating the subsequent result of Theorem \ref{ebb1}.

First, the function $f(\sigma^2,w)=H_3^n(a,b,w,\sigma^2)$ is the solution to an optimization problem that solves for the minima of an objective function subject to constraint $\phi\in[0,1]$.
Despite its complexity, a solution can be found quickly using a single variable parameter sweep.

Second, it is necessary to verify the assumptions that $h^{-(2)}$, $f^{-(2)}$ and $z^{-(1)}$ exist and that $z^{-(1)}$ and $f^{-(2)}$ are monotonically increasing in their first argument.
It is easy to note that $h(\sigma^2,t)=H_1^n\left(\sigma^2/b^2,t/b\right)$ is a closed-form function that is monotonically decreasing from $1$ to $0$ on the second argument, so $h^{-(2)}$ exists and is monotonically increasing in its first argument.  However the remaining assumptions are more difficult to verify.
For any function, the values that the function takes can be plotted as an array of points and the values that the inverse of that function takes can be determined by conducting coordinate swaps on those points.
The values of $f(\sigma^2,w)=H_3^n(a,b,w,\sigma^2)$ were computed and were seen to be monotonically decreasing in its second argument confirming that $f^{-(2)}$ exists.
The function $z(\sigma^2,w)=\sigma^2-f^{-(2)}\left(\sigma^2,w\right)$ is then seen to be a manipulation on the coordinate swapped points of $f(\sigma^2,w)=H_3^n(a,b,w,\sigma^2)$.
By coordinate swapping again, $z^{-(1)}$ was seen to be a regular function monotonically increasing on its first argument, hence satisfying assumptions.

Third, to numerically calculate the result of Theorem \ref{ebb1} the functions $h^{-(2)}$ and $z^{-(1)}$ were numerically evaluated by direct parameter searches and then composed as:
$h^{-(2)}(z^{-(1)}(\hat{\sigma}^2,y-x),x)$ - which is the inner part of the expression of the new EBB parameterised by $x$ explicitly and also $a,b$ implicitly.
%
However we typically don't know the values of $a$ and $b$, but instead know the mean is somewhere within a finite interval of width $D=b-a$.
Given this, we then take the worst case values of $a$ and $b$ consistent with a given $D$, 
and then take the best $x\in[0,y]$ subject to all other bounds.

\section{Comparison to existing bounds}\label{evaluation}
In this section, we make three comparisons of our results to existing concentration bounds, namely (i) Lemma \ref{variance2} is compared to M\&P's entropic bound, then 
our EBB is compared to (ii) M\&P's EBB and (iii) Bennett's inequality with perfect variance information.

First, M\&P's entropic bound \cite{Maurer50empiricalbernstein} 
(originally presented in \cite{MR2245497}) 
is given by:
\begin{equation}\label{eq:fe} 
\p(\sigma^2 - \hat{\sigma}^2>w) \le \exp\left(\frac{-(n-1)w^2}{2\sigma^2D^2}\right) 
\end{equation}
%
The improvement our variance bound (Lemma \ref{variance2}) offers over theirs is given by:
\begin{align}
Y\left(\frac{\sigma^2}{D^2},\frac{w}{D^2},n\right)
 =\exp\left(\frac{-(n-1)w^2}{2\sigma^2D^2}\right) -\max_{b} H_3^n\left(D(1-b),Db,w,\sigma^2\right)\label{eq:advantage}
\end{align}
where $b$ has a viable range between $0.5$ and $0.5-\sqrt{0.25-\sigma^2/D^2}$ (via Popoviciu's inequality).
Figure \ref{biggraph2} plots this improvement against $\sigma^2$ and $w$ for $n=200$, which shows large regions of advantage.
However, it is possible to use the minima of several different variance bounds, so in constructing our EBB, we take the minima of our variance bound and the entropic bound.

Second, we compare our EBB directly with M\&P's EBB~\cite{Maurer50empiricalbernstein}, 
given by:
\begin{equation}\label{maurersbound} \p\left(\mu-\hat{\mu}>\sqrt{\frac{2\hat{\sigma}^2\log(2/y)}{n}}+\frac{7D\log(2/y)}{3(n-1)}\right)<y. \end{equation}
In order to fairly compare our EBB to M\&P's we apply Popoviciu's inequality as a domain restriction, 
and carry it through their derivation, as we did to our own EBB. 
Specifically, this is the domain where:
\[ \frac{1}{2}>\frac{\sqrt{\hat{\sigma}^2}}{D}+\sqrt{\frac{2\log(2/y)}{n-1}} \]
We plot the improvement our EBB offers in this domain, as shown in Figure \ref{biggraph3}. 
In this plot, a probability 0.5 bound is shown to shrink by approximately one third.
More generally, we observe that our refinement of M\&P's EBB is be uniformly tighter across a large range of values.

\begin{figure}[t!]
\centering
\begin{tikzpicture}[scale=0.8]
	\begin{axis}[
	xmin=0,   xmax=0.25,
	ymin=0,   ymax=0.25,
	zmin=-0.15,   zmax=1.0,
	xtick={0.05,0.10,0.15,0.20,0.25},
	ytick={0.05,0.10,0.15,0.20},
	%ztick={-0.2,-0.1,0,0.1},
	xlabel=$\frac{\sigma^2}{D^2}$,
	ylabel=$\frac{w}{D^2}$,
	%zlabel=$blah$,
	xticklabel style={/pgf/number format/fixed},
	yticklabel style={/pgf/number format/fixed},
	zticklabel style={/pgf/number format/fixed},
	view={-105}{35},
	%point meta min=-0.3, point meta max=0.3,
	point meta min=-0.1, point meta max=1.0,
	title={Advantage over Entropic bound for n=200},
	%colorbar horizontal,
	colorbar,
	colorbar style={
		at={(1.07,0.64)},
		%title=Advantage,
		%ylabel=Z-value,
		%ytick={-1,-0.75,...,1},
		height=0.52*\pgfkeysvalueof{/pgfplots/parent axis height},
		xticklabel style={
			text width=2.5em,
			%align=below,
			%anchor=north west,
			/pgf/number format/.cd,
			fixed,
			fixed zerofill
		}
	}
	]
	\addplot3[patch, shader=flat] 
	file
	{graph1.dat};
	\end{axis}
\end{tikzpicture}
	\vspace{-5pt}
\caption{The strength of our variance bound over Maurer's Entropic bound. The graph of $Y\left(\frac{\sigma^2}{D^2},\frac{w}{D^2},n\right)$ from Equation \ref{eq:advantage}}\label{biggraph2}
\end{figure}

\begin{figure}[]{}
    \centering
	\begin{tikzpicture}
	\begin{axis}[
		title={Bound reduction of our EBB over  Maurer and Pontil’s},
		xlabel={$\hat{\sigma}^2/D^2$},
		xmin=0, xmax=0.25,
		ymin=25, ymax=40,
		xtick={0,0.05,0.1,0.15,0.2,0.25},
		ytick={30,35,40},
		yticklabel=$\pgfmathprintnumber{\tick}\%$,
		ymajorgrids=true,
		grid style=dashed,
		xticklabel style={/pgf/number format/fixed},
	]
	\addplot[] coordinates {
(0.0, 10.038489469957923)(0.005, 23.729228874038338)(0.01, 26.46795119155083)(0.015, 28.061119743643296)(0.02, 29.141938583623652)(0.025, 30.066155991693723)(0.03, 30.907282335052788)(0.035, 31.738722848538305)(0.04, 32.54914392836502)(0.045, 33.05291848928947)(0.05, 33.651509619741496)(0.055, 34.151805087746446)(0.06, 34.768247610158575)(0.065, 35.35764746719292)
		}node[pos=1.0](endofplotsquare){} ;
	\node [above] at (endofplotsquare) {$\scriptstyle n=50$};
	\addplot[] coordinates {
(0.0, 12.591458904845746)(0.005, 26.08582516018055)(0.01, 28.044488963240152)(0.015, 29.219014176778845)(0.02, 30.101019545112305)(0.025, 30.739739304373572)(0.03, 31.209391146592484)(0.035, 31.67459564986504)(0.04, 32.10560417423678)(0.045, 32.53522214247566)(0.05, 32.98480753922602)(0.055, 33.33123349968554)(0.06, 33.66064263107598)(0.065, 33.983296057116895)(0.07, 34.371432119724126)(0.075, 34.76400092304011)(0.08, 35.165771922230526)(0.085, 35.51929445366766)(0.09, 35.890640326573575)
		}node[pos=1.0](endofplotsquare){} ;
	\node [above] at (endofplotsquare) {$\scriptstyle n=75$};
	\addplot[] coordinates {
(0.0, 14.817995440815901)(0.005, 27.90751007185735)(0.01, 29.219819451516923)(0.015, 30.070639062533996)(0.02, 30.629290720122317)(0.025, 31.104197838170627)(0.03, 31.14038996461402)(0.035, 31.62526607199946)(0.04, 31.911575841232846)(0.045, 32.3187069670152)(0.05, 32.59698646227685)(0.055, 32.85814963311234)(0.06, 33.115830685662)(0.065, 33.379908028841236)(0.07, 33.578110917203176)(0.075, 33.87653264786374)(0.08, 34.19803078792182)(0.085, 34.470564003329045)(0.09, 34.774201537103245)(0.095, 35.03784322660741)(0.1, 35.337583634279)(0.105, 35.60362789769355)(0.11, 35.90890662248758)
		}node[pos=1.0](endofplotsquare){} ;
	\node [above right] at (endofplotsquare) {$\scriptstyle n=100$};
	\addplot[] coordinates {
(0.0, 17.342661445161745)(0.005, 29.461247776997926)(0.01, 30.502124709956824)(0.015, 30.94634600450878)(0.02, 31.116833768989828)(0.025, 31.344627574353588)(0.03, 31.62499327739429)(0.035, 31.772139980592)(0.04, 31.975727165299386)(0.045, 32.02196228998142)(0.05, 32.183034431467235)(0.055, 32.352369659168474)(0.06, 32.54250416890406)(0.065, 32.87047963677422)(0.07, 33.017679271803296)(0.075, 33.31333732160584)(0.08, 33.55087101615144)(0.085, 33.53938459819124)(0.09, 33.68714872653657)(0.095, 33.89275583281304)(0.1, 34.15600891069251)(0.105, 34.290920495879966)(0.11, 34.57974857223946)(0.115, 34.747357884723435)(0.12, 34.97811379083637)(0.125, 35.09584827017029)(0.13, 35.36531839253051)
		}node[pos=1.0](endofplotsquare){} ;
	\node [above right] at (endofplotsquare) {$\scriptstyle n=150$};
	\addplot[] coordinates {
(0.0, 19.269181617386778)(0.005, 30.47328215171227)(0.01, 30.970505248952783)(0.015, 31.155076903228505)(0.02, 31.370737591330126)(0.025, 31.563153411429678)(0.03, 31.716924278688328)(0.035, 31.602163041853583)(0.04, 31.762160711176872)(0.045, 31.905759719654245)(0.05, 32.05956774531062)(0.055, 32.101874254626836)(0.06, 32.32639539364612)(0.065, 32.465858041087344)(0.07, 32.663895247621326)(0.075, 32.797586647322234)(0.08, 32.99998541625402)(0.085, 33.15092115439265)(0.09, 33.13907818080335)(0.095, 33.32527974281349)(0.1, 33.47347491095124)(0.105, 33.70030345616673)(0.11, 33.78337094262078)(0.115, 33.94866206353597)(0.12, 34.19406008169977)(0.125, 34.30666804274627)(0.13, 34.5014054670121)(0.135, 34.67351335871075)(0.14, 34.82497129829329)(0.145, 34.95753413863828)
		}node[pos=1.0](endofplotsquare){} ;
	\node [right] at (endofplotsquare) {$\scriptstyle n=200$};
	\addplot[] coordinates {
(0.0, 21.01455983414305)(0.005, 31.398323351742654)(0.01, 31.29316800287044)(0.015, 31.380044700971307)(0.02, 31.499573558604126)(0.025, 31.501955199548522)(0.03, 31.342388805161228)(0.035, 31.555898653589576)(0.04, 31.540720961712708)(0.045, 31.556719994430246)(0.05, 31.815518124296712)(0.055, 31.947447662218103)(0.06, 31.979020008525413)(0.065, 31.929950573976118)(0.07, 32.151946530365926)(0.075, 32.30372613153442)(0.08, 32.39631985663968)(0.085, 32.28147349936643)(0.09, 32.43775937546441)(0.095, 32.55064623256504)(0.1, 32.77372870056995)(0.105, 32.81284419609248)(0.11, 32.96572615770543)(0.115, 32.94748952790814)(0.12, 33.04474761150041)(0.125, 33.25359991684834)(0.13, 33.30204392434083)(0.135, 33.462830030160355)(0.14, 33.601886363972085)(0.145, 33.7211101175424)(0.15, 33.822185822075845)(0.155, 33.90661477833436)(0.16, 34.09961256888578)
		}node[pos=1.0](endofplotsquare){} ;
	\node [right] at (endofplotsquare) {$\scriptstyle n=300$};
	\addplot[] coordinates {
(0.0, 23.733576061543907)(0.005, 31.93999128292596)(0.01, 31.642400396531094)(0.015, 31.54212092349261)(0.02, 31.12052542652318)(0.025, 31.129819611252405)(0.03, 31.344098301521242)(0.035, 31.231838999520004)(0.04, 31.185453514912005)(0.045, 31.51029078782499)(0.05, 31.401697787018254)(0.055, 31.43592520457107)(0.06, 31.367624957687056)(0.065, 31.45753767654653)(0.07, 31.468778394474676)(0.075, 31.6423499409508)(0.08, 31.751037287923307)(0.085, 31.804794091938522)(0.09, 31.59991862434968)(0.095, 31.778311022724473)(0.1, 31.913384999263183)(0.105, 32.010501900631745)(0.11, 32.074189915872516)(0.115, 31.915973789453584)(0.12, 32.11613625130849)(0.125, 32.10053700848796)(0.13, 32.24708311545571)(0.135, 32.3692691037866)(0.14, 32.46936498795406)(0.145, 32.54937215145163)(0.15, 32.61106237732128)(0.155, 32.65601018366708)(0.16, 32.85390573088976)(0.165, 32.867317678660584)(0.17, 33.03199624865481)(0.175, 33.01872182909822)(0.18, 33.15487119563348)
		}node[pos=1.0](endofplotsquare){} ;
	\node [right] at (endofplotsquare) {$\scriptstyle n=500$};
	\addplot[] coordinates {
(0.0, 26.48466951022569)(0.005, 31.610541001763814)(0.01, 31.094245131329373)(0.015, 30.691021818068354)(0.02, 30.878933354114203)(0.025, 30.854623560301786)(0.03, 30.855718952687877)(0.035, 30.985476785778605)(0.04, 30.84839664811395)(0.045, 30.94907807084863)(0.05, 30.882232292715344)(0.055, 30.68950445827823)(0.06, 30.77857995587979)(0.065, 30.768677505684852)(0.07, 30.679146150855704)(0.075, 30.870441770906094)(0.08, 30.653781659199446)(0.085, 30.72198559607093)(0.09, 30.738566645167236)(0.095, 30.710992728150178)(0.1, 30.95229310334558)(0.105, 30.847606478652455)(0.11, 31.009527688997892)(0.115, 31.135832380489546)(0.12, 30.946326663430018)(0.125, 31.017664917855072)(0.13, 31.06348584444511)(0.135, 31.08638415275851)(0.14, 31.0886271157673)(0.145, 31.072204850949028)(0.15, 31.29715291414822)(0.155, 31.244828197450204)(0.16, 31.429852460842593)(0.165, 31.347766957340134)(0.17, 31.49894525891586)(0.175, 31.63356906325342)(0.18, 31.514234978296805)(0.185, 31.62214364046394)(0.19, 31.716729481001114)(0.195, 31.79891328121711)(0.2, 31.869534804168858)
		}node[pos=1.0](endofplotsquare){} ;
	\node [below] at (endofplotsquare) {$\scriptstyle n=1000$};
	\end{axis}
	\end{tikzpicture}
	\vspace{-10pt}
	\caption{The percent reduction of the 0.5 probability bound, that going from Maurer and Pontil's EBB to our EBB would achieve, for various $n$, in the domain valid for their EBB.}
	\label{biggraph3}

	\vspace{15pt}

	\begin{tikzpicture}
	\begin{axis}[
		title={Potential bound reduction with $\hat{\sigma}^2 = \sigma^2$ over our EBB},
		xlabel={$\hat{\sigma}^2/D^2$},
		xmin=0, xmax=0.25,
		ymin=0, ymax=100,
		xtick={0,0.05,0.1,0.15,0.2,0.25},
		ytick={0,20,40,60,80,100},
		yticklabel=$\pgfmathprintnumber{\tick}\%$,
		legend pos=south west,
		ymajorgrids=true,
		grid style=dashed,
		xticklabel style={/pgf/number format/fixed},
	]
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 75.02420135527589)(0.01, 68.58202038924931)(0.015, 64.13237924865832)(0.02, 60.71118820468343)(0.025, 57.819103972950124)(0.03, 55.33498759305211)(0.035, 53.04630381803412)(0.04, 50.96)(0.045, 49.21383647798742)(0.05, 47.51937984496124)(0.055, 46.02446483180428)(0.06, 44.47806354009077)(0.065, 42.99625468164794)(0.07, 41.57386785449146)(0.075, 40.20618556701031)(0.08, 38.93352812271731)(0.085, 37.63596809282088)(0.09, 36.38328530259366)(0.095, 35.17191977077364)(0.1, 34.04558404558404)(0.105, 32.88447909284196)(0.11, 31.68666196189132)(0.115, 30.639494026704146)(0.12, 29.481792717086833)(0.125, 28.35195530726257)(0.13, 27.228412256267408)(0.135, 26.0778859527121)(0.14, 24.930555555555557)(0.145, 24.31129476584022)(0.15, 23.140495867768596)(0.155, 21.862068965517242)(0.16, 20.525224602626125)(0.165, 19.8489010989011)(0.17, 18.413793103448278)(0.175, 17.707618393960193)(0.18, 15.975103734439834)(0.185, 15.161957270847692)(0.19, 14.36426116838488)(0.195, 13.452299245024022)(0.2, 12.542837559972584)(0.205, 11.51473612063057)(0.21, 13.115845539280958)(0.215, 12.117177097203728)(0.22, 13.71280724450194)(0.225, 17.65424557116677)(0.23, 25.69558101472995)(0.235, 35.30794546309356)(0.24, 56.085994309200125)
		}node[pos=0.4](endofplotsquare){} ;
	\node [above right] at (endofplotsquare) {$\scriptstyle n=50$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 70.89337175792507)(0.01, 63.881401617250674)(0.015, 59.23076923076923)(0.02, 55.66502463054187)(0.025, 52.67538644470868)(0.03, 50.345622119815665)(0.035, 48.20627802690583)(0.04, 46.2800875273523)(0.045, 44.646680942184155)(0.05, 42.96218487394958)(0.055, 41.54639175257732)(0.06, 40.22289766970618)(0.065, 38.983050847457626)(0.07, 37.75811209439528)(0.075, 36.50485436893204)(0.08, 35.31669865642994)(0.085, 34.25047438330171)(0.09, 33.23943661971831)(0.095, 32.18604651162791)(0.1, 31.152073732718893)(0.105, 30.228310502283104)(0.11, 29.257246376811594)(0.115, 28.39173405211141)(0.12, 27.475468331846567)(0.125, 26.572187776793623)(0.13, 25.704225352112676)(0.135, 24.84689413823272)(0.14, 23.93385552654482)(0.145, 23.03030303030303)(0.15, 22.155172413793103)(0.155, 21.28755364806867)(0.16, 20.35928143712575)(0.165, 19.453924914675767)(0.17, 18.46808510638298)(0.175, 17.502124044180118)(0.18, 16.397621070518266)(0.185, 15.306122448979592)(0.19, 14.054514480408859)(0.195, 13.463166807790008)(0.2, 11.925042589437819)(0.205, 11.205432937181664)(0.21, 10.414902624894157)(0.215, 9.551986475063398)(0.22, 8.622147083685546)(0.225, 10.262725779967159)(0.23, 11.961722488038278)(0.235, 20.45616535994298)(0.24, 34.51481696687972)
		}node[pos=0.693](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$\scriptstyle n=75$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 67.61904761904762)(0.01, 60.31468531468531)(0.015, 55.5921052631579)(0.02, 51.95618153364632)(0.025, 49.0990990990991)(0.03, 46.97406340057637)(0.035, 44.75524475524475)(0.04, 42.93478260869565)(0.045, 41.246684350132625)(0.05, 39.766839378238345)(0.055, 38.40304182509506)(0.06, 37.142857142857146)(0.065, 35.97560975609756)(0.07, 34.97005988023952)(0.075, 33.844339622641506)(0.08, 32.7906976744186)(0.085, 31.76605504587156)(0.09, 30.804077010192525)(0.095, 29.86577181208054)(0.1, 28.98230088495575)(0.105, 28.11816192560175)(0.11, 27.302275189599133)(0.115, 26.394849785407725)(0.12, 25.61105207226355)(0.125, 24.94736842105263)(0.13, 24.217118997912316)(0.135, 23.316062176165804)(0.14, 22.633744855967077)(0.145, 21.859039836567927)(0.15, 21.196754563894523)(0.155, 20.141700404858298)(0.16, 19.335347432024168)(0.165, 18.61861861861862)(0.17, 17.74675972083749)(0.175, 17.063492063492063)(0.18, 16.12265084075173)(0.185, 15.369458128078819)(0.19, 14.454277286135694)(0.195, 13.555992141453832)(0.2, 12.561334641805692)(0.205, 11.307767944936087)(0.21, 9.881422924901186)(0.215, 9.251968503937007)(0.22, 8.537782139352306)(0.225, 7.647058823529412)(0.23, 9.333333333333334)(0.235, 11.00832562442183)(0.24, 24.0625)(0.245, 55.32786885245902)
		}node[pos=1.0](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$n=100$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 62.98342541436464)(0.01, 55.223880597014926)(0.015, 50.23041474654378)(0.02, 46.753246753246756)(0.025, 44.03292181069959)(0.03, 41.61735700197239)(0.035, 39.84819734345351)(0.04, 37.981651376146786)(0.045, 36.58969804618117)(0.05, 35.233160621761655)(0.055, 34.00673400673401)(0.06, 32.89473684210526)(0.065, 31.612903225806452)(0.07, 30.647709320695103)(0.075, 29.658385093167702)(0.08, 28.702290076335878)(0.085, 27.994011976047904)(0.09, 27.245949926362297)(0.095, 26.41509433962264)(0.1, 25.644699140401148)(0.105, 24.858757062146893)(0.11, 24.022346368715084)(0.115, 23.448275862068964)(0.12, 22.646657571623464)(0.125, 22.10242587601078)(0.13, 21.36181575433912)(0.135, 20.871862615587848)(0.14, 20.157068062827225)(0.145, 19.58495460440986)(0.15, 19.02313624678663)(0.155, 18.471337579617835)(0.16, 17.825537294563844)(0.165, 17.189460476787954)(0.17, 16.375)(0.175, 15.77639751552795)(0.18, 15.061728395061728)(0.185, 14.478527607361963)(0.19, 13.480392156862745)(0.195, 12.804878048780488)(0.2, 12.257281553398059)(0.205, 10.94890510948905)(0.21, 10.194174757281553)(0.215, 9.101941747572816)(0.22, 7.907542579075426)(0.225, 7.38498789346247)(0.23, 6.521739130434782)(0.235, 5.669481302774427)(0.24, 10.136674259681094)(0.245, 33.693843594009984)
		}node[pos=1.0](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$n=150$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 59.642857142857146)(0.01, 51.41955835962145)(0.015, 46.820809248554916)(0.02, 43.24324324324324)(0.025, 40.40920716112532)(0.03, 38.292682926829265)(0.035, 36.5967365967366)(0.04, 34.831460674157306)(0.045, 33.47826086956522)(0.05, 32.06751054852321)(0.055, 30.942622950819672)(0.06, 29.8)(0.065, 28.90625)(0.07, 27.915869980879542)(0.075, 26.96629213483146)(0.08, 26.102941176470587)(0.085, 25.270758122743683)(0.09, 24.778761061946902)(0.095, 24.041811846689896)(0.1, 23.32761578044597)(0.105, 22.504230118443317)(0.11, 22.0)(0.115, 21.38157894736842)(0.12, 20.650406504065042)(0.125, 20.064205457463885)(0.13, 19.523809523809526)(0.135, 18.838304552590266)(0.14, 18.322981366459626)(0.145, 17.81874039938556)(0.15, 17.35159817351598)(0.155, 16.867469879518072)(0.16, 16.417910447761194)(0.165, 15.828402366863905)(0.17, 15.27165932452276)(0.175, 14.847161572052402)(0.18, 14.057971014492754)(0.185, 13.525179856115107)(0.19, 13.0)(0.195, 12.357954545454545)(0.2, 11.614730878186968)(0.205, 10.985915492957746)(0.21, 10.0)(0.215, 9.396914446002805)(0.22, 8.531468531468532)(0.225, 7.5524475524475525)(0.23, 6.3113604488078545)(0.235, 5.594405594405594)(0.24, 7.462686567164179)(0.245, 23.214285714285715)
		}node[pos=1.0](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$n=200$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 54.54545454545455)(0.01, 46.52173913043478)(0.015, 41.732283464566926)(0.02, 38.32116788321168)(0.025, 35.95890410958904)(0.03, 33.980582524271846)(0.035, 31.888544891640866)(0.04, 30.56379821958457)(0.045, 29.428571428571427)(0.05, 27.977839335180054)(0.055, 26.881720430107528)(0.06, 25.848563968668408)(0.065, 25.126903553299492)(0.07, 24.069478908188586)(0.075, 23.300970873786408)(0.08, 22.565320665083135)(0.085, 22.273781902552205)(0.09, 21.4123006833713)(0.095, 20.80536912751678)(0.1, 20.044052863436125)(0.105, 19.696969696969695)(0.11, 18.976545842217483)(0.115, 18.658280922431867)(0.12, 18.181818181818183)(0.125, 17.551020408163264)(0.13, 17.10261569416499)(0.135, 16.69980119284294)(0.14, 16.110019646365423)(0.145, 15.728155339805825)(0.15, 15.355086372360844)(0.155, 14.990512333965844)(0.16, 14.473684210526315)(0.165, 14.12639405204461)(0.17, 13.627992633517495)(0.175, 13.138686131386862)(0.18, 12.681159420289855)(0.185, 12.050359712230216)(0.19, 11.764705882352942)(0.195, 11.327433628318584)(0.2, 10.73943661971831)(0.205, 10.13986013986014)(0.21, 9.40766550522648)(0.215, 8.996539792387543)(0.22, 8.290155440414507)(0.225, 7.253886010362694)(0.23, 6.540447504302926)(0.235, 5.344827586206897)(0.24, 4.810996563573883)(0.245, 11.67192429022082)
		}node[pos=1.0](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$n=300$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 48.091603053435115)(0.01, 40.38461538461539)(0.015, 36.0)(0.02, 32.8125)(0.025, 30.58252427184466)(0.03, 28.440366972477065)(0.035, 26.956521739130434)(0.04, 25.726141078838175)(0.045, 24.0)(0.05, 23.46153846153846)(0.055, 22.304832713754646)(0.06, 21.58273381294964)(0.065, 20.97902097902098)(0.07, 20.068027210884352)(0.075, 19.269102990033222)(0.08, 18.83116883116883)(0.085, 18.095238095238095)(0.09, 17.956656346749227)(0.095, 17.325227963525837)(0.1, 16.71641791044776)(0.105, 16.129032258064516)(0.11, 15.85014409221902)(0.115, 15.536723163841808)(0.12, 15.041782729805014)(0.125, 14.794520547945206)(0.13, 14.324324324324325)(0.135, 13.866666666666667)(0.14, 13.421052631578947)(0.145, 13.246753246753247)(0.15, 12.820512820512821)(0.155, 12.658227848101266)(0.16, 12.030075187969924)(0.165, 11.881188118811881)(0.17, 11.519607843137255)(0.175, 11.138014527845037)(0.18, 10.79136690647482)(0.185, 10.451306413301662)(0.19, 10.117647058823529)(0.195, 10.023310023310023)(0.2, 9.49074074074074)(0.205, 9.174311926605505)(0.21, 8.447488584474886)(0.215, 8.371040723981901)(0.22, 7.657657657657658)(0.225, 7.174887892376682)(0.23, 6.263982102908278)(0.235, 5.369127516778524)(0.24, 4.464285714285714)(0.245, 3.7861915367483294)
		}node[pos=1.0](endofplotsquare){} ;
	%\node [above] at (endofplotsquare) {$n=500$};
	\addplot[] coordinates {
(0.0, 100.0)(0.005, 41.02564102564103)(0.01, 33.333333333333336)(0.015, 29.09090909090909)(0.02, 26.446280991735538)(0.025, 23.66412213740458)(0.03, 22.142857142857142)(0.035, 20.945945945945947)(0.04, 19.871794871794872)(0.045, 19.01840490797546)(0.05, 18.235294117647058)(0.055, 17.51412429378531)(0.06, 16.939890710382514)(0.065, 15.873015873015873)(0.07, 15.897435897435898)(0.075, 15.0)(0.08, 15.048543689320388)(0.085, 14.218009478672986)(0.09, 13.88888888888889)(0.095, 13.574660633484163)(0.1, 12.88888888888889)(0.105, 12.608695652173912)(0.11, 12.393162393162394)(0.115, 11.764705882352942)(0.12, 11.934156378600823)(0.125, 11.740890688259109)(0.13, 11.155378486055778)(0.135, 10.980392156862745)(0.14, 10.81081081081081)(0.145, 10.64638783269962)(0.15, 10.150375939849624)(0.155, 10.0)(0.16, 9.523809523809524)(0.165, 9.747292418772563)(0.17, 9.285714285714286)(0.175, 8.8339222614841)(0.18, 9.059233449477352)(0.185, 8.620689655172415)(0.19, 8.532423208191126)(0.195, 8.108108108108109)(0.2, 8.02675585284281)(0.205, 7.308970099667774)(0.21, 7.2368421052631575)(0.215, 7.166123778501628)(0.22, 6.472491909385114)(0.225, 6.109324758842444)(0.23, 5.7507987220447285)(0.235, 5.396825396825397)(0.24, 4.444444444444445)(0.245, 3.7974683544303796)
		}node[pos=0.85](endofplotsquare){} ;
	\node [below left] at (endofplotsquare) {$\scriptstyle n=1000$};
	\end{axis}
	\end{tikzpicture}
	\vspace{-10pt}
	\caption{The percent reduction in the 0.5 probability bound that going from our EBB to using Bennett's inequality (perfect variance information, $\hat{\sigma}^2 = \sigma^2$) achieves, for $n=50,75,100,150,200,300,500,1000$.}
	\label{biggraph4}
\end{figure}

Third, a comparison is made of the further improvement in confidence over our EBB that can be achieved with perfect information about the variance; specifically, Bennett's inequality is used 
%\footnote{Bennett's inequality is here assumed to be relatively tight} 
assuming $\hat{\sigma}^2=\sigma^2$. 
This improvement is plotted in Figure \ref{biggraph4}, which shows that when the variance is small, uncertainty about the variance is the most detrimental to an EBB, such as ours.
However, in general, going from our EBB to perfect variance information shrinks the bounds by about another third.

\section{Application: Multi-Armed Bandits}
\label{sec:bandits}
One example use of concentration inequalities is in the context of the \textit{upper-confidence bound} (UCB) method in \textit{multi-armed bandit} (MAB) problems.
In this section we consider the performance of UCB employing different concentration inequalities in an example MAB, in order to show the benefit of using our EBB.

\subsection{MAB Problem Description}
There are several variations of MAB problems, however the classic MAB \cite{Robbins1952} problem comprises a single bandit machine with $K$ arms, each of which returns rewards that are independently drawn from an unknown distribution when it is pulled. 
In general, the MAB problem is to design an algorithm for sequentially choosing between the $K$ arms in order to maximise the sum of the (initially unknown) stochastic rewards that each arm yields.
Initially, a player must choose exploratory actions to learn about the rewards that each arm returns, before exploiting this information to choose the higher-valued arms.
In this way, MABs illustrate finite horizon reinforcement learning dynamics, 
and is one of the clearest examples of the exploration-exploitation trade-off in machine learning.

Formally, at each time-step, $n$, 
a player has to choose which of the arms to pull.
However, the player initially has no knowledge of the rewards of each arm, $k\in \mathcal{K}$, so it must learn these values in order to deduce a policy that maximises its sum of rewards.
As argued above, in real-world applications, reward values are typically bounded, so we assume that each arm's reward distribution has bounded supports. 
Denote the mean of this distribution and the width of its support $\mu_k$ and $D_k$, respectively.

Let $A  = \{a(1), a(2), \ldots \}$ be a finite sequence of arm pulls, where $a(n)$ is the arm pulled at time-step $t$, $a(n)\in \mathcal{K}$.
Let $R(A)$ be the total return to the player from following the sequence $A$.
The expectation of $A$ is:
\[
\mathbb{E}\left[ R(A) \right] = \sum_{a(t) \in A} \mu_k
\]
An optimal sequence of arm pulls, $A^*$ is one that maximises the expression above, that is:
\[
A^* = \arg\max_{A} \mathbb{E}\left[ R(A) \right] 
    = \arg\max_{A} \sum_{a(n) \in A} \mu_k
\]
However, in order to determine $A^*$, we have to know the value of $\mu_k$ in advance, which we do not.
Thus, $A^*$ is a \textit{theoretical} optimum value, which is
not achievable in general.
Instead, a typical approach to MABs is to define a \textit{loss} or \textit{regret} function, $L(A)$ for an arbitrary algorithm $A$:
\begin{equation}
\label{eqn:regret}
L(A) = \mathbb{E}\left[ R(A^*) \right] - \mathbb{E}\left[ R(A) \right]
\end{equation}
Using this regret function, the MAB problem is transformed to one of finding a sequence, $A$, that minimises $L(A)$.

\subsection{Upper-Confidence Bound Methods}
One well-known and effective strategy for the MAB is UCB \cite{Lai_1985}.
Under UCB, at each iteration, $n$, the arm with the greatest upper confidence bound on the estimated mean of its reward as inferred from past rewards (at some confidence level) is selected.
Specifically, the general form of UCB methods is to define a \textit{confidence interval}, $CI$ on the estimate of the mean:
\[
\mathbb{P}\left(\mu - \hat{\mu} \ge CI \right) \le y
\]
where $y$ is a confidence level,  
and then at each iteration, to select the arm with the greatest upper confidence bound given this confidence interval:
\[
a(n) = \arg\max_{k\in \mathcal{K}} 
\left[ \hat{\mu}_k(n) + CI_k (n) \right]
\]
where $\hat{\mu}_k(n)$ and $ CI_k(n)$ are the mean estimate and confidence interval at time-step $n$, respectively.
In this way, the initial selection of arms is driven by the degree of uncertainty about their rewards, as captured by using the confidence bounds, while over time, the best performing arms are selected more often.

UCB methods can be categorised by the specific type of bandit problem they apply to, and also the method used to infer the confidence interval.
% It is worth mentioning that bandit problems are an increasingly active area of research, and that there are methods competitive to UCB \cite{doi:10.1287/moor.2014.0650}.
One typical UCB method uses Hoeffding's inequality to set the confidence interval \cite{Auer2002}, where Hoeffding's inequality is given by:
\begin{equation}\label{eq:hoeffdings_simple}
\p\left(\mu-\hat{\mu}\ge\sqrt{\frac{D^2\log(1/y)}{2n}}\right) 
\le y.
\end{equation}
Additionally we consider the EBB type UCB method developed by \cite{10.1007/978-3-540-75225-7_15} per their inequality:
\begin{equation}
\p\left(\mu-\hat{\mu}\ge\sqrt{\frac{\hat{\sigma}^2\log(3/t)}{2n}} + \frac{3D\log(3/t)}{2n}\right) 
\le t.
\end{equation}
We also consider a UCB method with the EBB developed by M\&P \cite{Maurer50empiricalbernstein}, 
particularly utilizing the bound of inequality \eqref{maurersbound} (in Section~\ref{evaluation}).
All three are compared to UCB employing our EBB to define the upper confidence bound.
Additionally, we also compare to randomly choosing actions, for a na\"{i}ve baseline.
In all cases we selected UCB to minimise a probability 0.5 bound.

We used a confidence level of 0.5 in all cases simply as a representative of a mid-range bound, 
but note that potentially some different dynamics could occur with the selection of more extreme bounds (i.e.~close to 0 or 1). %\footnote{Which although simple, may be far from ideal. More complex analyses involve the use of an `exploration function' of steadily increasing probability stricture. eg. \cite{10.1007/978-3-540-75225-7_15}}

For the application of our EBB we hand-tuned a function approximating our EBB's numerical probability 0.5 bound:
\begin{equation}\label{eq:prob_bound} \p\left(\mu-\hat{\mu}\ge \frac{D}{\sqrt{n}}\; \min\left[ \sqrt{2\log 2},
\footnotesize
\left(\begin{matrix*}[c]
\frac{3}{5}\sqrt{\min\left[1,\frac{\hat{\sigma}^2}{D^2}+\frac{25}{n}\right]} \\+ \ln\left(\max\left[1,n\left(1-\frac{\hat{\sigma}^2}{D^2}\right)\right]\right)^{-4}\end{matrix*}
\normalsize
\right)\right]\right) 
\lessapprox 0.5 \end{equation}
The process of creating the above expression involved plotting the numerical data, and manually fitting an approximate symbolic expression. This expression was used \textit{in situ} to simplify the application of our EBB in the bandit context. However the numeric data itself may have been calculated and used directly, at the cost of longer compute times.
%In this expression we have taken the minimum with $\sqrt{2\log(2)}$ which is taking a minimum with a twice-weakened Hoeffding's inequality (Equation \ref{eq:hoeffdings_simple}) to give some value to our expression where it would otherwise be undefined, particularly when $n(1-\hat{\sigma}^2/D^2)\le 1$.

\subsection{Problem instances and results}
In the example bandit problems considered here, the number of arms is $K = 8$, each of which yield rewards of between $0$ and $1$.
For each arm $k$, there is a unique $\alpha_k$ and $\beta_k$ parameters of its beta distribution over rewards, and for each realization of the problem, these $\alpha_k$ and $\beta_k$ are drawn uniformly from between 0 and 3.
%
For these problems, we used the different confidence bound approaches, 
and measured their performance in terms of regret, defined in \eqref{eqn:regret}. 
As noted above, regret is a measure of the performance of bandit algorithms identified by the expected loss of selecting an arm against choosing only the ideal arm.
The regret of the different methods of choosing actions was estimated as the average regret obtained across $100,000$ instances of this bandit problem.
We computed the average regret of these methods over finite arm-pulling budgets, $N$, in order to assess the algorithm's finite-time performance.

\begin{figure}
    \centering
	\begin{tikzpicture}
	\begin{axis}[
		title={Expected regret for bandit algorithms with budget $N$},
		xlabel={$N$},
		xmin=0, xmax=400,
		ymin=0, ymax=0.35,
		ymajorgrids=true,
		grid style=dashed
	]
	\addplot[blue] coordinates {
(20, 0.310951130364) (30, 0.317304721799) (40, 0.303506740539) (50, 0.286502047961) (60, 0.271750798627) (70, 0.258441105474) (80, 0.244084337607) (90, 0.23154222192) (100, 0.21962674765) (110, 0.209364293145) (120, 0.19849795256) (130, 0.189366124494) (140, 0.179985057504) (150, 0.17175192486) (160, 0.164084467112) (170, 0.15795328799) (180, 0.151595586119) (190, 0.145627208562) (200, 0.139841473843) (210, 0.135131674343) (220, 0.130210872033) (230, 0.126186563148) (240, 0.121707370459) (250, 0.118323364967) (260, 0.114727672756) (270, 0.11135242178) (280, 0.107973086348) (290, 0.104854372357) (300, 0.101926121277) (310, 0.0993107935735) (320, 0.0965791677494) (330, 0.0944273468526) (340, 0.0919468150041) (350, 0.0897017110445) (360, 0.0874165452919) (370, 0.085411858643) (380, 0.0837605537036) (390, 0.0817399520606)
		}node[pos=0.52](endofplotsquare){} ;
		\node [blue,above,rotate=-25] at (endofplotsquare) {\footnotesize Maurer\&Pontil};
	\addplot[red,line width=0.4mm] coordinates {
(20, 0.336942958587) (30, 0.336937645823) (40, 0.33793528862) (50, 0.336950104881) (60, 0.336542611243) (70, 0.337280819312) (80, 0.337200777509) (90, 0.337451863926) (100, 0.335809963856) (110, 0.337793875156) (120, 0.33654914298) (130, 0.335875820615) (140, 0.336188909491) (150, 0.339081235627) (160, 0.337206338081) (170, 0.337020887335) (180, 0.336563951732) (190, 0.336823591936) (200, 0.335728527085) (210, 0.336906574325) (220, 0.336981316156) (230, 0.33591692432) (240, 0.336764452534) (250, 0.338074323749) (260, 0.336715624161) (270, 0.336287747782) (280, 0.335670715253) (290, 0.337037990821) (300, 0.338315025894) (310, 0.336139218506) (320, 0.334622390817) (330, 0.336859134941) (340, 0.336317904597) (350, 0.336124307504) (360, 0.336277839902) (370, 0.336613274) (380, 0.336662753516) (390, 0.337483689505)
		}node[pos=0.715](endofplotsquare){} ;
		\node [red,below] at (endofplotsquare) {\footnotesize Random};
	\addplot[blue] coordinates {
(20, 0.28743290587) (30, 0.232382220095) (40, 0.20296927431) (50, 0.181606720226) (60, 0.165745102011) (70, 0.153907558509) (80, 0.143186137085) (90, 0.134590089348) (100, 0.126573002174) (110, 0.119992831407) (120, 0.11427869441) (130, 0.108890725408) (140, 0.104018433267) (150, 0.0998081258891) (160, 0.0960210094774) (170, 0.0924770288966) (180, 0.0891490256632) (190, 0.0862832212207) (200, 0.0832737235473) (210, 0.0807582587196) (220, 0.0781651915387) (230, 0.0759558632013) (240, 0.0739131187913) (250, 0.0719286269452) (260, 0.0700910030206) (270, 0.0683275770601) (280, 0.0667819025719) (290, 0.0650880008227) (300, 0.063500206177) (310, 0.0623834758598) (320, 0.0608073686435) (330, 0.0593185615513) (340, 0.0583541183652) (350, 0.0571870323598) (360, 0.0559368431009) (370, 0.054899877847) (380, 0.0538413306667) (390, 0.052941312716)
		}node[pos=0.29](endofplotsquare){} ;
		\node [blue,above,rotate=-25] at (endofplotsquare) {\footnotesize Hoeffding};
	\addplot[blue] coordinates {
(20, 0.306061843642) (30, 0.285754524727) (40, 0.269931278197) (50, 0.248615326378) (60, 0.230327866882) (70, 0.214922429349) (80, 0.200054374281) (90, 0.187439612189) (100, 0.175026770923) (110, 0.165017888537) (120, 0.155510023043) (130, 0.146850970099) (140, 0.139027366099) (150, 0.132617934825) (160, 0.126130658589) (170, 0.120431591885) (180, 0.115019877981) (190, 0.110269427886) (200, 0.105649535257) (210, 0.101741763249) (220, 0.0977283222415) (230, 0.0941251046786) (240, 0.0909714233319) (250, 0.0879807411491) (260, 0.0851390725522) (270, 0.0824012109451) (280, 0.079883684561) (290, 0.0775606819917) (300, 0.0752888280648) (310, 0.0732028631441) (320, 0.070993850246) (330, 0.069161594945) (340, 0.0673921094242) (350, 0.06583053422) (360, 0.0640749729154) (370, 0.0625422168091) (380, 0.0610836359114) (390, 0.0597357326982)
		}node[pos=0.35](endofplotsquare){} ;
		\node [blue,above right, rotate=-25] at (endofplotsquare) {\footnotesize Audibert};
	\addplot[line width=0.30mm] coordinates {
(20, 0.315351878837) (30, 0.252310598394) (40, 0.21365051234) (50, 0.185173245204) (60, 0.164633657836) (70, 0.149662482149) (80, 0.136725328307) (90, 0.126768907712) (100, 0.117664528623) (110, 0.110326598166) (120, 0.103415978409) (130, 0.0975188110085) (140, 0.0922740034531) (150, 0.0878113744221) (160, 0.0837255031) (170, 0.0797008178449) (180, 0.0760441489445) (190, 0.0729725631572) (200, 0.0697582108496) (210, 0.0671583991446) (220, 0.06468719194) (230, 0.0621409299865) (240, 0.0601285592881) (250, 0.0581341532097) (260, 0.0561603237441) (270, 0.0545519043883) (280, 0.0527161522742) (290, 0.0513002710141) (300, 0.0497036485461) (310, 0.0484855329667) (320, 0.0470042219926) (330, 0.045703669572) (340, 0.0446693501732) (350, 0.0433740760739) (360, 0.0423482852895) (370, 0.0412370883341) (380, 0.0403742986427) (390, 0.0394378538536)
		}node[pos=0.85](endofplotsquare){} ;
		\node [below,rotate=-3] at (endofplotsquare) {\footnotesize Our method};
	\end{axis}
	\end{tikzpicture}
	\vspace{-5pt}
	\caption{The expected regret of bandit algorithms and a baseline method in the example bandit problem: UCB method using our bound \eqref{eq:prob_bound}, Hoeffding's, Audibert et.al's, and Maurer \& Pontil's inequalities; and method of uniform randomly choosing an arm.}
	\label{biggraph44}
\end{figure}

The the performance of the four methods and the na\"{i}ve baseline are shown in Figure~\ref{biggraph44}.
From this figure, we see that minimizing an upper confidence bound utilizing our inequality \eqref{eq:prob_bound} results in best performance (lowest regret), except marginally in the region of very small sample budgets.

It is somewhat surprising to see the more complicated EBB methods \cite{Maurer50empiricalbernstein,10.1007/978-3-540-75225-7_15} perform worse than the much simpler Hoeffding's inequality. As EBB inequalities are specifically constructed in a way to incorporate the estimate of the variance, then the potential advantage comes when there are sufficiently many samples for reliable variance estimation. However a bound without this construction (such as Hoeffding's inequality) may be tighter and more effective for small/medium sample budgets. 
As expected, the random method of choosing arms had a constant expected average regret across action budgets, as it does not learn with additional samples of the arms' rewards.

\section{Conclusion}\label{sec:conclusion}

In this paper, we have extended existing work on concentration inequalities to derive a new and stronger EBB.
Our EBB has many applications, in any setting where a mean value must be estimated with confidence, such as bandit problems.
Our EBB was shown to tighten known EBB-based confidence intervals by about a third, thereby improving the value of these types of concentration inequalities. 
This value was demonstrated in a MAB problem, where using our EBB in a UCB algorithm was shown to improve online learning performance.

\appendix
\section{Proofs}
\subsection{Small Proofs}\label{appendix:small}
%\small
\begin{proof}[Proof of Probability Union - Lemma \ref{prob_union}]
For any events $A$ and $B$\\
$\p(A\cup B) \le \p(A)+\p(B)$, hence for events $a>b$ and $b>c$:\\ $\p((a>b) \cup (b>c)) \le \p(a>b) + \p(b>c)$\\
If $a>c$, then $(a>b) \cup (b>c)$ is true irrespective of $b$, so:\\
$\p(a>c) \le \p((a>b) \cup (b>c))$
\hfill $\blacksquare$
\end{proof}

\begin{proof}[Proof of Variance Decomposition - Lemma \ref{variance1}]By expanding and $\hat{\sigma}^2$:\\
\(\quad\hat{\sigma}^2=\frac{1}{n-1}\sum_i\left(x_i-\frac{1}{n}\sum_jx_j \right)^2 
=\frac{1}{n-1}\left(\sum_ix_i^2-\frac{1}{n}\sum_{i,j}x_ix_j \right) = \frac{n}{n-1}\left(\hat{\sigma}_0^2-\hat{\mu}^2\right)\hfill\blacksquare\)
\end{proof}

\begin{proof}[Proof of Chernoff Bound - Lemma \ref{chernoff1}]\\
$\p(\hat{\mu}\ge t) =  \p\left(\exp\left(s\sum_{i=1}^nx_i\right)\ge \exp(snt)\right)$\\
\-\hspace{8mm}$\le \E\left[\exp\left(s\sum_{i=1}^nx_i\right)\right]\exp(-snt) \le \E\left[\exp\left(sX\right)\right]^n\exp(-snt)
$\\
using Markov's inequality and the i.i.d of the samples, respectively.
$\hfill\blacksquare$
\end{proof}

\subsection{A Proof of Bennett's inequality}\label{appendix:A}

\begin{theorem}[Parabola Fitting]\label{thm:parabola}
For $b>0$, $a<b$ and $z>0$, there exists an $\alpha,\beta,\gamma$ such that: $\alpha x^2+\beta x+\gamma\ge \exp(x)$ for all $a\le x\le b$, and:\\
\-\hspace{3mm}$z\alpha+\gamma = (z\exp(b) + b^2\exp(-z/b))(z + b^2)^{-1}$.
\end{theorem}
\begin{proof}
A example parabola $\alpha x^2+\beta x+\gamma$ which that satisfies these requirements tangentially touches the exponential curve at one point (at $x=f<b$) and intersects it at another (at $x=b$), as illustrated in Figure \ref{fig:graph1}.
Thus the parabola's intersection at $x=b$ and its tangential intersection at $x=f$ can be written in matrix algebra:
$$
\begin{bmatrix}
    \alpha \\
    \beta \\
	\gamma
\end{bmatrix}
=
\begin{bmatrix}
    b^2 & b & 1 \\
    f^2 & f & 1 \\
	2f  & 1 & 0
\end{bmatrix}^{-1}
\begin{bmatrix}
    \exp(b) \\
    \exp(f) \\
	\exp(f)
\end{bmatrix}$$
This gives our parabola parameters $\alpha,\beta,\gamma$, in terms of $f$ and $b$, hence:\\
\-\hspace{3mm}$z\alpha+\gamma = (((z+fb-b)(f-b-1)-b)e^f+(f^2+z)e^b)(b-f)^{-2}$\\
Minimizing with respect to $f$ occurs at $f=\frac{-z}{b}$ and gives the result.$\hfill\blacksquare$
\end{proof}

\begin{proof}[Proof of Bennett's inequlity -- Lemma \ref{hoeffdings1}]
As random variable X is bounded $a\le X\le b$, for any $s>0$, by Theorem \ref{thm:parabola}, there exist parameters $\alpha,\beta,\gamma$ such that, $\alpha s^2X^2+\beta sX+\gamma\ge \exp(sX)$ is always satisfied, hence for these we have:
\-\hspace{3mm}\(\E\left[\exp(sX)\right] \le \E[\alpha s^2X^2+\beta sX+\gamma] \le \alpha s^2\E[X^2]+\gamma \le \alpha  s^2\sigma^2+\gamma\)\\
\-\hspace{20.5mm}\( \le (\sigma^2\exp(sb) + b^2\exp(-s\sigma^2/b))(\sigma^2 + b^2)^{-1}\)\\
Hence by application of lemma \ref{chernoff1}:\\
\-\hspace{3mm}\(\p(\hat{\mu}\ge t) \;\le\; (\sigma^2\exp(sb) + b^2\exp(-s\sigma^2/b))^n((\sigma^2 + b^2)\exp(st))^{-n}\)\\
and finding the minimum with respect to $s$ completes the proof.$\hfill \blacksquare$
\end{proof}

\subsection{Remaining Proofs}\label{appendix:B}

\begin{proof}[Proof of Sample Square Bound - Lemma \ref{sample_squares}]
There exist parameters $\alpha,\gamma$ such for all $a\le X\le b$ that $\alpha X^2 + \gamma \ge \exp(-qX^2)$ whence:\\
\-\hspace{3mm}\(\E[\exp(-qX^2)] \le \E[\alpha x^2 +\gamma] \le \alpha\sigma^2 + \gamma \)\\
With $d=\max(b,-a)$, we choose (Fig \ref{fig:graph111}) $\alpha=(\exp(-qd^2)-1)d^{-2}$ and $\gamma=1$\\
Then applying lemma \ref{chernoff1} to the mean of the negated sample squares gives:\\
\-\hspace{3mm}\(
\p(-\hat{\sigma}_0^2\ge t) \le \left(\frac{\sigma^2}{d^2}\exp(-qd^2)+1-\frac{\sigma^2}{d^2}\right)^n\exp(-qnt) 
\)\\
Substituting $t$ for $y-\sigma^2$ and minimizing with $q$ completes the proof.
$\hfill\blacksquare$
\end{proof}

\begin{proof}[Proof of Sample Variance Bound - Lemma \ref{variance2}]
By Lemmas \ref{sample_squares} and \ref{variance1}:\\
\-\hspace{3mm}\(\p\left(\sigma^2 - \hat{\sigma}^2 > \frac{n}{n-1}\left(\hat{\mu}^2+y- \frac{1}{n}\sigma^2\right)\right) 
\le H_2^n\left(\frac{\sigma^2}{d^2},\frac{y}{d^2}\right)\)\\
Also, by manipulating the inner inequality of equation \ref{eq_no1}:\\ \-\hspace{3mm}\(\p\left(\frac{n}{n-1}\left(\hat{\mu}^2+y-\frac{1}{n}\sigma^2\right)\ge \frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)\right) \le H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right)\)\\
Applying lemma \ref{prob_union} to the above two equations gives:\\
\-\hspace{3mm}\(\p\left(\sigma^2 - \hat{\sigma}^2 > \frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)\right) \le H_2^n\left(\frac{\sigma^2}{d^2},\frac{y}{d^2}\right)+H_1^n\left(\frac{\sigma^2}{b^2},\frac{r}{b}\right)+H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r}{a}\right)\)\\
For $w=\frac{n}{n-1}\left(r^2+y-\frac{1}{n}\sigma^2\right)$ there is a range of possible $r,y>0$ which we parameterise by value $\phi$, such that $0\le\phi\le 1$:\\
\-\hspace{3mm}\(y(\phi) = (1-\phi)\left(\frac{n-1}{n}w+\frac{1}{n}\sigma^2\right) \quad\text{and}\quad
r(\phi)^2 = \phi\left(\frac{n-1}{n}w+\frac{1}{n}\sigma^2\right)\)\\
Thus:\\
\-\hspace{3mm}\(\p\left(\sigma^2 - \hat{\sigma}^2 > w\right) 
\le H_2^n\left(\frac{\sigma^2}{d^2},\frac{y(\phi)}{d^2}\right) 
  + H_1^n\left(\frac{\sigma^2}{b^2},\frac{r(\phi)}{b}\right) + H_1^n\left(\frac{\sigma^2}{a^2},\frac{-r(\phi)}{a}\right)\)\\
The result of this proof follows by taking the minimum over $\phi$.
$\hfill\blacksquare$
\end{proof}

\begin{figure}%
\centering
\parbox{2in}{

\begin{tikzpicture}[scale=0.7]
\draw[->] (-3.5,0) -- (2,0) node[anchor=north] {$x$};
\draw[->] (0,0) -- (0,4) node[anchor=east] {};
\draw[smooth, domain=-3.5:2.0, color=black, line width=0.20mm] 
    plot (\x,{e^(\x)/2}) node [right] {\footnotesize $e^x$};
\draw[smooth, domain=-3.5:2.0, color=red, line width=0.20mm] 
    plot (\x,{(0.316137167001903*\x*\x + 1.39988395124422*\x + 1.67055451771745)/2}) node [right] {\footnotesize $\alpha x^2+\beta x+\gamma$};
\draw (1.5,-0.1) -- (1.5,{e^(1.5)/2});
\draw (-2,-0.1) -- (-2,{e^(-2)/2});
\draw (-2.5,-0.1) -- (-2.5,0);
\draw[black,fill] (1.5,{e^(1.5)/2}) circle (0.25mm);
\draw[black,fill] (-2,{e^(-2)/2}) circle (0.25mm);
\draw	(-2.5,-0.25) node{{\scriptsize $a$}}
		(-2,-0.25) node{{\scriptsize $f$}}
		(1.5,-0.25) node{{\scriptsize $b$}};
\end{tikzpicture}

\caption{A parabola parametarised by touching and intercepting points $f,b$ above an exponential curve for all $a\le x\le b$}%
\label{fig:graph1}}%
\qquad
\begin{minipage}{2in}%

\begin{tikzpicture}[scale=1.2]
\draw[->] (-2.2,0) -- (2.2,0) node[anchor=north] {$x$};
\draw[->] (0,0) -- (0,1.5) node[anchor=east] {};
\draw[smooth, domain=-2.0:2.0, color=black, line width=0.20mm] 
    plot (\x,{e^(-(\x*\x))}) node [above] {\footnotesize $e^{-qx^2}$};
\draw[smooth, domain=-1.8:1.8, color=red, line width=0.20mm] 
    plot (\x,{-0.4825*\x*\x+1}) node [right] {\footnotesize $g(x)$};
\draw (1.3,-0.1) -- (1.3,{e^(-1.3*1.3)});
\draw (-1,-0.1) -- (-1,{e^(-1*1)});
\draw	(-1,-0.25) node{{\scriptsize $a$}}
		(1.3,-0.25) node{{\scriptsize $b$}};
\end{tikzpicture}

\caption{$g(x)=(e^{-qd^2}-1)d^{-2}x^2+1$ over function $f(x)=e^{-qx^2}$ for all $a\le x\le b$ where $d=\max(b,-a)$; in the case $a=-1,b=1.3,q=1$}%
\label{fig:graph111}%
\end{minipage}%
\end{figure}

%\bibliographystyle{splncs04}
%\bibliography{references}

\begin{thebibliography}{10}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }
\providecommand{\doi}[1]{https://doi.org/#1}

\bibitem{AgarwalDekelXiao2010}
Agarwal, A., Dekel, O., Xiao, L.: Optimal algorithms for online convex
  optimization with multi-point bandit feedback. In: 23rd Annual Conf. Learning
  Theory (COLT'10) (2010)

\bibitem{Aggarwal2015}
Aggarwal, C.C.: Data Mining: The Textbook, chap. Outlier analysis, pp.
  237--263. Springer Publishing Company, Incorporated (2015)

\bibitem{AudibertBubeck_COLT2009}
Audibert, J.Y., Bubeck, S.: Minimax policies for adversarial and stochastic
  bandits. In: 22nd Annual Conf. Learning Theory (COLT'09) (2009)

\bibitem{10.1007/978-3-540-75225-7_15}
Audibert, J.Y., Munos, R., Szepesv{\'a}ri, C.: Tuning bandit algorithms in
  stochastic environments. In: Hutter, M., Servedio, R.A., Takimoto, E. (eds.)
  Algorithmic Learning Theory. pp. 150--165. Springer Berlin Heidelberg,
  Berlin, Heidelberg (2007)

\bibitem{AuerCesa-BianchiEtal_SIAM2003}
Auer, P., Cesa-{B}ianchi, N., Freund, Y., Schapire, R.: The
  non-stochasticmulti-armed bandit problem. SIAM Journal on Computing
  \textbf{31}(1),  48--77 (2003)

\bibitem{Auer2002}
Auer, P., Cesa-Bianchi, N., Fischer, P.: Finite-time analysis of the multiarmed
  bandit problem. Machine Learning  \textbf{47}(2),  235--256 (May 2002)

\bibitem{10.2307/2282438}
Bennett, G.: Probability inequalities for the sum of independent random
  variables. Journal of the American Statistical Association  \textbf{57}(297),
   33--45 (1962)

\bibitem{Bentkus08boundsfor}
Bentkus, V., Ju\v{s}kevi\v{c}ius, T.: Bounds for tail probabilities of
  martingales using skewness and kurtosis. Lithuanian Mathematical Journal
  \textbf{48}(1),  30--37 (Jan 2008)

\bibitem{MR3363542}
Bercu, B., Delyon, B., Rio, E.: Concentration inequalities for sums and
  martingales. Springer Briefs in Mathematics, Springer (2015)

\bibitem{Burnstein1}
Bernstein, S.N.: On a modification of {C}hebyshev’s inequality and of the
  error formula of {L}aplace. Uchenye Zapiski Nauch.-Issled. Kaf. Ukraine,
  Sect. Math  \textbf{1},  38--48 (1924)

\bibitem{8000571}
Bhaduri, M., Zhan, J., Chiu, C., Zhan, F.: A novel online and non-parametric
  approach for drift detection in big data. IEEE Access  \textbf{5},
  15883--15892 (2017)

\bibitem{Chebyshev1}
Bienaymé, I.J.: Considérations àl'appui de la découverte de {L}aplace.
  Comptes Rendus de l'Académie des Sciences  \textbf{37},  309--324 (1853)

\bibitem{Boucheron2004}
Boucheron, S., Lugosi, G., Bousquet, O.: Concentration inequalities. In:
  Bousquet, O., von Luxburg, U., R{\"a}tsch, G. (eds.) Advanced Lectures on
  Machine Learning: ML Summer Schools 2003, Canberra, Australia, February 2 -
  14, 2003, T{\"u}bingen, Germany, August 4 - 16, 2003, Revised Lectures, pp.
  208--240. Springer Berlin Heidelberg, Berlin, Heidelberg (2004)

\bibitem{Boucheron_concentrationinequalities}
Boucheron, S., Lugosi, G., Massart, P.: Concentration inequalities using the
  entropy method. The Annals of Probability  \textbf{31}(3),  1583--1614 (2003)

\bibitem{Cesa-BianchiLugosi2006}
Cesa-{B}ianchi, N., Lugosi, G.: Prediction, Learning, and Games. Cambridge
  University Press (2006)

\bibitem{efron1981}
Efron, B., Stein, C.: The jackknife estimate of variance. Annals of Statistics
  \textbf{9}(3),  586--596 (05 1981)

\bibitem{FlaxmanKalaiMcMahan2005}
Flaxman, A., Kalai, A., McMahan, B.: Online convex optimization in the bandit
  setting: Gradient descent without a gradient. In: Proc. 16th Annual ACM-SIAM
  Symposium on Discrete Algorithms (SODA'05). p. 385–394 (2005)

\bibitem{hoeffding1}
Hoeffding, W.: Probability inequalities for sums of bounded random variables.
  Journal of the American Statistical Association  \textbf{58}(301),  13--30
  (Mar 1963)

\bibitem{KiferShaiGehrke2004}
Kifer, D., Ben-David, S., Gehrke, J.: Detecting change in data streams. In:
  Proc. 30th Int. Conf. Very Large Data Bases (VLDB'04). pp. 180--191. VLDB '04
  (2004)

\bibitem{Lai_1985}
Lai, T., Robbins, H.: Asymptotically efficient adaptive allocation rules.
  Advances in Applied Mathematics  \textbf{6}(1),  4--22 (Mar 1985)

\bibitem{MR2245497}
Maurer, A.: Concentration inequalities for functions of independent variables.
  Random Structures \& Algorithms  \textbf{29}(2),  121--138 (2006)

\bibitem{Maurer50empiricalbernstein}
Maurer, A., Pontil, M.: Empirical {B}ernstein bounds and sample variance
  penalization. stat. Proceedings of the 22nd Annual Conf. Learning Theory
  (COLT'09) (June 2009)

\bibitem{Mnih:2008:EBS:1390156.1390241}
Mnih, V., Szepesv\'{a}ri, C., Audibert, J.Y.: Empirical {B}ernstein stopping.
  In: Proc. 25th Int. Conf. Machine Learning (ICML'08). pp. 672--679 (2008)

\bibitem{Pinelis2014}
Pinelis, I.: On the {B}ennett-{H}oeffding inequality. Annales de i'Institut
  Henri Poincar\'{e} - Probabilit\'{e}s et Statistiques  \textbf{50}(1),
  15--27 (2014)

\bibitem{Zia-UrRehman2012}
Rehman, M.Z., Li, T., Li, T.: Exploiting empirical variance for data stream
  classification. Journal of Shanghai Jiaotong University (Science)
  \textbf{17}(2),  245--250 (Apr 2012)

\bibitem{Robbins1952}
Robbins, H.: Some aspects of the sequential design of experiments. Bulletin of
  the AMS  \textbf{55},  527--535 (1952)

\bibitem{zbMATH05780164}
Sharma, R., Gupta, M., Kapoor, G.: Some better bounds on the variance with
  applications. Journal of Mathematical Inequalities  \textbf{4}(3),  355--363
  (2010)

\bibitem{Talagrand1995}
Talagrand, M.: Concentration of measure and isoperimetric inequalities in
  product spaces. Publications Math{\'e}matiques de l'Institut des Hautes
  {\'E}tudes Scientifiques  \textbf{81}(1),  73--205 (Dec 1995)

\bibitem{zbMATH00812598}
Talagrand, M.: The missing factor in {H}oeffding's inequalities. Annales de
  l'Institut Henri Poincare, Probability and Statistics  \textbf{31}(4),
  689--702 (1995)

\bibitem{DBLP:conf/aaai/ThomasTG15}
Thomas, P.S., Theocharous, G., Ghavamzadeh, M.: High-confidence off-policy
  evaluation. In: Proc. 29th AAAI Conf. Artificial Intelligence (AAAI'15). pp.
  3000--3006 (2015)

\bibitem{Tran-ThanhChapmanRJ_AAAI2009}
Tran-Thanh, L., Chapman, A.C., Rogers, A., Jennings, N.R.: Knapsack based
  optimal policies for budget-limited multi-armed bandits. In: Proc.~26th AAAI
  Conf. Artificial Intelligence (AAAI'12). pp. 1134--1140. AAAI'12 (2012)

\end{thebibliography}

\end{document}

### 2020-05-09 note/note.tex
added note

\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage[a4paper, total={8in, 11in}]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\DeclareMathOperator*{\argmax}{\arg\!\max}
\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\p}{\mathbb{P}}
\DeclareMathOperator{\pr}{\mathbb{P}}
\newlength{\dhatheight}
\newcommand{\doublehat}[1]{%
    \settoheight{\dhatheight}{\ensuremath{\hat{#1}}}%
    \addtolength{\dhatheight}{-0.15ex}%
    \hat{\vphantom{\rule{1pt}{\dhatheight}}%
    \smash{\hat{#1}}}}

\begin{document}

After my talk on Thursday, some people asked how to improve Hoeffding's inequality, and how it could be made to give confidence-intervals that do not exceed the data's bounds.
Hoeffding's inequality is easy to use and can be essential in some formal proofs. But my research has led me to know that there are better bounds. And if my learning is usefull for someone else, then I regard that as a best kind of outcome!\\

The easiest way to show how Hoeffding's inequality can be improved is to show how a better bound can be created by omitting an approximation in its derivation - ie. creating a universally more powerfull bound.\\
Hoeffding's inequality is an example of a Chernoff bound, which uses Markov's inequality:\\

\begin{lemma}[Markov's Inequality] for any non-negative random variable $X$ and any $a>0$ that: $\p(X\ge a)\le \E[X]/a$ 
\end{lemma}

\begin{lemma}[Chernoff Bound]\label{chernoff1}
If $\hat{\mu} = \frac{1}{n}\sum_{i=1}^nx_i$ is sample mean of $n$ independent and identically distributed samples of random variable $X$ ($x_i\sim X$), then for any $s,t>0$: $\p(\hat{\mu}\ge t)\le\E\left[\exp(sX)\right]^n\exp(-snt)$
\end{lemma}
\begin{proof}
$\p(\hat{\mu}\ge t) =  \p\left(\exp\left(s\sum_{i=1}^nx_i\right)\ge \exp(snt)\right)$ hence by Markov's inequality $\p(\hat{\mu}\ge t)\le \E\left[\exp\left(s\sum_{i=1}^nx_i\right)\right]\exp(-snt)$\\
The result follows as we assume that our samples are independant (for any independant variables $A,B$ that $\E[AB]=\E[A]\E[B]$).
\end{proof}
%Many phenominally powerfull probability bounds follow by finding upper bounds for $\E\left[\exp(sX)\right]$ - which is also called the moment generating function; including Hoeffing's bound:

\begin{theorem}[Hoeffding's inequality for mean zero]\label{hoeffdings_inequality}
Let $X$ be a random variable that is bounded $a\le X\le b$, with a mean $\mu=0$.  Then letting $D=b-a$, then for any $t>0$, the mean $\hat{\mu}$ of $n$ independent samples of $X$ is bounded:
$\p(\hat{\mu}\ge t)\le \exp\left(\frac{-2nt^2}{D^2}\right)$
\end{theorem}
\begin{proof}
To prove Hoeffding's inequality we develop an upper bound for $\E[\exp(sX)]$, if we assume variable $X$ has a probability density function $f(x)$, then we can fit a line over $\exp(sx)$ as:
$\label{Hoeffdings_line_fitting}\E[\exp(sX)] = \int_a^bf(x)\exp(sx)dx \le \int_a^bf(x)(\frac{x-a}{b-a}e^{sb} + \frac{b-x}{b-a}e^{sa})dx$\\
Using the fact that the mean $\mu = \int_a^bf(x)xdx = 0$ thus:
$\E[\exp(sX)] \le \frac{1}{sb-sa}\left(sb\exp(sa) - sa\exp(sb) \right)$\\
Given the fact that for any $\kappa,\gamma$:
$\frac{1}{\kappa-\gamma}(\kappa\exp(\gamma)-\gamma\exp(\kappa))\le \exp\left(\frac{1}{8}(\kappa-\gamma)^2\right)~~~~~\refstepcounter{equation}(\theequation)\label{Hoeffdings_lemma} $\\
Thus $\label{hoeffdings_lemma_eq}\E[\exp(sX)] \le \exp\left(\frac{1}{8}s^2(b-a)^2 \right)$
and by our Chernoff bound (lemma \ref{chernoff1}) we get:
$ \p(\hat{\mu}\ge t) \le \exp\left(\frac{1}{8}s^2(b-a)^2 n-snt\right) $
And minimising with respect to $s$ gives the result.
\end{proof}
\-\hspace{1cm}\\
At a first glance, the most limiting feature of this derivation is the requirement that the mean is zero, however this is ultimately immaterial and simplifies the derivation. We just consider our data as if it were shifted to have a mean of zero, leaving $D$ unchanged. hence we get the equation we know and love:\\

\begin{theorem}[Hoeffding's inequality]\label{Hoeffdings_inequality_proper}
Let $X$ be a real-valued random variable that is bounded $a\le X\le b$.  Then for $D=b-a$ and any $t>0$, the mean $\hat{\mu}$ of $n$ independent samples of $X$ is probability bounded by:\\
\begin{equation}\p(\hat{\mu}-\mu\ge t)\le \exp\left(-2nt^2/D^2\right)
\quad\text{Or by rearranging:}\quad
\p\left(\hat{\mu}-\mu\ge \sqrt{D^2\log(1/t)/(2n)}\right)\le t\end{equation}
\end{theorem}
\-\hspace{1cm}\\
However we can easily do better.\\

\begin{theorem}\label{hoeffdings_inequality22}
Let $X$ be a real-valued random variable that is bounded $a\le X\le b$, with a mean $\mu$ of zero.  Then for $t>0$, the mean $\hat{\mu}$ of $n$ independent samples of $X$ is probability bounded by:
\begin{equation}\p(\hat{\mu}\ge t)\le \left( \frac{b}{b-a}\left(\frac{b(a-t)}{a(b-t)}\right)^{\frac{a-t}{b-a}} -\frac{a}{b-a}\left(\frac{b(a-t)}{a(b-t)}\right)^{\frac{b-t}{b-a}}  \right)^n
\end{equation}
\end{theorem}
\begin{proof}
Exactly the same proof as Theorem \ref{hoeffdings_inequality} except do not use Equation \ref{Hoeffdings_lemma}, leading to:\\
$ \p(\hat{\mu}\ge t) \le (b\exp(sa) - a\exp(sb))^n\exp(-snt)(b-a)^{-n} $ and minimising with respect to $s$ gives the result.
%$$ s = \frac{1}{b-a}\log\left(\frac{b(a - t)}{a(b - t)}\right) $$
\end{proof}
\-\hspace{1cm}\\
Now, this concentration inequality is more powerful but more difficult to manipulate, we also dont usually know $a$ or $b$ (since that would correspond to knowing the mean itself). But we usually know that our data is bounded, for instance if we are dealing with binary data then we know that, our variable $X$ (not shifted to have a zero mean) is bounded $0<X<1$, and we directly get:\\

\begin{theorem}[Also called Hoeffding's inequality]\label{hoeffdings_inequality23}
Let $X$ be a real-valued random variable that is bounded $0\le X\le 1$, with mean $\mu$. Then for $t>0$, the mean $\hat{\mu}$ of $n$ independent samples of $X$ is probability bounded by:
\begin{equation}\p(\hat{\mu}-\mu\ge t)\le \left[\left(\frac{1-\mu}{1-t-\mu}\right)^{1-t-\mu}  \left(\frac{\mu}{t+\mu}\right)^{t+\mu}\right]^n
\end{equation}
\end{theorem}
\begin{proof}Follows directly from Theorem \ref{hoeffdings_inequality22} with the substitution $a=-\mu$ and $b=1-\mu$.
\end{proof}

This eqution is also credited to Hoeffding and is found widely in literature.
So, if you have binary data and your sample mean $\hat{\mu}$ and you want know how likely it is at underestimating the data mean $\mu$ by $t$ then this equation gives this (the equivalent inequality for overestimation is similar)

\pagebreak

So, how much improvement is given by Theorem \ref{hoeffdings_inequality23} over our Hoeffding's inequality Theorem \ref{Hoeffdings_inequality_proper} over what might be achieved perfectly?\\ Consider the following figure:
\-\hspace{1cm}\\

\begin{figure}[h]
\centering

\begin{tikzpicture}[xscale=18.7, yscale=3]
\draw[->] (-0.1,0) -- (0.3,0) node[anchor=north] {$t$};
\draw[->] (0,0) -- (0,1.1) node[anchor=east] {};
\draw[smooth, domain=0:0.3, color=black, line width=0.20mm, samples=100] 
    plot (\x,{e^(-2*9*(\x*\x))}) node [above] {};
\draw[smooth, domain=0:0.15, color=red, line width=0.20mm, samples=100] 
    plot (\x,{((((1-0.85)/(1-\x-0.85))^(1-\x-0.85)) * (((0.85)/(\x+0.85))^(\x+0.85)))^9}) node [right] {};

%\draw[smooth, domain=0:0.85, color=black, line width=0.20mm] 
%    plot (0,0)(1,1) node [above] {};

\draw [color=blue] plot coordinates {((0, 1.0) (0.01, 0.5858470553103369) (0.02, 0.541116769443986) (0.03, 0.4940266224163914) (0.04, 0.4448836480573838) (0.05, 0.39410018156932936) (0.060000000000000005, 0.34221013038093756) (0.07, 0.2898869021427757) (0.08, 0.23796310401811177) (0.09, 0.1874521323190363) (0.09999999999999999, 0.13957177653389025) (0.10999999999999999, 0.09576996688795385) (0.11999999999999998, 0.057752799775041316) (0.12999999999999998, 0.02751498069314216) (0.13999999999999999, 0.007372829712548668) (0.15, 0.0)
};

\draw (0.1,-0.1) -- (0.1,0.1);
\draw	(0.1,-0.25) node{{\scriptsize $0.1$}};

\draw (0.05,-0.1) -- (0.05,0.1);
\draw	(0.05,-0.25) node{{\scriptsize $0.05$}};

\draw (0.15,-0.1) -- (0.15,1);
\draw	(0.15,-0.25) node{{\scriptsize $0.15$}};

\draw	(0.0,-0.25) node{{\scriptsize $0$}};

\draw	(-0.01,1) node{{\scriptsize $1$}};

\end{tikzpicture}

\caption{for binary data, if your sample mean is $\hat{\mu}=0.85$, the probability envelopes of Hoeffdings inequality (black) and from Theorem \ref{hoeffdings_inequality23} (red) above a hypothetical minimum (blue) for $n=9$ }
\label{fig:graph111}
\end{figure}

And from this figure, we can see that the bound derived from Theorem \ref{hoeffdings_inequality23} as the red line is below the black line corresponding to Hoeffding's inequality (Theorem \ref{Hoeffdings_inequality_proper}).
The ideal blue bound (or atleast what I currently suspect is ideal (!) - contact me if you might like to do collaboration or something) is as follows:

$$\p(\hat{\mu}-\mu>t)\le\max\left(\left(1+\frac{t}{\hat{\mu}-1}\right)^n,\sum_{m=0}^{\lfloor \hat{\mu}n\rfloor}\binom{n}{m}
\left(\frac{(\hat{\mu}+t-1)(n-\lfloor \hat{\mu}n \rfloor)}{n(1-\hat{\mu})}\right)^{n-m}
\left(1-\frac{(\hat{\mu}+t-1)(n-\lfloor \hat{\mu}n \rfloor)}{n(1-\hat{\mu})}\right)^{m}
\right)$$

Which I anticipate is the result of Optimal Uncertainty Quantification procedure \cite{doi:10.1137/10080782X} - which basically is the process of searching directly for the worst case probability distribution for your random variables constrained by what you know.\\

In anycase, the literature on concentration inequalities is simply vast, and there are lots of improvements to be made, and an array of techniques which can be applied.
Sticking to the original Hoeffding's inequality is safe for publication purposes - as people understand and know it.
but there is no reason to stay bound to what we are familiar with.

\section{an additional note}
So, in deriving (most, but importantly not all) concentration inequalities (such as Hoeffding's) we start with the assumption of distribution parameters and then deduce the likely error of sampling statistics from that. However the way in which we often use these inequalities is in reverse, starting from knowledge of sampling statistics and then making inferences about the distribution parameters.
And if you are a baysian like I am, you should be very worried... as this is technically invalid use.
However, I understand that ultimately the same problem is part of statistical hypothesis testing generally.

\bibliographystyle{plain}
%\bibliographystyle{authordate1}
\bibliography{bib}

\end{document}

### 2020-05-09 note/math3.py

@@ -1,0 +1,27 @@
+from sympy import symbols, exp, simplify, diff, factor, expand, Sum, Rational
+import sympy
+from sympy.interactive.printing import init_printing
+init_printing(use_unicode=False, wrap_line=False, no_global=True)
+from sympy.matrices import Matrix
+from sympy.solvers import solve
+from sympy.abc import x,i,j
+from sympy.core import Add, Mul
+import pdb
+
+a,b,D,t,s = symbols('a,b,D,t,s')
+
+F = (b*exp(s*a) - a*exp(s*b))*exp(-s*t)/(b-a)
+
+#F = F.subs({a:b-D})
+diffF = diff(F,s)
+
+diffF *= (b-a)*exp(s*t)
+diffF = diffF.expand().simplify()
+
+solF = F.subs({s:solve(diffF,s)[0]})
+
+pdb.set_trace()
+#print 
+
+
+

### 2020-05-09 note/test.py

@@ -1,0 +1,19 @@
+from math import exp
+
+
+def xxrange(start,stop,step):
+	x = start
+	while x<stop:
+		yield x
+		x += step
+
+def f(k,g):
+	if (k-g==0):
+		return 0
+	return exp((k-g)**2*1.0/8) - (k*exp(g)-g*exp(k))/(k-g)
+
+for x in xxrange(-10,10,0.005):
+	for y in xxrange(-10,10,0.005):
+		#print f(x,y)
+		if f(x,y)<0:
+			print "whoa"

### 2020-05-09 note/test2.py

@@ -1,0 +1,66 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from math import factorial, floor
+
+def xxrange(start,stop,step):
+	x = start
+	while (x<stop):
+		yield x
+		x += step
+
+def ncr(n,r):
+	return factorial(n)/(factorial(n-r)*factorial(r))
+
+hatmu = 0.7
+t=0.01
+mu=hatmu+t
+n = 9
+
+
+import pdb
+pdb.set_trace()
+
+cutoff = 1-n*(1-hatmu)/(n-floor(hatmu*n))
+alpha_cutoff = (mu-1)*1.0/(cutoff-1)
+cutoff_probability = 0
+for nn in range(0,int(floor(hatmu*n))+1):
+	cutoff_probability += ncr(n,nn)*alpha_cutoff**(n-nn)*(1-alpha_cutoff)**(nn)
+
+cutoff = (n*hatmu-1)/(n-1)
+print cutoff
+
+xvalues = []
+values = []
+values2 = []
+
+for x in list(xxrange(0,hatmu,0.001)):
+	alpha = (mu-1)/(x-1)
+	p = 0
+	for nn in range(0,n+1):
+		if (nn*x+(n-nn)<=n*hatmu):
+			p += ncr(n,nn)*alpha**nn*(1-alpha)**(n-nn)
+	values.append(p)
+	xvalues.append(x)
+	if (x>cutoff):
+		values2.append(cutoff_probability)
+	else:
+		values2.append(0.0)
+
+
+x = np.array(xvalues)
+y = np.array(values)
+y2 = np.array(values2)
+
+
+#x = np.linspace(0, 10, 500)
+#y = np.sin(x)
+
+fig, ax = plt.subplots()
+
+line2, = ax.plot(x, y)
+line2, = ax.plot(x, y2)
+
+
+ax.legend()
+plt.show()
+

### 2020-05-09 note/test3.py

@@ -1,0 +1,37 @@
+import numpy as np
+from math import factorial, floor
+
+def xxrange(start,stop,step):
+	x = start
+	while (x<stop):
+		yield x
+		x += step
+
+def ncr(n,r):
+	return factorial(n)/(factorial(n-r)*factorial(r))
+
+
+
+
+def max_probability(hatmu,n,t):
+	mu=hatmu+t
+	cutoff = 1-n*(1-hatmu)/(n-floor(hatmu*n))
+	alpha_cutoff = (mu-1)*1.0/(cutoff-1)
+	cutoff_probability = 0
+	for nn in range(0,int(floor(hatmu*n))+1):
+		cutoff_probability += ncr(n,nn)*alpha_cutoff**(n-nn)*(1-alpha_cutoff)**(nn)
+	return cutoff_probability
+
+def max_probability2(hatmu,n,t):
+	mu=hatmu+t
+	alpha = (mu-1)/(hatmu-1)
+	return alpha**n
+
+
+hatmu = 0.85
+n = 9
+
+for t in xxrange(0,1-hatmu,0.01):
+	print (t,max(max_probability(hatmu,n,t),max_probability2(hatmu,n,t))),
+
+
